### 2021-04-12 src/data-processing/prep_data.Rmd
add prep data file

---
title: 'Prepare Data'
author: 
output: 
  github_document:
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r "setup", include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center",
                      fig.path=('../../report/figures/'))
library(printr)
options(digits = 2)
library(rmarkdown)
```

# Scripts
- [Required Packages &amp; Reproducibility](#required-packages-&amp;-reproducibility)
- [Tidy Data](#tidy-data)
- [Save Data for Analysis](#save-data-for-analysis)
- [Visualization of Data](#visualization-of-data)
  - [Dependent Variable](#dependent-variable)
  - [Independent Variable](#independent-variable)
  - [Control Variables](#control-variables)
  - [Correlations Matrix](#correlations-matrix)

## Required Packages &amp; Reproducibility
```{r "env", message=FALSE, warning=F}
rm(list=ls())
renv::snapshot()
source(here::here("src/lib/functions.R"))
```

## Tidy Data

```{r "get data from Qualtrics"}
pret <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
                  force_request = TRUE, verbose = TRUE,
                 label = FALSE, convert = FALSE) %>%
  filter(Consent == 1)  %>%
  select(matches("PreT\\d"), id = ResponseId) %>%
  select(-matches("PreT[26]_NPS_GROUP")) %>%
  unite(order_PreT5, matches("PreT5_DO_\\d+"), sep="|") %>%
  unite(order_PreT7, matches("PreT7_DO_\\d+"), sep="|") %>%
  unite(order_PreT, matches("Pre-Treatment_DO_PreT\\d+"), sep="|") %>%
  select(id, PreT1:PreT5_4, PreT6:PreT7_5, 
         order_PreT5, order_PreT7, order_PreT) %>%
  mutate(across(matches("PreT5_\\d+"), 
            ~recode(., `15` = 5, `14` = 4, `13` = 3,
                    `12` = 2, `11` = 1)))

td <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
                  force_request = TRUE, verbose = TRUE,
                 label = FALSE, convert = FALSE) %>%
  filter(Consent == 1) %>%
  select(matches("FL_32"), id = ResponseId) %>%
  pivot_longer(cols = FL_32_DO_FL_104:FL_32_DO_FL_118,
               names_to = "Def") %>%
  drop_na(value) %>%
  mutate(Def = recode(Def,
                       `FL_32_DO_FL_104` = "Rachid Amezian + Compromis",
                       `FL_32_DO_FL_106` = "Rachid Amezian + Geen compromis",
                       `FL_32_DO_FL_108` = "Karel van der Kleijn + Compromis",
                       `FL_32_DO_FL_110` = "Karel van der Kleijn + Geen compromis",
                       `FL_32_DO_FL_112` = "Rachida Amezian + Compromis",
                       `FL_32_DO_FL_114` = "Rachida Amezian + Geen compromis",
                       `FL_32_DO_FL_116` = "Karin van der Kleijn + Compromis",
                       `FL_32_DO_FL_118` = "Karin van der Kleijn + Geen compromis")) %>%
  select(-value)

ti <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
                  force_request = TRUE, verbose = TRUE,
                 label = FALSE, convert = FALSE) %>%
  filter(Consent == 1) %>%
  select(matches("FL_78"), id = ResponseId) %>%
  pivot_longer(cols = FL_78_DO_FL_123:FL_78_DO_FL_142,
               names_to = "Imm") %>%
  drop_na(value) %>%
  mutate(Imm = recode(Imm,
                       `FL_78_DO_FL_123` = "Rachid Amezian + Compromis",
                       `FL_78_DO_FL_125` = "Rachid Amezian + Geen compromis",
                       `FL_78_DO_FL_129` = "Karel van der Kleijn + Compromis",
                       `FL_78_DO_FL_132` = "Karel van der Kleijn + Geen compromis",
                       `FL_78_DO_FL_134` = "Rachida Amezian + Compromis",
                       `FL_78_DO_FL_137` = "Rachida Amezian + Geen compromis",
                       `FL_32_DO_FL_139` = "Karin van der Kleijn + Compromis",
                       `FL_32_DO_FL_142` = "Karin van der Kleijn + Geen compromis"))  %>%
  select(-value)

te <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
                  force_request = TRUE, verbose = TRUE,
                 label = FALSE, convert = FALSE) %>%
  filter(Consent == 1) %>%
  select(matches("FL_84"), id = ResponseId) %>%
  pivot_longer(cols = FL_84_DO_FL_144:FL_84_DO_FL_161,
               names_to = "Edu") %>%
  drop_na(value) %>%
  mutate(Edu = recode(Edu,
                       `FL_84_DO_FL_144` = "Rachid Amezian + Compromis",
                       `FL_84_DO_FL_145` = "Rachid Amezian + Geen compromis",
                       `FL_84_DO_FL_148` = "Karel van der Kleijn + Compromis",
                       `FL_84_DO_FL_151` = "Karel van der Kleijn + Geen compromis",
                       `FL_84_DO_FL_153` = "Rachida Amezian + Compromis",
                       `FL_84_DO_FL_157` = "Rachida Amezian + Geen compromis",
                       `FL_84_DO_FL_159` = "Karin van der Kleijn + Compromis",
                       `FL_84_DO_FL_161` = "Karin van der Kleijn + Geen compromis")) %>%
  select(-value)

tc <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
                  force_request = TRUE, verbose = TRUE,
                 label = FALSE, convert = FALSE) %>%
  filter(Consent == 1) %>%
  select(matches("FL_101"), id = ResponseId) %>%
  pivot_longer(cols = FL_101_DO_FL_163:FL_101_DO_FL_177,
               names_to = "COVID") %>%
  drop_na(value) %>%
  mutate(COVID = recode(COVID,
                       `FL_101_DO_FL_163` = "Rachid Amezian + Compromis",
                       `FL_101_DO_FL_165` = "Rachid Amezian + Geen compromis",
                       `FL_101_DO_FL_167` = "Karel van der Kleijn + Compromis",
                       `FL_101_DO_FL_169` = "Karel van der Kleijn + Geen compromis",
                       `FL_101_DO_FL_171` = "Rachida Amezian + Compromis",
                       `FL_101_DO_FL_173` = "Rachida Amezian + Geen compromis",
                       `FL_101_DO_FL_175` = "Karin van der Kleijn + Compromis",
                       `FL_101_DO_FL_177` = "Karin van der Kleijn + Geen compromis")) %>%
  select(-value)

pt <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
                  force_request = TRUE, verbose = TRUE,
                 label = FALSE, convert = FALSE) %>%
  filter(Consent == 1) %>%
  select(matches("PT-[A-Z]\\d"), id = ResponseId) %>%
  select(-matches("PT-[A-Z]\\d_NPS_GROUP")) %>%
  unite(order_PT_D1, matches("PT-D1_DO_\\d+"), sep="|") %>%
  unite(order_PT_D, matches("PostTreatment-Defense_DO_PT-D\\d+"), sep="|") %>%
  unite(order_PT_E1, matches("PT-E1_DO_\\d+"), sep="|") %>%
  unite(order_PT_E, matches("PostTreatment-Education_DO_PT-E\\d+"), sep="|") %>%
  unite(order_PT_I1, matches("PT-I1_DO_\\d+"), sep="|") %>%
  unite(order_PT_I, matches("PostTreatment-Immigration_DO_PT-I\\d+"), sep="|") %>%
  unite(order_PT_C1, matches("PT-C1_DO_\\d+"), sep="|") %>%
  unite(order_PT_C, matches("PostTreatment-Corona_DO_PT-C\\d+"), sep="|") %>%
  select(id, `PT-D1_1`:`PT-D1_6`, `PT-D2`:`PT-I1_6`, `PT-I2`:`PT-E1_6`, 
         `PT-E2`: `PT-C1_6`, `PT-C2`:`PT-C4`, order_PT_D1, order_PT_D,
         order_PT_E1, order_PT_E, order_PT_I1, order_PT_I, 
         order_PT_C1, order_PT_C)

bg <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
                  force_request = TRUE, verbose = TRUE,
                 label = FALSE, convert = FALSE) %>%
  filter(Consent == 1) %>%
  select(id = ResponseId, matches("F\\d"), etnicity) %>%
  unite(order_F6, matches("F6_DO_\\d+"), sep="|") %>%
  select(id, F1:F3, F4 = F4_1_TEXT, F5 = etnicity, F6, F7:F8, order_F6)

d <- left_join(bg, pret, by = "id")
d <- left_join(d, td, by = "id")
d <- left_join(d, ti, by = "id")
d <- left_join(d, te, by = "id")
d <- left_join(d, tc, by = "id")
d <- left_join(d, pt, by = "id")
rm(bg, pret, td, ti, te, tc, pt)
```

## Save Data for Analysis
```{r "save data"}
save(d, file = here("data/intermediate/cleaned_data.RData"))
```

## Visualization of Data

### Dependent Variable
```{r "Dependent Variable", echo=F}
```

### Independent Variable
```{r "Independent Variables", echo=F, message=FALSE, warning=FALSE,fig.width=10, fig.height=10}

```

### Correlations Matrix
```{r "Correlations Matrix", echo=F, message=T, warning=T, fig.width=15, fig.height=15}

```

### 2021-04-12 src/lib/functions.R

@@ -1,0 +1,3 @@
+library(here)
+library(tidyverse)
+library(qualtRics)

### 2021-04-13 docs/pap/poweranalysis.R
add pap details

@@ -1,16 +1,10 @@
 # Power Analysis
-library(DeclareDesign)
-library(tidyverse)
-library(ggpubr)
-library(scales)
-
 rm(list = ls())
+source(here::here("src/lib/functions.R"))
 
 #H1 & H2
 N <- 100
-assignment_prob <- 0.25 
-# only 2 in 8 conditions is have women/migration background + compromise condition. 
-# So there is a 1/4 you are exposed to the full women/migration background compromise condition
+assignment_prob <- 0.25 # only 2 in 8 conditions is have women/migration background + compromise condition. 
 treatment_effect <- 0.1
 
 population <- declare_population(N = N, u = rnorm(N))

### 2021-04-13 src/lib/functions.R

@@ -1,3 +1,6 @@
 library(here)
 library(tidyverse)
 library(qualtRics)
+library(DeclareDesign)
+library(ggpubr)
+library(scales)

### 2021-04-13 src/data-processing/prep_data.Rmd
pap info

@@
   unite(order_PreT, matches("Pre-Treatment_DO_PreT\\d+"), sep="|") %>%
-  select(id, PreT1:PreT5_4, PreT6:PreT7_5, 
+  select(id, PreT1:PreT5_4, PreT6:PreT7_7, PreT8, 
          order_PreT5, order_PreT7, order_PreT) %>%
@@
 
-td <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
+tr <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
                   force_request = TRUE, verbose = TRUE,
@@
   filter(Consent == 1) %>%
-  select(matches("FL_32"), id = ResponseId) %>%
-  pivot_longer(cols = FL_32_DO_FL_104:FL_32_DO_FL_118,
-               names_to = "Def") %>%
-  drop_na(value) %>%
-  mutate(Def = recode(Def,
-                       `FL_32_DO_FL_104` = "Rachid Amezian + Compromis",
-                       `FL_32_DO_FL_106` = "Rachid Amezian + Geen compromis",
-                       `FL_32_DO_FL_108` = "Karel van der Kleijn + Compromis",
-                       `FL_32_DO_FL_110` = "Karel van der Kleijn + Geen compromis",
-                       `FL_32_DO_FL_112` = "Rachida Amezian + Compromis",
-                       `FL_32_DO_FL_114` = "Rachida Amezian + Geen compromis",
-                       `FL_32_DO_FL_116` = "Karin van der Kleijn + Compromis",
-                       `FL_32_DO_FL_118` = "Karin van der Kleijn + Geen compromis")) %>%
-  select(-value)
-
-ti <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
-                  force_request = TRUE, verbose = TRUE,
-                 label = FALSE, convert = FALSE) %>%
-  filter(Consent == 1) %>%
-  select(matches("FL_78"), id = ResponseId) %>%
-  pivot_longer(cols = FL_78_DO_FL_123:FL_78_DO_FL_142,
-               names_to = "Imm") %>%
-  drop_na(value) %>%
-  mutate(Imm = recode(Imm,
-                       `FL_78_DO_FL_123` = "Rachid Amezian + Compromis",
-                       `FL_78_DO_FL_125` = "Rachid Amezian + Geen compromis",
-                       `FL_78_DO_FL_129` = "Karel van der Kleijn + Compromis",
-                       `FL_78_DO_FL_132` = "Karel van der Kleijn + Geen compromis",
-                       `FL_78_DO_FL_134` = "Rachida Amezian + Compromis",
-                       `FL_78_DO_FL_137` = "Rachida Amezian + Geen compromis",
-                       `FL_32_DO_FL_139` = "Karin van der Kleijn + Compromis",
-                       `FL_32_DO_FL_142` = "Karin van der Kleijn + Geen compromis"))  %>%
-  select(-value)
-
-te <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
-                  force_request = TRUE, verbose = TRUE,
-                 label = FALSE, convert = FALSE) %>%
-  filter(Consent == 1) %>%
-  select(matches("FL_84"), id = ResponseId) %>%
-  pivot_longer(cols = FL_84_DO_FL_144:FL_84_DO_FL_161,
-               names_to = "Edu") %>%
-  drop_na(value) %>%
-  mutate(Edu = recode(Edu,
-                       `FL_84_DO_FL_144` = "Rachid Amezian + Compromis",
-                       `FL_84_DO_FL_145` = "Rachid Amezian + Geen compromis",
-                       `FL_84_DO_FL_148` = "Karel van der Kleijn + Compromis",
-                       `FL_84_DO_FL_151` = "Karel van der Kleijn + Geen compromis",
-                       `FL_84_DO_FL_153` = "Rachida Amezian + Compromis",
-                       `FL_84_DO_FL_157` = "Rachida Amezian + Geen compromis",
-                       `FL_84_DO_FL_159` = "Karin van der Kleijn + Compromis",
-                       `FL_84_DO_FL_161` = "Karin van der Kleijn + Geen compromis")) %>%
-  select(-value)
-
-tc <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
-                  force_request = TRUE, verbose = TRUE,
-                 label = FALSE, convert = FALSE) %>%
-  filter(Consent == 1) %>%
-  select(matches("FL_101"), id = ResponseId) %>%
-  pivot_longer(cols = FL_101_DO_FL_163:FL_101_DO_FL_177,
-               names_to = "COVID") %>%
-  drop_na(value) %>%
-  mutate(COVID = recode(COVID,
-                       `FL_101_DO_FL_163` = "Rachid Amezian + Compromis",
-                       `FL_101_DO_FL_165` = "Rachid Amezian + Geen compromis",
-                       `FL_101_DO_FL_167` = "Karel van der Kleijn + Compromis",
-                       `FL_101_DO_FL_169` = "Karel van der Kleijn + Geen compromis",
-                       `FL_101_DO_FL_171` = "Rachida Amezian + Compromis",
-                       `FL_101_DO_FL_173` = "Rachida Amezian + Geen compromis",
-                       `FL_101_DO_FL_175` = "Karin van der Kleijn + Compromis",
-                       `FL_101_DO_FL_177` = "Karin van der Kleijn + Geen compromis")) %>%
-  select(-value)
+  select(matches("name-[A-Z]"), compromis, id = ResponseId)
 
@@
   unite(order_F6, matches("F6_DO_\\d+"), sep="|") %>%
+  mutate(F1 = recode(F1, `1` = 0, `2` = 1, `3` = 2, `4` = 999)) %>%
   select(id, F1:F3, F4 = F4_1_TEXT, F5 = etnicity, F6, F7:F8, order_F6)
@@
 d <- left_join(bg, pret, by = "id")
-d <- left_join(d, td, by = "id")
-d <- left_join(d, ti, by = "id")
-d <- left_join(d, te, by = "id")
-d <- left_join(d, tc, by = "id")
+d <- left_join(d, tr, by = "id")
 d <- left_join(d, pt, by = "id")
-rm(bg, pret, td, ti, te, tc, pt)
+rm(bg, pret, tr, pt)
 ```

### 2021-04-13 docs/pap/poweranalysis.R

@@ -20,31 +20,14 @@ designs <- redesign(design=two_arm_design, N=seq(500,2500,250), treatment_effect
 alpha <- .05
 my_diagnosands <- declare_diagnosands(power.onetailed=mean(p.value<alpha), keep_defaults=TRUE)
 diagnosis1 <- diagnose_designs(designs,diagnosands=my_diagnosands)
-diagnosis <- diagnosis1$diagnosands_df[,c(2,3,7)]
+diagnosis <- diagnosis1$diagnosands_df
+diagnosis1  <- diagnosis %>% 
+  select(N, treatment_effect, power.onetailed) %>%
+  mutate(id = "Power-Analysis for H1 and H2")
 
-ggplot(diagnosis, aes(x=N, y=power.onetailed, group=factor(treatment_effect), colour=factor(treatment_effect))) +
-  geom_line() +
-  geom_hline(yintercept=0.95, linetype="dashed") +
-  geom_hline(yintercept=0.8, linetype="dashed", color = "grey") +
-  geom_vline(xintercept = 2000,linetype="dotdash", color = "darkgrey") +
-  ylim(c(0,1)) +
-  labs(x = "Number of Respondents", y = "Power: One-Tailed",
-       subtitle = "Power-Analysis for H1 and H2") +
-  scale_y_continuous(labels=percent) +
-  theme_minimal() +
-  scale_color_viridis_d() +
-  theme(plot.title = element_text(hjust = 0.5),
-        plot.subtitle = element_text(hjust = 0.5),
-        legend.position="bottom",
-        legend.title = element_blank()) +
-  guides(color=guide_legend(nrow=1,byrow=TRUE))
-
-  
 #H3
 N <- 100
-assignment_prob <- 0.125 
-# only 1 in 8 conditions is have women + migration background + compromise condition. 
-# So there is a 1/8 you are exposed to the full women + migration background compromise condition
+assignment_prob <- 0.125 # only 1 in 8 conditions is have women + migration background + compromise condition. 
 treatment_effect <- 0.1
 
 population <- declare_population(N = N, u = rnorm(N))
@@ -60,32 +43,35 @@ designs <- redesign(design=two_arm_design, N=seq(500,2500,250), treatment_effect
 alpha <- .05
 my_diagnosands <- declare_diagnosands(power.onetailed=mean(p.value<alpha), keep_defaults=TRUE)
[…]

### 2021-04-14 src/data-processing/prep_data.Rmd
minor edits getting data from qualtrics

@@
 - [Save Data for Analysis](#save-data-for-analysis)
+- [Check Missing Values](#check-missing-values)
 - [Visualization of Data](#visualization-of-data)
@@
 rm(list=ls())
+source(here::here("src/lib/functions.R"))
 renv::snapshot()
-source(here::here("src/lib/functions.R"))
 ```
@@
 ## Tidy Data
+This code chuck downloads the data from Qualtrics using the API and cleans the raw data.
 
-```{r "get data from Qualtrics"}
-pret <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
-                  force_request = TRUE, verbose = TRUE,
-                 label = FALSE, convert = FALSE) %>%
-  filter(Consent == 1)  %>%
-  select(matches("PreT\\d"), id = ResponseId) %>%
-  select(-matches("PreT[26]_NPS_GROUP")) %>%
-  unite(order_PreT5, matches("PreT5_DO_\\d+"), sep="|") %>%
-  unite(order_PreT7, matches("PreT7_DO_\\d+"), sep="|") %>%
-  unite(order_PreT, matches("Pre-Treatment_DO_PreT\\d+"), sep="|") %>%
-  select(id, PreT1:PreT5_4, PreT6:PreT7_7, PreT8, 
-         order_PreT5, order_PreT7, order_PreT) %>%
-  mutate(across(matches("PreT5_\\d+"), 
-            ~recode(., `15` = 5, `14` = 4, `13` = 3,
-                    `12` = 2, `11` = 1)))
-
-tr <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
-                  force_request = TRUE, verbose = TRUE,
-                  label = FALSE, convert = FALSE) %>%
-  filter(Consent == 1) %>%
-  select(matches("name-[A-Z]"), compromis, id = ResponseId)
-
-pt <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
-                  force_request = TRUE, verbose = TRUE,
-                 label = FALSE, convert = FALSE) %>%
-  filter(Consent == 1) %>%
-  select(matches("PT-[A-Z]\\d"), id = ResponseId) %>%
-  select(-matches("PT-[A-Z]\\d_NPS_GROUP")) %>%
-  unite(order_PT_D1, matches("PT-D1_DO_\\d+"), sep="|") %>%
-  unite(order_PT_D, matches("PostTreatment-Defense_DO_PT-D\\d+"), sep="|") %>%
-  unite(order_PT_E1, matches("PT-E1_DO_\\d+"), sep="|") %>%
-  unite(order_PT_E, matches("PostTreatment-Education_DO_PT-E\\d+"), sep="|") %>%
-  unite(order_PT_I1, matches("PT-I1_DO_\\d+"), sep="|") %>%
-  unite(order_PT_I, matches("PostTreatment-Immigration_DO_PT-I\\d+"), sep="|") %>%
-  unite(order_PT_C1, matches("PT-C1_DO_\\d+"), sep="|") %>%
-  unite(order_PT_C, matches("PostTreatment-Corona_DO_PT-C\\d+"), sep="|") %>%
-  select(id, `PT-D1_1`:`PT-D1_6`, `PT-D2`:`PT-I1_6`, `PT-I2`:`PT-E1_6`, 
-         `PT-E2`: `PT-C1_6`, `PT-C2`:`PT-C4`, order_PT_D1, order_PT_D,
-         order_PT_E1, order_PT_E, order_PT_I1, order_PT_I, 
-         order_PT_C1, order_PT_C)
-
-bg <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
-                  force_request = TRUE, verbose = TRUE,
-                 label = FALSE, convert = FALSE) %>%
-  filter(Consent == 1) %>%
-  select(id = ResponseId, matches("F\\d"), etnicity) %>%
-  unite(order_F6, matches("F6_DO_\\d+"), sep="|") %>%
-  mutate(F1 = recode(F1, `1` = 0, `2` = 1, `3` = 2, `4` = 999)) %>%
-  select(id, F1:F3, F4 = F4_1_TEXT, F5 = etnicity, F6, F7:F8, order_F6)
-
-d <- left_join(bg, pret, by = "id")
-d <- left_join(d, tr, by = "id")
-d <- left_join(d, pt, by = "id")
-rm(bg, pret, tr, pt)
+```{r "get data from Qualtrics", results="hide"}
+source(here("src/data-processing/tidy_data.R"))
 ```
@@
 save(d, file = here("data/intermediate/cleaned_data.RData"))
+```
+
+## Check Missing Values
+
+We employ the following criteria:
+
+- If 10% or less of the values on the dimension are missing, then we re-code the missing values to the overall mean.
+- If 11% or more of the values on the dimension are missing, then we re-code the missing values to a constant (for instance 0) and include a dummy variable indicating whether the response on the covariate was missing or not.
+
+```{r "check missings"}
+
 ```

### 2021-04-14 src/data-processing/tidy_data.R

@@ -1,0 +1,54 @@
+# Tidy Qualtrics Data
+pret <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
+                     force_request = TRUE, verbose = TRUE,
+                     label = FALSE, convert = FALSE) %>%
+  filter(Consent == 1)  %>%
+  select(matches("PreT\\d"), id = ResponseId) %>%
+  select(-matches("PreT[26]_NPS_GROUP")) %>%
+  unite(order_PreT5, matches("PreT5_DO_\\d+"), sep="|", na.rm = TRUE) %>%
+  unite(order_PreT7, matches("PreT7_DO_\\d+"), sep="|", na.rm = TRUE) %>%
+  unite(order_PreT, matches("Pre-Treatment_DO_PreT\\d+"), sep="|", na.rm = TRUE) %>%
+  select(id, PreT1:PreT5_4, PreT6:PreT7_7, PreT8, 
+         order_PreT5, order_PreT7, order_PreT) %>%
+  mutate(across(matches("PreT5_\\d+"), 
+                ~recode(., `15` = 5, `14` = 4, `13` = 3,
+                        `12` = 2, `11` = 1))) 
+
+tr <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
+                   force_request = TRUE, verbose = TRUE,
+                   label = FALSE, convert = FALSE) %>%
+  filter(Consent == 1) %>%
+  select(matches("name-[A-Z]"), compromis, id = ResponseId)
+
+pt <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
+                   force_request = TRUE, verbose = TRUE,
+                   label = FALSE, convert = FALSE) %>%
+  filter(Consent == 1) %>%
+  select(matches("PT-[A-Z]\\d"), id = ResponseId) %>%
+  select(-matches("PT-[A-Z]\\d_NPS_GROUP")) %>%
+  unite(order_PT_D1, matches("PT-D1_DO_\\d+"), sep="|", na.rm = TRUE) %>%
+  unite(order_PT_D, matches("PostTreatment-Defense_DO_PT-D\\d+"), sep="|", na.rm = TRUE) %>%
+  unite(order_PT_E1, matches("PT-E1_DO_\\d+"), sep="|", na.rm = TRUE) %>%
[…]

### 2021-04-14 docs/pap/compromise-punishment-pap.Rmd
update pap

---
title: 'Pre-Analysis Plan'
author: '16 April 2021'
output: 
  github_document:
    toc: yes
    number_sections: true
editor_options: 
  chunk_output_type: console
---

# Hypothesis

# Research Desing and Protocol

## Sample
I will conduct this survey experiment in the Netherlands in April 2021.  
Our sample, recruited through [KiesKompas](https://www.kieskompas.nl/en/), will consist of 2,000 participants (based on the power analysis presented below) of 18 years and older.  
The study has been approved by the [Research Ethics Review Committee](https://fsw.vu.nl/nl/onderzoek/research-ethics-review/index.aspx) of the _Vrije Universiteit Amsterdam_ (see the approval [here](../EthicalApproval.pdf).  
To ensure good quality of our data, two attention checks (discussed in more detail below) are included.  
Each respondent failing the attention check will be excluded and replaced with another 'good' response.

## Experimental Protocol
The study is conducted online and in Dutch.  
Participants are told that they are taking part in a survey to get an overview of how Dutch people form their views on politics. 
After reading an informed consent message participants are forwarded to the main questionnaire (or
the survey will be terminated if they do not agree to the consent form).

First, participants complete a set of background variables on their stances on the political issues used in the experiment (i.e. corona-measures, defense, education, immigration) and on their attitude towards women in politics -- the full codeboek can be viewed [here](#).  
The pre-treatment block ends with one of the two attention checks included in this survey. 
When participants fail this attention check, a warning appears asking them to read the question again
carefully  and  to  answer  again.   
Only when they have answered it correctly, they enter the first round of the experiment. 
After each round of the experiment, some filler questions are asked about the respondents demographics. 
The stimuli in the experiment are news messages in the same style as the Dutch news website [nu.nl](https://www.nu.nl/).
In these news messages, we manipulate: a) the _gender_ of the politician (male vs. female); b) the _migration background_ of the politician (based on a Arabic sounding name (Rachid(a) Amezian) or a native Dutch sounding name (Karel/Karin van der Kleijn)); and c) whether the politician _striked a compromise or not_.
This creates a full `2*2*2` factorial experiment with four rounds.  
Every round, the news message covers a new issue.  
The issues are:  "defense" (increase cooperation of the defense units), "immigration" (immigration stop in western countries), "education" (expansion creative elementary school activities), "COVID-
19" (emergency legislation to combat COVID-19).
For every round, the politicians name, and thereby gender and immigration background, are manipulated in the text and in the picture as well as the decision to strike a compromise.
For an illustration of the stimulus material, see the Figure below.
All manipulated elements are within the blue boxes.

<img src="FMPdefensie_annotated.png" style="display: block; margin: auto;" />

The text is translated from ARTICLE, the original authors have done XXX. Justification names. Pictures come from ...

## Power Analysis
As we explain in detail in section 4, we use OLS regression with anger (H1-H2) or anx-
iety  (H3-4)  as  dependent  variable  and  the  three  manipulations  (certainty,  control  and
responsibility) as independent variables.  We will test each hypothesis separately for all
four issues.  We used the R package "DeclareDesign" (Blair et al., 2019) for our power
analysis 1, assuming a small effect of b= 0.2 (Figure 2, yellow line).  As our hypotheses are  directional,  we  will run  one-tailed  tests  with  an  alpha  of  .05.   Our  power  analysis shows that testing hypotheses 1 (a, b and c) and 3 (a and b), requires a sample size of 1,200 participants (x-axis) to reach power of 0.95 (black dashed line, Figure 2, panel A). Note that if the effect size b is bigger then .2 { i.e., .3, .4, .5 or .6 { smaller sample sizes
are sufficient to reach power of 0.95. To test Hypotheses 2 (Anger frame) and 4 (Anxiety Frame), we can detect a small effect b = 0.2 (yellow line) with a power of .8 (gray dashed line) and a one-tailed test of signficance at alpha .05 with a sample of 1,500 participants (Figure 2, Panel B). At 1,800 participants, with a small effect and one-tailed test of significance at .05, we reach power of .88.  A sample of 1.800 participants therefore gives us suficient power to test Hypotheses 1 and 3 but a probability of 12% for a Type II error remains when testing
Hypotheses 2 and 4.  We will therefore test Hypotheses 2 and 4 first by issue and second,
by pooling our data across issues.  This will give us sufficient power to test H2 and 4.

# Measures

## Dependent Variables

## Control Variables

## Attention Checks

## Exclusion Criteria

# Analysis

## Hypothesis 1

## Hypothesis 2

## Hypothesis 3

# Stimulus Material

### 2021-04-19 docs/pap/compromise-punishment-pap.Rmd
add changes to pap

@@
     number_sections: true
+  bookdown::pdf_book:
+    base_format: rticles::jss_article
 editor_options: 
   chunk_output_type: console
+bibliography: references.bib
 ---
@@
 Participants are told that they are taking part in a survey to get an overview of how Dutch people form their views on politics.
-After reading an informed consent message participants are forwarded to the main questionnaire (or
-the survey will be terminated if they do not agree to the consent form).
+After reading an informed consent message participants are forwarded to the main questionnaire (or the survey will be terminated if they do not agree to the consent form).
 
@@
 Every round, the news message covers a new issue.
-The issues are:  "defense" (increase cooperation of the defense units), "immigration" (immigration stop in western countries), "education" (expansion creative elementary school activities), "COVID-
-19" (emergency legislation to combat COVID-19).
+The issues are: "defense" (increase cooperation of the defense units), "immigration" (immigration stop in western countries), "education" (expansion creative elementary school activities), "COVID-19" (emergency legislation to combat COVID-19).
 For every round, the politicians name, and thereby gender and immigration background, are manipulated in the text and in the picture as well as the decision to strike a compromise.
@@
 
-<img src="FMPdefensie_annotated.png" style="display: block; margin: auto;" />
+```{r ssa-logo, fig.align = 'center', out.width = "75%", fig.cap = "The new SSA logo, which is actually a scatterplot, which is super neat!", echo = FALSE}
+knitr::include_graphics(here::here("docs/pap/FMPdefensie_annotated.png"))
+```
 
-The text is translated from ARTICLE, the original authors have done XXX. Justification names. Pictures come from ...
+The text of the treatment is a Dutch translation of the stimulus material developed by @bauer2017punished. 
+The authors have pre-tested the text of the stimuli material several times [see the Web Appendix of @bauer2017punished].
+The photo's of their stimuli material can unfortunately not be used, because a) @bauer2017punished only investigate the difference between men and women politicians, using solely photo''s of caucasians; and b) the American flag was present in their material.
+Instead, I have used photo's from local politicians of the city of The Hague that are not know to the general public. 
+The men politicians are in real life representatives of the [liberal-progressive party D66](https://www.denhaag.nl/nl/bestuur-en-organisatie/gemeenteraad/raadsleden-en-fractievertegenwoordigers/boutkabout-a.-abid-fractievertegenwoordiger-d66.htm) (man with immigrant background) and of the [christian democratic party CDA](https://www.denhaag.nl/nl/bestuur-en-organisatie/gemeenteraad/raadsleden-en-fractievertegenwoordigers/groot-de-d.p.-daniel-fractievertegenwoordiger-cda.htm) (man without immigrant background).
+The women politicians are in real life representatives of a [right-wing populist party _Hart voor Deen Haag/ Groep de Mos_](https://www.denhaag.nl/nl/bestuur-en-organisatie/gemeenteraad/raadsleden-en-fractievertegenwoordigers/davituliani-n.-nino-raadslid-hart-voor-den-haaggroep-de-mos.htm) (woman with migration background) and of the [social democratic party PvdA](https://www.denhaag.nl/nl/bestuur-en-organisatie/gemeenteraad/raadsleden-en-fractievertegenwoordigers/holman-j.-janneke-raadslid-pvda.htm) (woman without immigrant background).
+Thereby we have a spread over the ideological different parties present in Dutch politics.
+The names for the politicians without immigration background are _Karel_ (man) and _Karin_ (woman) _van der Kleijn_, which are typical native Dutch names.
+For the politicians with an immigration background, we picked _Rachid_ (man) and _Rachida_ (woman) _Amezian_.
 
 ## Power Analysis
-As we explain in detail in section 4, we use OLS regression with anger (H1-H2) or anx-
-iety  (H3-4)  as  dependent  variable  and  the  three  manipulations  (certainty,  control  and
-responsibility) as independent variables.  We will test each hypothesis separately for all
+As detailed in [Section 4](#analysis), I conduct an OLS regression within a multiverse approach [@simonsohn2019specification,@steegen2016increasing] using the four post-treatment questions on the politician's a) leadership evaluaton (scale); b) general favorability; c) representative quality; and d) career perspective as dependent variable and the three manipulations (gender, migration background and whether or not the politician is willing to strike a compromise ) as independent variables.
+Each hypothesis is tested separately for all four issues.
+
+We will test each hypothesis separately for all
 four issues.  We used the R package "DeclareDesign" (Blair et al., 2019) for our power

### 2021-04-19 src/data-processing/tidy_data.R
preprocessed data

@@ -46,7 +46,7 @@ bg <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
   select(id = ResponseId, matches("F\\d"), etnicity) %>%
   unite(order_F6, matches("F6_DO_\\d+"), sep="|") %>%
   mutate(F1 = recode(F1, `1` = 0, `2` = 1, `3` = 2, `4` = 999)) %>%
-  select(id, F1:F3, F4 = F4_1_TEXT, F5 = etnicity, F6, F7:F8, order_F6)
+  select(id, F1:F3, F4 = F4_1_TEXT, F5 = etnicity, F6, F7:F8, F9, order_F6)
 
 d <- left_join(bg, pret, by = "id")
 d <- left_join(d, tr, by = "id")

### 2021-04-19 docs/pap/compromise-punishment-pap.Rmd
changes pap

@@
 output: 
-  github_document:
+  pdf_document:
     toc: yes
     number_sections: true
-  bookdown::pdf_book:
-    base_format: rticles::jss_article
 editor_options: 
@@
 bibliography: references.bib
+header-includes:
+   - \usepackage{floatrow}
+   - \floatsetup[figure]{capposition=top}
 ---
 
+\newpage
 # Hypothesis
@@
 For every round, the politicians name, and thereby gender and immigration background, are manipulated in the text and in the picture as well as the decision to strike a compromise.
-For an illustration of the stimulus material, see the Figure below.
+For an illustration of the stimulus material, see Figure \ref{fig:treatment_example}.
 All manipulated elements are within the blue boxes.
 
-```{r ssa-logo, fig.align = 'center', out.width = "75%", fig.cap = "The new SSA logo, which is actually a scatterplot, which is super neat!", echo = FALSE}
+```{r ssa-logo, fig.align = 'center', out.width = "100%", fig.cap = "\\label{fig:treatment_example}Annotated Example of Stimulus Material", echo = FALSE, fig.topcaption=TRUE}
 knitr::include_graphics(here::here("docs/pap/FMPdefensie_annotated.png"))
@@
 ## Power Analysis
-As detailed in [Section 4](#analysis), I conduct an OLS regression within a multiverse approach [@simonsohn2019specification,@steegen2016increasing] using the four post-treatment questions on the politician's a) leadership evaluaton (scale); b) general favorability; c) representative quality; and d) career perspective as dependent variable and the three manipulations (gender, migration background and whether or not the politician is willing to strike a compromise ) as independent variables.
+As detailed in [Section 4](#analysis), I conduct an OLS regression within a multiverse approach [@simonsohn2019specification;@steegen2016increasing] using the four post-treatment questions on the politician's a) leadership evaluaton (scale); b) general favorability; c) representative quality; and d) career perspective as dependent variable and the three manipulations (gender, migration background and whether or not the politician is willing to strike a compromise ) as independent variables.
 Each hypothesis is tested separately for all four issues.

### 2021-04-19 docs/pap/compromise-punishment-pap.Rmd
changes pap

@@
 bibliography: references.bib
+urlcolor: blue
+linkcolor: blue
 header-includes:
@@
 \newpage
-# Hypothesis
+# Hypotheses
 
@@
 
-```{r ssa-logo, fig.align = 'center', out.width = "100%", fig.cap = "\\label{fig:treatment_example}Annotated Example of Stimulus Material", echo = FALSE, fig.topcaption=TRUE}
+```{r treatment-example, fig.align = 'center', out.width = "85%", fig.cap = "\\label{fig:treatment_example}Annotated Example of Stimulus Material", echo = FALSE, fig.topcaption=TRUE}
 knitr::include_graphics(here::here("docs/pap/FMPdefensie_annotated.png"))
@@
 The text of the treatment is a Dutch translation of the stimulus material developed by @bauer2017punished.
-The authors have pre-tested the text of the stimuli material several times [see the Web Appendix of @bauer2017punished].
+The authors have pre-tested the text of the stimuli material several times [see the [Web Appendix](https://static-content.springer.com/esm/art%3A10.1007%2Fs11109-016-9356-6/MediaObjects/11109_2016_9356_MOESM1_ESM.docx) of @bauer2017punished].
 The photo's of their stimuli material can unfortunately not be used, because a) @bauer2017punished only investigate the difference between men and women politicians, using solely photo''s of caucasians; and b) the American flag was present in their material.
@@
 The men politicians are in real life representatives of the [liberal-progressive party D66](https://www.denhaag.nl/nl/bestuur-en-organisatie/gemeenteraad/raadsleden-en-fractievertegenwoordigers/boutkabout-a.-abid-fractievertegenwoordiger-d66.htm) (man with immigrant background) and of the [christian democratic party CDA](https://www.denhaag.nl/nl/bestuur-en-organisatie/gemeenteraad/raadsleden-en-fractievertegenwoordigers/groot-de-d.p.-daniel-fractievertegenwoordiger-cda.htm) (man without immigrant background).
-The women politicians are in real life representatives of a [right-wing populist party _Hart voor Deen Haag/ Groep de Mos_](https://www.denhaag.nl/nl/bestuur-en-organisatie/gemeenteraad/raadsleden-en-fractievertegenwoordigers/davituliani-n.-nino-raadslid-hart-voor-den-haaggroep-de-mos.htm) (woman with migration background) and of the [social democratic party PvdA](https://www.denhaag.nl/nl/bestuur-en-organisatie/gemeenteraad/raadsleden-en-fractievertegenwoordigers/holman-j.-janneke-raadslid-pvda.htm) (woman without immigrant background).
+The women politicians are in real life representatives of a [right-wing populist party _Hart voor Den Haag/ Groep de Mos_](https://www.denhaag.nl/nl/bestuur-en-organisatie/gemeenteraad/raadsleden-en-fractievertegenwoordigers/davituliani-n.-nino-raadslid-hart-voor-den-haaggroep-de-mos.htm) (woman with migration background) and of the [social democratic party PvdA](https://www.denhaag.nl/nl/bestuur-en-organisatie/gemeenteraad/raadsleden-en-fractievertegenwoordigers/holman-j.-janneke-raadslid-pvda.htm) (woman without immigrant background).
 Thereby we have a spread over the ideological different parties present in Dutch politics.
@@
 Each hypothesis is tested separately for all four issues.
+To calculate power for the hypotheses, the R package `DeclareDesign` is used [@blair2019declaring].
+Based on the study of @bauer2017punished, the effect sizes are between `0.2` and `0.1` -- i.e. a small effect visualized by the purple lines in Figure \ref{fig:power1}.
+The hypothesis are directional, Figure \ref{fig:power1} therefore displays one-tailed tests with $\alpha$ `= 0.05`.
+The power analysis shows that testing hypotheses 1 and 2 requires a sample size of `1,800` participants (x-axis) to reach `95%` power (black dashed line, in the left-panel of Figure \ref{fig:power1}).
+Note that if the effect size is bigger then `0.2` (i.e. `0.3`, `0.4`, `0.5`, or `0.6`) smaller sample sizes
+are sufficient to reach `95\%` power.
+To test H3, the combination of gender and migration background, we can detect a small effect `b = 0.2` (purple line) with a power of `80%` (gray dashed line) and a one-tailed test of signficance at $\alpha$ `=0.05` with a sample of `1,800` participants (Right-Panel of Figure \ref{fig:power1}).
+At `2,000` participants, with a small effect and one-tailed test of significance at $\alpha$ `=0.05`, I reach power of `88%`.
+A sample of `2,000` participants therefore gives me suficient power to test Hypotheses 1 and 2, but a probability of `12%` for a Type II error remains when testing Hypotheses 3. 
+I will therefore test all hypotheses first by issue and second, by pooling our data across issues.
+As Figure \ref{fig:power2} demonstrates, this will give sufficient power even if we do two-tailed testing.
 
-We will test each hypothesis separately for all
-four issues.  We used the R package "DeclareDesign" (Blair et al., 2019) for our power
-analysis 1, assuming a small effect of b= 0.2 (Figure 2, yellow line).
-As our hypotheses are  directional,  we  will run  one-tailed  tests  with  an  alpha  of  .05.
-Our  power  analysis shows that testing hypotheses 1 (a, b and c) and 3 (a and b), requires a sample size of 1,200 participants (x-axis) to reach power of 0.95 (black dashed line, Figure 2, panel A).
-Note that if the effect size b is bigger then .2 { i.e., .3, .4, .5 or .6 { smaller sample sizes
-are sufficient to reach power of 0.95.
-To test Hypotheses 2 (Anger frame) and 4 (Anxiety Frame), we can detect a small effect b = 0.2 (yellow line) with a power of .8 (gray dashed line) and a one-tailed test of signficance at alpha .05 with a sample of 1,500 participants (Figure 2, Panel B).
-At 1,800 participants, with a small effect and one-tailed test of significance at .05, we reach power of .88.
-A sample of 1.800 participants therefore gives us suficient power to test Hypotheses 1 and 3 but a probability of 12% for a Type II error remains when testing
-Hypotheses 2 and 4.  We will therefore test Hypotheses 2 and 4 first by issue and second,
-by pooling our data across issues.  This will give us sufficient power to test H2 and 4.
+```{r power-example, eval = FALSE}
+source(here::here("docs/pap/poweranalysis.R"))
+```
+
+```{r power, fig.align = 'center', out.width = "100%", fig.cap = "\\label{fig:power1}Power Analysis", echo = FALSE, fig.topcaption=TRUE}
+knitr::include_graphics(here::here("docs/pap/power_analysis.png"))
+```
+
+```{r power-pooled, fig.align = 'center', out.width = "100%", fig.cap = "\\label{fig:power2}Power Analysis - Pooled", echo = FALSE, fig.topcaption=TRUE}
+knitr::include_graphics(here::here("docs/pap/power_analysis-pooled.png"))
+```
 
@@
 # Stimulus Material
+
+\newpage
+# References

### 2021-04-21 docs/pap/compromise-punishment-pap.Rmd
update pap

@@
 ---
-title: 'Pre-Analysis Plan'
+title: "Pre-Analysis Plan: Who Bends and Who Breaks? Experimental Evidence for Conditions Affecting Voters' Evaluations of Politicians Striking Compromises"
 author: '16 April 2021'
@@
    - \floatsetup[figure]{capposition=top}
+   - \floatsetup[table]{capposition=top}
+   - \usepackage{booktabs}
+   - \usepackage{longtable}
+   - \usepackage{array}
+   - \usepackage{multirow}
+   - \usepackage{wrapfig}
+   - \usepackage{float}
+   - \usepackage{colortbl}
+   - \usepackage{pdflscape}
+   - \usepackage{tabu}
+   - \usepackage{threeparttable}
+   - \usepackage{threeparttablex}
+   - \usepackage[normalem]{ulem}
+   - \usepackage{makecell}
+   - \usepackage{xcolor}
 ---
+```{r setup, include=FALSE}
+## include this at top of your RMarkdown file for pretty output
+## make sure to have the printr package installed: install.packages('printr')
+knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
+#library(printr)
+library(tidyverse)
+library(kableExtra)
+options(kableExtra.latex.load_packages = FALSE)
+```
 
 \newpage
-# Hypotheses
+# Theoretical Background
+
+# Expectations
+
+**Gender hypothesis** (_H1_):  Women politicians are evaluated lower when striking a political compromise compared to men politicians.
+
+**Migration hypothesis** (_H2_): Politicians with a migration background are evaluated lower when striking a political compromise compared to politicians without a migration background.
+
+**Intersection hypothesis** (_H3_): Women politician with a migration background are evaluated lower when striking a political compromise compared to men politicians without a migration background.
 
@@
 I will conduct this survey experiment in the Netherlands in April 2021.
-Our sample, recruited through [KiesKompas](https://www.kieskompas.nl/en/), will consist of 2,000 participants (based on the power analysis presented below) of 18 years and older.
-The study has been approved by the [Research Ethics Review Committee](https://fsw.vu.nl/nl/onderzoek/research-ethics-review/index.aspx) of the _Vrije Universiteit Amsterdam_ (see the approval [here](../EthicalApproval.pdf).
-To ensure good quality of our data, two attention checks (discussed in more detail below) are included.
+The sample, recruited through [KiesKompas](https://www.kieskompas.nl/en/), will consist of 2,000 participants (based on the power analysis presented in Figure \ref{fig:power1}) of 18 years and older.
+Kieskompas works with non-random opt-in respondents.
+Therefore, I measure many demographic background variables (see [Section 3.2](#control-variables)).
+Balance checks will be conducted to demonstrate whether certain categories are over represented in a certain experimental group.
+The study has been approved by the [Research Ethics Review Committee](https://fsw.vu.nl/nl/onderzoek/research-ethics-review/index.aspx) of the _Vrije Universiteit Amsterdam_ (see the approval [here](https://github.com/MarikenvdVelden/compromise-punish/blob/main/docs/EthicalApproval.pdf)).
+To ensure good quality of our data, two attention checks (discussed in more detail in [Section 3.3](#attention-checks)) are included.
 Each respondent failing the attention check will be excluded and replaced with another 'good' response.
@@
 To calculate power for the hypotheses, the R package `DeclareDesign` is used [@blair2019declaring].
-Based on the study of @bauer2017punished, the effect sizes are between `0.2` and `0.1` -- i.e. a small effect visualized by the purple lines in Figure \ref{fig:power1}.
+Based on the study of @bauer2017punished, the effect sizes are between `b = 0.2` and `b = 0.1` -- i.e. a small effect visualized by the purple and blue lines in Figure \ref{fig:power1}.
 The hypothesis are directional, Figure \ref{fig:power1} therefore displays one-tailed tests with $\alpha$ `= 0.05`.
@@
 are sufficient to reach `95\%` power.
-To test H3, the combination of gender and migration background, we can detect a small effect `b = 0.2` (purple line) with a power of `80%` (gray dashed line) and a one-tailed test of signficance at $\alpha$ `=0.05` with a sample of `1,800` participants (Right-Panel of Figure \ref{fig:power1}).
+To test H3, the combination of gender and migration background, we can detect a small effect `b = 0.2` (blue line) with a power of `80%` (gray dashed line) and a one-tailed test of signficance at $\alpha$ `=0.05` with a sample of `1,800` participants (Right-Panel of Figure \ref{fig:power1}).
 At `2,000` participants, with a small effect and one-tailed test of significance at $\alpha$ `=0.05`, I reach power of `88%`.
@@
 
-```{r power, fig.align = 'center', out.width = "100%", fig.cap = "\\label{fig:power1}Power Analysis", echo = FALSE, fig.topcaption=TRUE}
+```{r power, fig.align = 'center', out.width = "100%", fig.cap = "\\label{fig:power1}Power Analysis", fig.topcaption=TRUE}
 knitr::include_graphics(here::here("docs/pap/power_analysis.png"))
@@
 
-```{r power-pooled, fig.align = 'center', out.width = "100%", fig.cap = "\\label{fig:power2}Power Analysis - Pooled", echo = FALSE, fig.topcaption=TRUE}
+```{r power-pooled, fig.align = 'center', out.width = "100%", fig.cap = "\\label{fig:power2}Power Analysis - Pooled", fig.topcaption=TRUE}
 knitr::include_graphics(here::here("docs/pap/power_analysis-pooled.png"))
@@
 ## Dependent Variables
+I rely on four measures reflecting different aspects of how people judge politicians.
+The evaluation of politicians' character traits are statements deriving from @aaldering2016political.
+The other three neasures to evaluate the politician of the treatment are translated from @bauer2017punished -- i.e. favorability, representation, and career perspectives.
+General favorability is shown to be related to vote choice [@elis2010dynamics], perceptions of represenation are related to legislative compromise and cooperation [@doherty2013whom], and career perspective is included because critiques of women are typically manifested in their leadership skills [@eagly2007female].
+Since the questionaire is in Dutch, Table \ref{tab:dv} describes the measures both in English and in Dutch.
+
+1. _Evaluation of politicians' character traits_ This measure exists of six statements -- see Table \ref{tab:dv} `PT-1_1` till `PT-1_6`.
+Each statement is measured on a 5-point Likert-scale: From `very much disagree` to `very much agree`.
+If `Cronbach's` $\alpha$ `=>0.8`, I will construct an additive scale for this measure.
+When `Cronbach's` $\alpha$ `<0.8`, I will add the statement as seperate dependent variables in the multiverse analysis.
+
+2.
+_Favorability_ In this measure respondents are asked to rank the politician from very unfavorable (value of `0`) to very favorable (value of `10`) for the decision to (not) strike a compromise on the issue at stake.
+See Table \ref{tab:dv} `PT-2` for the exact phrasing of the question.
+
+3. _Representation_ In this measure, respondents are surveyed on how well the statement "[NAME] is a good representative of [HIS/HER] constituency" describes the politician.
+The politician can be evaluated on an 11-point scale from `very poorly` (value of `0`) till `very well` (value of 10).
+See Table \ref{tab:dv} `PT-3` for the exact phrasing of the question.
+
+4. _Career perspective_ This measure evaluates the politician more broadly by asking whether the politician is likely to move up in leadership position. 
+Respondents answer this question on an 11 point scale, ranging from `very unlikely` (value of `0`) till `very likely` (value of `10`).
+See Table \ref{tab:dv} `PT-4` for the exact phrasing of the question.
+
+```{r dv, topcaption=TRUE}
+d <- tibble(Variable = c("leadership_eval (PT-1)", "leadership_eval (PT-1_1)",
+                         "leadership_eval (PT-1_2)", "leadership_eval (PT-1_3)",
+                         "leadership_eval (PT-1_4)", "leadership_eval (PT-1_5)",
+                         "leadership_eval (PT-1_6)", "favorable (PT-2)", 
+                         "representation (PT-3)", "career (PT-4)"), 
+            `Wording ENG` = c("To what extent does the following statement apply to [NAME]? [NAME] ...", 
+                              "... has integrity", "... is competent", 
+                              "... is decisive", "... is empathetic", 
+                              "... is sympathetic",
+                              "... knows what goes on in society",
+                              "How disapproving or approving are you of the decision by [NAME] to [NOT] strike a compromise on the [ISSUE]?",
+                              "How well does the following statement describe the politician in question: [NAME] is a good representative of [HIS/HER] constituency.",
+                              "Do you think [NAME] is likely to move up the ladder, for example as a minister in government or a leadership position in parliament?"),
+            `Wording NL` = c("In hoeverre is onderstaande stelling van toepassing op [NAAM]? [NAAM]...", 
+                             "... is integer", "... is competent", "... is daadkrachtig",
+                             "... is empathisch","... is sympatiek",
+                             "... weet goed wat er leeft in de samenleving",
+                             "Hoe afkeurend of goedkeurend staat u tegenover de beslissing van [NAAM] om [(G)EEN] compromis te sluiten op [ISSUE]?",
+                             "Hoe goed beschrijft de volgende stelling de desbetreffende politicus: [NAAM] is een goede vertegenwoordiger van [ZIJN/HAAR] achterban.",
+                             "Denkt u dat [NAAM] waarschijnljk hogerop zal komen, bijvoorbeeld als minister in de regering of een leidinggevende positie in het parlement?"))
+
+kbl(d, booktabs =T, caption = "\\label{tab:dv}Survey Questions - DV") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = "3cm") %>%
+  column_spec(2, width = "7cm") %>%
+  column_spec(3, width = "7cm")
+
+```
+
+&nbsp;
 
@@
 
+As control variables, the following _demographics_ are measured: gender, age, education, geographical region, level of urbanness, migration background, vote choice in the 2021 parliamentary elections, employment, and income.
+For the analysis, only variables that are unbalanced over the experimental conditions will be included.
+Table \ref{tab:demographics} gives an overview of the questions asked in the survey as well as their English translations.
+
+- _Gender_ is measured as `sex` based on the advice of Kieskompas. The answer categories are `Male` (value of `1`), `Female` (value of `0`), and `Other` (value of `999`).
+
+- _Age_ is measured as a respondents birth year.
+
+- _Education_ is measured as the highest successfully completed level of education, recoded into three categories: High (Dutch levels _HBO_ and _WO_), Middle (Dutch levels _MBO_, _HAVO_, and _VWO_), and Low (Dutch levels _LBO_, _MAVO_, _elementary school_, or _none_).
+I create dummy variables for each level of education with the lowest category as base category.
+
+- _Geographical region_ is measured using the _Nielsen districs_, dividing the Netherlands into 1) the 3 major cities plus suburbs, Amsterdam (plus Diemen, Ouder-Amstel, Landsmeer, Amstelveen), Rotterdam (plus Schiedam, Capelle aan den IJssel, Krimpen aan den IJssel, Nederlek, Ridderkerk, Barendrecht, Albrandswaard) and The Hague (plus Leidschendam, Voorburg, Rijswijk, Wassenaar, Wateringen); 2) West (Noord-Holland, Zuid-Holland and Utrecht (excluding the major cities and their suburbs; 3) North (Groningen, Friesland and Drenthe), 4) East (Overijssel, Gelderland and Flevoland); and South (Zeeland, Noord-Brabant and Limburg).
+
+- _Urbanness_ Respondents are asked for their postal codes. 
+Using the [Dutch Bureau of Statistics's classification](https://www.cbs.nl/nl-nl/cijfers/detail/84721NED?q=stedelijkheid) we calculate the level of urbanism, ranging from `not at all urban` to `very urban`.
+
+- _Migration background_ I use the [Dutch Bureau of Statistics's classification](https://www.cbs.nl/nl-nl/over-ons/innovatie/project/cbs-experimenteert-met-dotmaps/migratieachtergrond) for the type of migration background.
+The Bureau of Statistics distinguishes between `No migration background`, `1st generation Western`, `2nd generation Western`, `1st generation Non-Western`, and `2nd generation Non-Western`.  
+I create dummy variables for each category with the `2nd generation Non-Western` as base category.
+
+- _Vote recall_ Respondents were asked which party they voted for in the 2021 parliamentary elections.
+The options were 1) all parties that were elected into parliament --`CDA`, `ChristenUnie`, `D66`, `Denk`, `Forum for Democracy`, `GroenLinks`, `PvdA`, `Animal Rights Party`, `PVV`, `SGP`, `SP`, `VVD`, `50Plus Party` -- 2) another party; 3) blanco vote; and 4) a `Don't know` option.
+
+- _Employment_ Respondents were asked which category of employment -- `Full-time employed`, `Part-time employed`, `Entrepreneur`, `Unemployed and searching for a job`, `Unemployed and not searching for a job or incapacitated`, `Housewife/Househusband or else`, `Retired`, `Student or full-time education` -- applied most to them.
+
+- _Income_ Respondents were questioned on their monthly income in bins of €500 -- `€500 or less`, `€501-€1000`, `€1001-€1500`, `€1501-€2000`, `€2001-€2500`, `€2501-€3000`, `€3001-€3500`, `€3501-€4000`, `€4501-€7500`, `€7501 or more` -- as well as giving them the options of `won't  say` and `don't know`.
+
+```{r demographics, topcaption=TRUE}
+d <- tibble(Variable = c("gender (F1)", "age (F2)", "education (F9)",
+                         "region (F3)", "postal_code (F4)", "migration_backgr (F5)",
+                         "vote_recall (F6)", "job (F7)", "income (F8)"), 
+            `Wording ENG` = c("What is your gender?", "What is your year of birth?",
+                              "What is your highest level of education?", 
+                             "In which region do you live?",
+                             "We ask your postal code to be able to make a classification on urbanity (very urban, strongly urban, moderately urban, little urban, not urban).
+By entering your postal code, you explicitly agree that your region of residence will be used for analysis purposes.",
+                             "Where is your country of birth, Where is your father's country of birth?, and Where is your monther's country of birth?",
+                              "Which party did you vote for during the last parliamentary elections of March 2021?",
+                             "What applies most to you? Are you...",
+                              "Can you indicate which income groups your net monthly household income falls into?"),
+            `Wording NL` = c("Wat is uw geslacht?", "Wat is uw geboortejaar?", 
+                             "Wat is uw hoogst GENOTEN opleiding","In welke regio woont u?",
+                             "Wij vragen uw postcode om een indeling op stedelijkheid (zeer sterk stedelijk, sterk stedelijk, matig stedelijk, weinig stedelijk, niet stedelijk) te kunnen maken.
+Door het invoeren van uw postcode gaat u er expliciet mee akkoord dat uw woonregio voor analyse doeleinden wordt gebruikt.",
+                             "Wat is uw geboorteland, Wat is het geboorteland van uw vader, en Wat is het geboorteland van uw moeder?",
+                             "Op welke politieke partij heeft u bij de vorige Tweede Kamerverkiezingen van maart 2021 gestemd?",
+                             "Wat is het meest op u van toepassing? Bent u...",
+                             "Kunt u aangeven in welke inkomensgroepen uw netto maandelijks huishoudinkomen valt?"))
+
+kbl(d, booktabs =T, caption = "\\label{tab:demographics}Survey Questions - Demographics") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = "3cm") %>%
+  column_spec(2, width = "7cm") %>%
+  column_spec(3, width = "7cm")
+
+```
+
+In addition, pre-treatment, respondents' ideological position, position on the issues migration, defense, educaton, and COVID-19 policies, attitudes towards women in politics, and political efficacy are measured in a random order (see Tables \ref{tab:pret1} and \ref{tab:pret2}).
+Those variables will only be included in the analyses if balance checks indicate they are necessary.
+Moreover, the variables will be used to explore heterogeneous relationships.
+
+- _Ideological position_ is measured using an 11-point scale ranging from left (`0`) to right (`10`).
+
+- _Position on immigration_ is measured using two items.
+In the first item, participants are asked to estimate the percentage of immigrants living in the Netherlands, which gives an indication of how prejudiced people are towards people with an immigrant background.
+In the second item, participants are asked to position themselves on whether people with an immigrant background should fully adapt to the Dutch culture on an 11-point scale, ranging from `fully maintain their own values` (value of `0`) to `fully adapt` (value of `10`).
+Hence, higher values indicate a stronger anti-migration position.
+
+```{r pret, topcaption=TRUE}
+d <- tibble(Variable = c("immigration-percentage (PreT1)", "immigration-assimilation (PreT2)",
+                         "defense (PreT3)", "education (PreT4)", "sexism-scale (PreT5)", 
+                         "sexism-scale (PreT5-1)","sexism-scale (PreT5-2)", "sexism-scale (PreT5-3)",
+                         "sexism-scale (PreT5-4)", "sexism-scale (PreT5-5)","rile-self (PreT6)",
+                         "poleff (PreT7)", "poleff (PreT7-1)", "poleff (PreT7-2)", "poleff (PreT7-3)", 
+                         "poleff (PreT7-4)", "poleff (PreT7-5)","poleff (PreT7-6)", "poleff (PreT7-7)",
+                         "corona-policy (PreT8)"), 
+            `Wording ENG` = c("What do you think is the share of immigrants of the Dutch population?
+By immigrants we mean people born in another country (first generation) and their children (second generation).
+Enter a percentage between 0 and 100 below, where 0 means that there are no immigrants in the Netherlands at all, 100 means that all residents of the Netherlands are immigrants, and 50 percent means that half of the Dutch population is immigrants.",
+                              "In the Netherlands, some think that Dutch people with a migration background should be able to live here while maintaining their own culture.
+Others think they should adapt completely to the Dutch culture.
+Where would you place yourself on a line from 0 to 10, where 0 means preservation of own culture for immigrants and 10 that they should adapt completely?",
+                              "The Netherlands must increase defense spending to meet NATO requirements.",
+                              "The Netherlands must increase spending on education to ensure its quality.",
+                              "To what extent do you agree with the following statements:",
+                              "I hope that in the next ten years the Netherlands will have a female prime minister",
+                             "Men are better at making political decisions than women.", 
+                             "It is easier in the Netherlands for a man to become a minister than for a woman.",
+                             "Political parties must do more to ensure that the number of women in the House of Representatives increases.", 
+                             "Women have fewer opportunities in politics in the Netherlands than men.",
+                             "In politics there is often talk about left and right. Where would you put yourself on this scale?",
+                             "You will now get to see a number of theses about Dutch politics. To what extent do you agree or disagree with these statements?",
+                             "The political parties are only interested in my vote and not in my opinion.", 
+                             "Against their better judgment, politicians promise more than they can deliver.", 
+                             "Most politicians are skilled people who know what they are doing.", 
+                             "Politicians are able to solve the most important problems.", 
+                             "I feel well represented by Dutch politicians.", 
+                             "What in politics is called `making compromises' is actually just betraying your principles.", 
+                             "A strong head of government is good for the Netherlands, even if he stretches the rules a bit to get things done.",
+                             "We would like to ask you for your opinion on the measures the government chooses to counter the coronavirus. All in all, are you in favor of:"),
+            `Wording NL` = c("Wat denkt u dat het aandeel is van immigranten van de Nederlandse bevolking?
+Onder immigranten verstaan we mensen die zijn geboren in een ander land (eerste generatie) en hun kinderen (tweede generatie).
+Vul hieronder een percentage in tussen 0 en 100, waarbij 0 betekent dat er helemaal geen immigranten in Nederland zijn, 100 betekent dat alle inwoners van Nederland immigrant zijn, en 50 procent betekent dat de helft van de Nederlandse bevolking immigrant is.",
+                             "In Nederland vinden sommigen dat Nederlanders met een migratieachtergrond hier moeten kunnen leven met behoud van de eigen cultuur.
+Anderen vinden dat zij zich geheel moeten aanpassen aan de Nederlandse cultuur.
+Waar zou u uzelf plaatsen op een lijn van 0 tot en met 10, waarbij de 0 behoud van eigen cultuur voor allochtonen betekent en de 10 dat zij zich geheel moeten aanpassen?",
+                             "Nederland moet de uitgaven aan defensie verhogen om zo te voldoen aan de eisen van de NAVO.",
+                             "Nederland moet de uitgaven aan het onderwijs verhogen om zo de kwaliteit ervan te kunnen waarborgen.",
+                             "In hoeverre bent u het eens met de volgende uitspraken:",
+                             "Ik hoop dat Nederland in de komende tien jaar een vrouwelijke minister-president krijgt", 
+                             "Mannen zijn beter in staat om politieke beslissingen te nemen dan vrouwen.", 
+                             "Het is in Nederland voor een man makkelijker om minister te worden dan voor een vrouw.", 
+                             "Politieke partijen moeten meer doen om te zorgen dat het aantal vrouwen in de Tweede Kamer toeneemt.", 
+                             "Vrouwen krijgen in Nederland minder kansen in de politiek dan mannen.",
+                             "In de politiek wordt vaak gesproken over links en rechts. Waar zou u uzelf op deze schaal plaatsen?",
+                             "In welke mate bent u het eens of oneens met deze stellingen?",
+                                "De politieke partijen zijn alleen maar geïnteresseerd in mijn stem en niet in mijn mening.",
+                             "Tegen beter weten in beloven politici meer dan ze kunnen waarmaken.", 
+                             "De meeste politici zijn bekwame mensen die weten wat ze doen.", 
+                             "Politici zijn in staat om de belangrijkste problemen op te lossen.", 
+                             "Ik voel mij goed vertegenwoordigd door Nederlandse politici.", 
+                             "Wat men in de politiek `het sluiten van compromissen' noemt, is eigenlijk gewoon het verraden van je principes.", 
+                             "Een sterke regeringsleider is goed voor Nederland, ook als deze de regels wat oprekt om dingen voor elkaar te krijgen.",
+                             "Hoe denkt u over de maatregelen die de regering kiest om het coronavirus tegen te gaan? Bent u al met al een voorstander van:"))
+
+kbl(d[1:11,], booktabs =T, caption = "\\label{tab:pret1}Survey Questions - PreTreatment Questions (1)") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = "3cm") %>%
+  column_spec(2, width = "7cm") %>%
+  column_spec(3, width = "7cm")
+
+kbl(d[12:dim(d)[1],], booktabs =T, caption = "\\label{tab:pret2}Survey Questions - PreTreatment Questions (2)") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = "3cm") %>%
+  column_spec(2, width = "7cm") %>%
+  column_spec(3, width = "7cm")
+```
+
+- _Position on defense_ is measured by asking people whether or not more money should be spend on defense to keep up with the NATO requirements using a 5-point Likert-scale (`fully disagree`, `disagree`, `neutral`, `agree`, `fully agree`).
+
+- _Position on education_ is measured by asking people whether or not more money should be spend on education to maintain the quality thereof using a 5-point Likert-scale (`fully disagree`, `disagree`, `neutral`, `agree`, `fully agree`).
+
+- _Position on COVID-19 policies_ is measured by asking people for your opinion on the measures the government chooses to counter the coronavirus, where people can choose for the options: `Much stricter measures to combat the virus (i.e.
+area ban).`, `Slightly stricter measures to prevent viruses.`, `The measures chosen by the government.`, `Slightly more flexible measures so that only the most vulnerable elderly are protected.`, `Much smoother measures to get the economy and nightlife going immediately.`
+
+- _Attitude towards women in politics_ is measured by using the sexism scale developed by Aaldering and Van der Pas.
+Using five statements (see Table \ref{tab:pret1}) people are asked on a 5-point Likert-scale whehter they `fully disagree`, `disagree`, `neutral`, `agree`, or `fully agree`.
+The items will be constructed into an additive scale.
+
+- _Political efficacy_ is measured using seven statements (see Table \ref{tab:pret2}) a 5-point Likert-scale (`fully disagree`, `disagree`, `neutral`, `agree`, `fully agree`).
+
 ## Attention Checks
+I include two attention checks in the survey.
+The first one is after the pre-treatment covariates, the second one is asked just before respondents enter the third round of the experimental treatments.
+The attention checks are taken from @berinsky2014separating and adapted to the Dutch context (see also PAPER IR).
+If a respondents fails the first attention check, a warning appears and the respondent can only continue with the survey once the respondent has correctly answered the question correctly.
+The second attention check also has a warning -- meaning that respondents have to select two options -- but if they fail to correctly pass the check, they are excluded.
+Each excluded respondent due to failing an attention check is replaced with another ``good respondent".
+
+**Attention Check 1**  When a big news story breaks people often go online to get up-to-the-minute details on what is going on.
+We want to know which websites people trust to get this information.
+We also want to know if people are paying attention to the question.
+To show that you have read this much, please ignore the question and select Volkskrant and Metro as your two answers.
+When there is a big news story, which is the one news website you would visit first? (Please
+only choose one).
+Eight (Dutch) news outlets are provided to choose from.
+Respondents pass the attention check if they select _de Volkskrant_ and _Metro_.
+
+**Attention Check 2**:
+We would like to get a sense of your general preferences.
+Most  modern  theories  of  decision  making  recognize  that  decisions  do  not take  place  in  a  vacuum.
+Individual  preferences  and  knowledge,  along  with  situational variables can greatly impact the decision process.
+To demonstrate that you've read this much,  just  go  ahead  and  select  both  red  and  green  among  the  alternatives  below,  no matter what your favourite color is.
+Yes, ignore the question below and select both of
+those options.
+What is your favourite color?
+Six colors are provided to choose from, respondents pass the attention check if they select red and green.
 
 ## Exclusion Criteria
+Participants are required to respond to each question.
+Participants who fail the second attention check will be excluded but replaced by another participant.
 
@@
 
+```{r stimulus, topcaption=TRUE}
+d <- tibble(` ` = c(1:8),
+            `Name Politician` = c(rep("Rachid Amezian", 2), rep("Karel van der Kleijn", 2),
+                                  rep("Rachida Amezian", 2), rep("Karin van der Kleijn", 2)),
+            Gender = c(rep("Men",4), rep("Women", 4)),
+            `Migration Background` = c(rep("Yes", 2), rep("No", 2),
+                                  rep("Yes", 2), rep("No", 2)),
+            Compromise = c("Yes", "No", "Yes", "No", "Yes", "No", "Yes", "No"))
+
+kbl(d, booktabs =T, caption = "\\label{tab:treat}Experimental Conditions",
+    align = c("l", "l", "c", "c", "c")) %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = ".5cm") %>%
+  column_spec(2, width = "3.2cm") %>%
+  column_spec(3, width = "2.5cm")%>%
+  column_spec(4, width = "3.5cm")%>%
+  column_spec(5, width = "2.5cm")
+
+```
+
+Table \ref{tab:treat} show the manipulations of the `2*2*2` experimental design, leading to 8 experimental groups.
+All stimulus material is developed by the [Network Institute of the _Vrije Universiteit Amsterdam_](https://networkinstitute.org/) and can be accessed [here](https://github.com/MarikenvdVelden/compromise-punish/tree/main/docs/pap/treatments).
+The treatment's texts are in Dutch.
+The English translation is displayed in Table \ref{tab:txt}.
+
+```{r text, topcaption=TRUE}
+d <- tibble(`  ` = c("Title", "First Paragraph", "Second Paragraph"),
+            ` ` = c("Politician makes [**no/ **] compromise on [**expansion creative elementary school activities/ intensifying defense cooperation/ migration freeze in Western countries/ Corona emergency legislation**]", "In this term, parliament faces a crucial crossroads regarding an [**expansion of creative elementary school activities/ intensification of defense cooperation/ migration freeze in Western countries/ extension of Corona emergency legislation**].
+With the deadline for a vote fast approaching, parliament must determine the future of the policy on [**expanding creative elementary school activities/ intensifying defense cooperation/ migration freeze in Western countries/ Corona emergency legislation**] in the Netherlands.
+A number of non-partisan organizations have urged parliament to reach a compromise on this issue.
+Time is running out.", "For this important bill to pass, politicians from different political parties will have to put aside their differences and reach a compromise.
+While many in parliament are still debating their positions, some members of both left and right parties have already shown a willingness to compromise.
+One of those who [**won't/ will**] compromise is the politician [**Rachid Amezian/ Rachida Amezian/ Karin van der Kleijn/ Karel van der Kleijn**].
+[**Rachid Amezian/ Rachida Amezian/ Karin van der Kleijn/ Karel van der Kleijn**] has already publicly stated that [**he / she**] wants to make [**no/ a**] compromises and will vote [**against/ for**] this bill.
+Although the vote is still a week away, [**Rachid Amezian/ Rachida Amezian/ Karin van der Kleijn/ Karel van der Kleijn**] has told numerous media sources that [**he/ she**] will not change [**his/ her**] vote.
+[**`This is just not an issue on which I want to compromise'/ `This is an issue on which I am willing to compromise'**] , said [**Rachid Amezian/ Rachida Amezian/ Karin van der Kleijn/ Karel van der Kleijn**].
+`My voters knew this when they elected me.'"))
+
+kbl(d, booktabs =T, caption = "\\label{tab:txt}Text of Experimental Treatment") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = "1cm") %>%
+  column_spec(2, width = "14cm")
+```
+
 \newpage

### 2021-04-21 docs/pap/compromise-punishment-pap.Rmd
update pap

@@
 \newpage
-# Theoretical Background
 
@@
 
+## Balance Checks
+I will conduct a balance test based on demographics (age, gender, education, geographical region, level of urbanness, migration background,  employment, and income), vote choice in the 2021 parliamentary elections, ideological self-placement, political efficacy, attitudes towards women in politics, and positions on the four issues, using the `cobalt` R package [@greifer2021].
+If the groups are unbalanced on one of these variables -- i.e. standardized mean differences `<0.05` -- I will add the covariates to the analyses.
+
+```{r balance, eval=FALSE, echo = TRUE}
+covs <- d %>%
+  mutate(treatment = paste(name, compromis, sep = "-")) %>%
+  select(treatment, PreT1:PreT8, F1:F9)
+
+balanced <-bal.tab(Treatment ~ PreT1 + PreT2 + PreT3 + PreT4 +
+                     PreT5 + PreT6 + PreT7 + PreT8 +
+                     factor(F1) + F2 + factor(F9) + factor(F3) +
+                     factor(F4) + factor(F5) + factor(F6) + F7 + F8,
+                     Age + Education + factor(Sex_str), data = covs,
+          thresholds = c(m = 0.05))[[1]]
+
+balanced <- balanced %>%
+  mutate(variable = c("Immigration (%)", "Immigration", "Defense", "Education", "Sexism",
+                      "Ideology", "Poltical Efficacy", "COVID-19",
+                      "Gender: Male", "Age", "Education: Middle", "Education: High",
+                      "Region: West", "Region: North", "Region: East", "Region: South",
+                      "Little Urban", "Moderatly Urban", "Highly Urban", 
+                      "Very Highly Urban", "Migration Background", "Bij1","CDA",
+                      "ChristenUnie", "D66", "Denk", "Forum for Democracy",
+                      "GroenLinks", "JA21", "PvdA", "Animal Rights Party", "PVV", 
+                      "SGP", "SP", "VOLT","VVD", "50Plus Party", "Employment",
+                      "Income"),
+         variable = factor(variable,
+                           levels = c("Immigration (%)", "Immigration", "Defense",
+                                      "Education", "Sexism", "Ideology", 
+                                      "Poltical Efficacy","COVID-19", 
+                                      "Gender: Male", "Age", "Education: Middle",
+                                      "Education: High", "Region: West", "Region: North",
+                                      "Region: East", "Region: South",
+                                      "Little Urban", "Moderatly Urban", "Highly Urban",
+                                      "Very Highly Urban", "Migration Background",
+                                      "Bij1","CDA", "ChristenUnie", "D66", "Denk", 
+                                      "Forum for Democracy", "GroenLinks", "JA21", 
+                                      "PvdA", "Animal Rights Party", "PVV", 
+                                      "SGP", "SP", "VOLT","VVD", "50Plus Party",
+                                      "Employment", "Income")),
+         difference = Diff.Un,2) %>%
+  select(variable, difference) %>%
+  ggplot(aes(x = variable, y = difference)) +
+  geom_point(size = 3, colour = "gray55") +
+  theme_bw() +
+  labs(x="", y= "Standardized Mean Differences") +
+  ggtitle("Covariate Balance") +
+  theme(plot.title = element_text(hjust = 0.5)) +
+  geom_hline(yintercept = 0) +
+  geom_hline(yintercept = 0.05, linetype = "dashed") +
+  geom_hline(yintercept = -0.05, linetype = "dashed") +
+  coord_flip()
+```
+
 ## Hypothesis 1
+I test the hypotheses formulated in [Section 1](#expectations) applying a multiverse approach [@steegen2016increasing;@simonsohn2019specification] using the `specr` R package [@masur2020specr].
+Instead of running various models using the different dependent variables
 

### 2021-04-21 src/analysis/balance-test.R

@@ -1,0 +1,48 @@
+covs <- d %>%
+  mutate(treatment = paste(name, compromis, sep = "-")) %>%
+  select(treatment, PreT1:PreT8, F1:F9) 
+
+balanced <-bal.tab(Treatment ~ PreT1 + PreT2 + PreT3 + PreT4 +
+                     PreT5 + PreT6 + PreT7 + PreT8 +
+                     factor(F1) + F2 + factor(F9) + factor(F3) +
+                     factor(F4) + factor(F5) + factor(F6) + F7 + F8,
+                   Age + Education + factor(Sex_str), data = covs,
+                   thresholds = c(m = 0.05))[[1]] 
+
+balanced <- balanced %>%
+  mutate(variable = c("Immigration (%)", "Immigration", "Defense", "Education", "Sexism",
+                      "Ideology", "Poltical Efficacy", "COVID-19",
+                      "Gender: Male", "Age", "Education: Middle", "Education: High",
+                      "Region: West", "Region: North", "Region: East", "Region: South",
+                      "Little Urban", "Moderatly Urban", "Highly Urban", 
+                      "Very Highly Urban", "Migration Background", "Bij1","CDA",
+                      "ChristenUnie", "D66", "Denk", "Forum for Democracy",
+                      "GroenLinks", "JA21", "PvdA", "Animal Rights Party", "PVV", 
+                      "SGP", "SP", "VOLT","VVD", "50Plus Party", "Employment",
+                      "Income"),
+         variable = factor(variable,
+                           levels = c("Immigration (%)", "Immigration", "Defense",
+                                      "Education", "Sexism", "Ideology", 
+                                      "Poltical Efficacy","COVID-19", 
+                                      "Gender: Male", "Age", "Education: Middle",
+                                      "Education: High", "Region: West", "Region: North",
+                                      "Region: East", "Region: South",
+                                      "Little Urban", "Moderatly Urban", "Highly Urban",
+                                      "Very Highly Urban", "Migration Background",
+                                      "Bij1","CDA", "ChristenUnie", "D66", "Denk", 
+                                      "Forum for Democracy", "GroenLinks", "JA21", 
+                                      "PvdA", "Animal Rights Party", "PVV", 
+                                      "SGP", "SP", "VOLT","VVD", "50Plus Party",
+                                      "Employment", "Income")),
[…]

### 2021-04-21 docs/pap/compromise-punishment-pap.Rmd
add updated pap

@@
 title: "Pre-Analysis Plan: Who Bends and Who Breaks? Experimental Evidence for Conditions Affecting Voters' Evaluations of Politicians Striking Compromises"
-author: '16 April 2021'
+date: "`r format(Sys.time(), '%d %B, %Y - %X (%Z)')`"
 output: 
@@
 
-```{r power-example, eval = FALSE}
+```{r power-example, eval = FALSE, echo = TRUE}
 source(here::here("docs/pap/poweranalysis.R"))
@@
 # Analysis
+I test the hypotheses formulated in [Section 1](#expectations) by fitting linear multivariate regressions separately for the four issues.
+In each model, will estimate the coefficient for gender of the politician (H1), migration background of the politician (H2), and the interaction of gendere and migration background (H3).
+I will apply a multiverse approach [@steegen2016increasing;@simonsohn2019specification].
+Instead of running various models using the different dependent variables, I will estimate whether the treatment explains the different operationalizations of the dependent variable ([see Section 3.1](#dependent-variables)) in one go and present the estimates and confidence intervals for the several combinations.
+I will only add control variables in the analyses that are unbalanced, as explained in [Section 4.1](#balance-checks).
 
@@
 If the groups are unbalanced on one of these variables -- i.e. standardized mean differences `<0.05` -- I will add the covariates to the analyses.
+I will use the code below to conduct the balance tests (see [here](https://github.com/MarikenvdVelden/compromise-punish/tree/main/src/analysis/balance-test.R) for the R script).
 
@@
 ## Hypothesis 1
-I test the hypotheses formulated in [Section 1](#expectations) applying a multiverse approach [@steegen2016increasing;@simonsohn2019specification] using the `specr` R package [@masur2020specr].
-Instead of running various models using the different dependent variables
+I test the _gender hypothesis_ using Equation \ref{eq:h1} and the code chunk below.
+The coefficient of $\beta_{1}$ denotes the difference in the evaluation of female and male politicians.
+The coefficient of $\beta_{2}$ denotes the difference in the evaluation of politicians who do and do not strike a comprmise.
+The coefficient of $\beta_{3}$ is the interaction of the  $\beta_{1}$ and  $\beta_{2}$.
+If the Average Marginal Effect of $\beta_{1}$ is negative and statistically siginificant when $\beta_{2} = 1$ (i.e. politician stroke a compromise), the _gender hypothesis_ will be confirmed.
+
+\begin{equation}\label{eq:h1}
+  \hat{Y} = \beta_{0} + \beta_{1}Female  + \beta_{2}Compromise + \beta_{3}Compromise * Female + \varepsilon
+\end{equation}
+
+```{r h1, eval = FALSE, echo = TRUE}
+df <- d %>% select(PT1:PT4, gender, compromise)
+
+depVarList <- setdiff(colnames(df), c("gender", "compromise"))
+allModels <- lapply(depVarList, function(x){
+  lm(formula= paste0("`", x, "` ~ gender * compromise"), 
+     data= d, na.action = na.omit)})
+
+for(i in 1:length(depVarList)){
+  if(i==1){
+    m <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
+      filter(factor=="gender") %>%
+      select(AME, lower, upper) %>%
+      mutate(y = depVarList[i])
+  }
+  else{
+    tmp <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
+      filter(factor=="gender") %>%
+      select(AME, lower, upper) %>%
+      mutate(y = depVarList[i])
+    m <- m %>%
+      add_case(tmp)
+  }
+}
+```
 
@@
 
+I test the _migration hypothesis_ using Equation \ref{eq:h2} and the code chunk below.
+The coefficient of $\beta_{1}$ denotes the difference in the evaluation of politicians with and without a migration background.
+If $\beta_{1}$ is negative and statistically siginificant, the _migration hypothesis_ will be confirmed.
+The coefficient of $\beta_{2}$ denotes the difference in the evaluation of politicians who do and do not strike a comprmise.
+The coefficient of $\beta_{3}$ is the interaction of the  $\beta_{1}$ and  $\beta_{2}$.
+If the Average Marginal Effect of $\beta_{1}$ is negative and statistically siginificant when $\beta_{2} = 1$ (i.e. politician stroke a compromise), the _migration hypothesis_ will be confirmed.
+
+\begin{equation}\label{eq:h2}
+  \hat{Y} = \beta_{0} + \beta_{1}Migration Background + \beta_{2}Compromise + \beta_{3}Compromise * Migration Background + \varepsilon
+\end{equation}
+
+```{r h2, eval = FALSE, echo = TRUE}
+df <- d %>%
+  mutate(migration = recode(name, 
+                         `Rachid Amezian` = 1,
+                         `Rachida Amezian` = 1,
+                         .default = 0)) %>%
+  select(PT1:PT4, migration, compromise)
+
+depVarList <- setdiff(colnames(df), c("migration", "compromise"))
+allModels <- lapply(depVarList, function(x){
+  lm(formula= paste0("`", x, "` ~ migration * compromise"), 
+     data= d, na.action = na.omit)})
+
+for(i in 1:length(depVarList)){
+  if(i==1){
+    m <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
+      filter(factor=="migration") %>%
+      select(AME, lower, upper) %>%
+      mutate(y = depVarList[i])
+  }
+  else{
+    tmp <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
+      filter(factor=="migration") %>%
+      select(AME, lower, upper) %>%
+      mutate(y = depVarList[i])
+    m <- m %>%
+      add_case(tmp)
+  }
+}
+```
+
 ## Hypothesis 3
+
+I test the _intersection hypothesis_ using Equation \ref{eq:h3} and the code chunk below.
+The coefficient of $\beta_{1}$ denotes the difference in the evaluation of female politicians with a migration background and the other politicians.
+If $\beta_{1}$ is negative and statistically siginificant, the _gender hypothesis_ will be confirmed.
+The coefficient of $\beta_{2}$ denotes the difference in the evaluation of politicians who do and do not strike a comprmise.
+The coefficient of $\beta_{3}$ is the interaction of the  $\beta_{1}$ and  $\beta_{2}$.
+If the Average Marginal Effect of $\beta_{1}$ is negative and statistically siginificant when $\beta_{2} = 1$ (i.e. politician stroke a compromise), the _intersection hypothesis_ will be confirmed.
+
+\begin{equation}\label{eq:h3}
+  \hat{Y} =\beta_{0} + \beta_{1}Intersection + \beta_{2}Compromise + \beta_{3}Compromise * Intersection + \varepsilon
+\end{equation}
+
+```{r h3, eval = FALSE, echo = TRUE}
+df <- d %>%
+  mutate(intersection = recode(name, 
+                         `Rachida Amezian` = 1,
+                         .default = 0)) %>%
+  select(PT1:PT4, intersection, compromise)
+
+depVarList <- setdiff(colnames(df), c("intersection", "compromise"))
+allModels <- lapply(depVarList, function(x){
+  lm(formula= paste0("`", x, "` ~ intersection * compromise"), 
+     data= d, na.action = na.omit)})
+
+for(i in 1:length(depVarList)){
+  if(i==1){
+    m <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
+      filter(factor=="intersection") %>%
+      select(AME, lower, upper) %>%
+      mutate(y = depVarList[i])
+  }
+  else{
+    tmp <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
+      filter(factor=="intersection") %>%
+      select(AME, lower, upper) %>%
+      mutate(y = depVarList[i])
+    m <- m %>%
+      add_case(tmp)
+  }
+}
+```
+
+## Pooled Data
+Using the pooled data we will estimate a within groups fixed effects model. 
+$Y\hat{Y}_{r, i, t}$ in Equation \ref{eq:pooled} denotes  the  evaluation  of  a politician of respondent $r$, during issue $i$ and at experimental round $t$ -- ranging from round 1 to round 4.
+$\alpha_{i}$ is the issue specific intercept, and $\gamma_{t}$ is the experimental round specific intercept.  
+The standard errors are clustered at the individual level.  
+If the Average Marginal Effect of $\beta_{1}$ is negative and statistically siginificant when $\beta_{2} = 1$ (i.e. politician stroke a compromise), the _intersection hypothesis_ will be confirmed.
+
+\begin{equation}\label{eq:pooled}
+    \hat{Y}_{r, i, t} =\beta_{0} + \beta_{1}Intersection_{r, i, t} + \beta_{2}Compromise + \beta_{3}Compromise * Intersection + \alpha_{i} + \gamma_{t} + \varepsilon_{r, i, t}
+\end{equation}
+
+## Statistical Significance
+All the hypotheses are directional, and therefore all of the tests will be one-tailed.
+I will use an $\alpha$-value of `0.05` as the value for statistical significance in all models above.
 

### 2021-04-21 docs/pap/compromise-punishment-pap.Rmd
add updated pap

@@
           thresholds = c(m = 0.05))[[1]] 
-
-balanced <- balanced %>%
-  mutate(variable = c("Immigration (%)", "Immigration", "Defense", "Education", "Sexism",
-                      "Ideology", "Poltical Efficacy", "COVID-19",
-                      "Gender: Male", "Age", "Education: Middle", "Education: High",
-                      "Region: West", "Region: North", "Region: East", "Region: South",
-                      "Little Urban", "Moderatly Urban", "Highly Urban", 
-                      "Very Highly Urban", "Migration Background", "Bij1","CDA",
-                      "ChristenUnie", "D66", "Denk", "Forum for Democracy",
-                      "GroenLinks", "JA21", "PvdA", "Animal Rights Party", "PVV", 
-                      "SGP", "SP", "VOLT","VVD", "50Plus Party", "Employment",
-                      "Income"),
-         variable = factor(variable,
-                           levels = c("Immigration (%)", "Immigration", "Defense",
-                                      "Education", "Sexism", "Ideology", 
-                                      "Poltical Efficacy","COVID-19", 
-                                      "Gender: Male", "Age", "Education: Middle",
-                                      "Education: High", "Region: West", "Region: North",
-                                      "Region: East", "Region: South",
-                                      "Little Urban", "Moderatly Urban", "Highly Urban",
-                                      "Very Highly Urban", "Migration Background",
-                                      "Bij1","CDA", "ChristenUnie", "D66", "Denk", 
-                                      "Forum for Democracy", "GroenLinks", "JA21", 
-                                      "PvdA", "Animal Rights Party", "PVV", 
-                                      "SGP", "SP", "VOLT","VVD", "50Plus Party",
-                                      "Employment", "Income")),
-         difference = Diff.Un,2) %>%
-  select(variable, difference) %>%
-  ggplot(aes(x = variable, y = difference)) +
-  geom_point(size = 3, colour = "gray55") +
-  theme_bw() +
-  labs(x="", y= "Standardized Mean Differences") +
-  ggtitle("Covariate Balance") +
-  theme(plot.title = element_text(hjust = 0.5)) +
-  geom_hline(yintercept = 0) +
-  geom_hline(yintercept = 0.05, linetype = "dashed") +
-  geom_hline(yintercept = -0.05, linetype = "dashed") +
-  coord_flip()
 ```
@@
 
+```{r fake-data, eval = FALSE}
+
+df <- tibble(gender = sample(c(0,1),100, replace = T),
+             compromise = sample(c(0,1),100, replace = T),
+             PT1 = sample(c(0,10),100, replace = T),
+             PT2 = sample(c(0,10),100, replace = T),
+             PT3 = sample(c(0,10),100, replace = T),
+             PT4 = sample(c(0,10),100, replace = T))
+```
+
 ```{r h1, eval = FALSE, echo = TRUE}
@@
   lm(formula= paste0("`", x, "` ~ gender * compromise"), 
-     data= d, na.action = na.omit)})
+     data= df, na.action = na.omit)})
 
@@
       filter(factor=="gender") %>%
-      select(AME, lower, upper) %>%
-      mutate(y = depVarList[i])
+      mutate(y = depVarList[i],
+             lower = AME - (1.645 * SE),
+             upper = AME + (1.645 * SE)) %>%
+      select(AME, upper, lower, y)
+
   }
@@
       filter(factor=="gender") %>%
-      select(AME, lower, upper) %>%
-      mutate(y = depVarList[i])
+      mutate(y = depVarList[i],
+             lower = AME - (1.645 * SE),
+             upper = AME + (1.645 * SE)) %>%
+      select(AME, upper, lower, y)
     m <- m %>%
@@
       filter(factor=="migration") %>%
-      select(AME, lower, upper) %>%
-      mutate(y = depVarList[i])
+      mutate(y = depVarList[i],
+             lower = AME - (1.645 * SE),
+             upper = AME + (1.645 * SE)) %>%
+      select(AME, upper, lower, y)
   }
@@
       filter(factor=="migration") %>%
-      select(AME, lower, upper) %>%
-      mutate(y = depVarList[i])
+      mutate(y = depVarList[i],
+             lower = AME - (1.645 * SE),
+             upper = AME + (1.645 * SE)) %>%
+      select(AME, upper, lower, y)
     m <- m %>%
@@
       filter(factor=="intersection") %>%
-      select(AME, lower, upper) %>%
-      mutate(y = depVarList[i])
+      mutate(y = depVarList[i],
+             lower = AME - (1.645 * SE),
+             upper = AME + (1.645 * SE)) %>%
+      select(AME, upper, lower, y)
   }
@@
       filter(factor=="intersection") %>%
-      select(AME, lower, upper) %>%
-      mutate(y = depVarList[i])
+      mutate(y = depVarList[i],
+             lower = AME - (1.645 * SE),
+             upper = AME + (1.645 * SE)) %>%
+      select(AME, upper, lower, y)
     m <- m %>%

### 2021-04-22 docs/pap/compromise-punishment-pap.Rmd
update pap

@@
 ---
-title: "Pre-Analysis Plan: Who Bends and Who Breaks? Experimental Evidence for Conditions Affecting Voters' Evaluations of Politicians Striking Compromises"
+title: "Pre-Analysis Plan: Bend or Break? Experimental Evidence of Voters' Punishment for Striking Political Compromises"
 date: "`r format(Sys.time(), '%d %B, %Y - %X (%Z)')`"
@@
 ```{r h1, eval = FALSE, echo = TRUE}
+source(here::here("src/lib/functions.R"))
+
 df <- d %>% select(PT1:PT4, gender, compromise)
-
-depVarList <- setdiff(colnames(df), c("gender", "compromise"))
-allModels <- lapply(depVarList, function(x){
-  lm(formula= paste0("`", x, "` ~ gender * compromise"), 
-     data= df, na.action = na.omit)})
-
-for(i in 1:length(depVarList)){
-  if(i==1){
-    m <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
-      filter(factor=="gender") %>%
-      mutate(y = depVarList[i],
-             lower = AME - (1.645 * SE),
-             upper = AME + (1.645 * SE)) %>%
-      select(AME, upper, lower, y)
-
-  }
-  else{
-    tmp <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
-      filter(factor=="gender") %>%
-      mutate(y = depVarList[i],
-             lower = AME - (1.645 * SE),
-             upper = AME + (1.645 * SE)) %>%
-      select(AME, upper, lower, y)
-    m <- m %>%
-      add_case(tmp)
-  }
-}
+h1 <- regression(data = df, a = gender, b = compromise)
 ```
@@
 
-depVarList <- setdiff(colnames(df), c("migration", "compromise"))
-allModels <- lapply(depVarList, function(x){
-  lm(formula= paste0("`", x, "` ~ migration * compromise"), 
-     data= d, na.action = na.omit)})
-
-for(i in 1:length(depVarList)){
-  if(i==1){
-    m <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
-      filter(factor=="migration") %>%
-      mutate(y = depVarList[i],
-             lower = AME - (1.645 * SE),
-             upper = AME + (1.645 * SE)) %>%
-      select(AME, upper, lower, y)
-  }
-  else{
-    tmp <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
-      filter(factor=="migration") %>%
-      mutate(y = depVarList[i],
-             lower = AME - (1.645 * SE),
-             upper = AME + (1.645 * SE)) %>%
-      select(AME, upper, lower, y)
-    m <- m %>%
-      add_case(tmp)
-  }
-}
+h2 <- regression(data = df, a = migration, b = compromise)
 ```
@@
 
-depVarList <- setdiff(colnames(df), c("intersection", "compromise"))
-allModels <- lapply(depVarList, function(x){
-  lm(formula= paste0("`", x, "` ~ intersection * compromise"), 
-     data= d, na.action = na.omit)})
-
-for(i in 1:length(depVarList)){
-  if(i==1){
-    m <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
-      filter(factor=="intersection") %>%
-      mutate(y = depVarList[i],
-             lower = AME - (1.645 * SE),
-             upper = AME + (1.645 * SE)) %>%
-      select(AME, upper, lower, y)
-  }
-  else{
-    tmp <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
-      filter(factor=="intersection") %>%
-      mutate(y = depVarList[i],
-             lower = AME - (1.645 * SE),
-             upper = AME + (1.645 * SE)) %>%
-      select(AME, upper, lower, y)
-    m <- m %>%
-      add_case(tmp)
-  }
-}
+h3 <- regression(data = df, a = intersection, b = compromise)
 ```
@@
 \end{equation}
+
+```{r pooled, echo = TRUE, eval = FALSE}
+h3_p <- pooled_regression(data = df, a = intersection, b = compromise, c = issues)
+```
 

### 2021-04-22 src/lib/functions.R

@@ -4,3 +4,63 @@ library(qualtRics)
 library(DeclareDesign)
 library(ggpubr)
 library(scales)
+library(margins)
+library(lme4)
+
+regression <- function(data, a, b){
+  
+  depVarList <- data %>% select(matches("PT[0-9]"))
+  indepVarList <- data %>% select(a, b) 
+  allModels <- apply(depVarList,2,function(xl)lm(xl ~ a*b, data= indepVarList))
+  depVarList <- data %>% select(matches("PT[0-9]")) %>% colnames()
+  
+  for(i in 1:length(depVarList)){
+    if(i==1){
+      m <- summary(margins(allModels[[i]]), at = list(b = 1))[2,] %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.645 * SE),
+               upper = AME + (1.645 * SE)) %>%
+        select(AME, upper, lower, y)
+    }
+    else{
+      tmp <- summary(margins(allModels[[i]]), at = list(b = 1))[2,] %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.645 * SE),
+               upper = AME + (1.645 * SE)) %>%
+        select(AME, upper, lower, y)
+      m <- m %>%
+        add_case(tmp)
+      
+    }
+  }
+  return(m)
+}
+pooled_regression <- function(data, a, b, c){
+  
+  depVarList <- data %>% select(matches("PT[0-9]"))
+  indepVarList <- data %>% select(a, b, c)
+  allModels <- apply(depVarList,2,function(xl)lmer(xl ~ a * b + (1 | c),data= indepVarList))
+  
+  depVarList <- data %>% select(matches("PT[0-9]")) %>% colnames()
+  
+  for(i in 1:length(depVarList)){
+    if(i==1){
+      m <- summary(margins(allModels[[i]]), at = list(b = 1))[2,] %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.645 * SE),
+               upper = AME + (1.645 * SE)) %>%
+        select(AME, upper, lower, y)
+    }
+    else{
+      tmp <- summary(margins(allModels[[i]]), at = list(b = 1))[2,] %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.645 * SE),
+               upper = AME + (1.645 * SE)) %>%
+        select(AME, upper, lower, y)
+      m <- m %>%
+        add_case(tmp)
+      
+    }
+  }
+  return(m)
+}

### 2021-04-22 docs/pap/compromise-punishment-pap.Rmd
finalize pap

@@
 
-**Gender hypothesis** (_H1_):  Women politicians are evaluated lower when striking a political compromise compared to men politicians.
+**Gender hypothesis** (_H1a_):  Women politicians are evaluated lower when striking a political compromise compared to men politicians.
+
+**Gender hypothesis** (_H1b_):  Women politicians are evaluated lower when not striking a political compromise compared to men politicians.
 
@@
 
-**Intersection hypothesis** (_H3_): Women politician with a migration background are evaluated lower when striking a political compromise compared to men politicians without a migration background.
+**Intersection hypothesis** (_H3a_): Women politician with a migration background are evaluated lower when striking a political compromise compared to men politicians without a migration background.
+
+**Intersection hypothesis** (_H3b_): Women politician with a migration background are evaluated lower when not striking a political compromise compared to men politicians without a migration background.
 

### 2021-04-23 src/analysis/Analysis.Rmd
add scripts for analyses

---
title: 'Analyses'
author: 
output: 
  github_document:
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r "setup", include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center",
                      fig.path=('../../report/figures/'))
library(printr)
options(digits = 2)
library(rmarkdown)
library(here)
```

# Scripts
- [Required Packages &amp; Reproducibility](#required-packages-&amp;-reproducibility)
- [Analyses](#analyses)

# Required Packages &amp; Reproducibility
```{r "env", message=FALSE, warning=F}
rm(list=ls())
source(here("src/lib/functions.R"))
```

# Analyses

```{r "data for analyses"}
load(here("data/intermediate/cleaned_data.RData"))
source(here("src/analysis/data-for-analyses.R"))
```

Next, we automatically extract a `.md` file for the online appendix, as well as a  latex table for the manuscript. 
We are using jinja2 template [src/analysis/table_descriptives.tex.j2](table.tex.j2) which is called with a json string containing the data.
To replicate, make sure `env/bin/pip install -U j2cli` is installed via your command line.

```{r "Table with Descriptives"}
source(here("src/analysis/descriptive-information-overview.R"))
table2 <- knitr::kable(descr, digits=2)
fn <- here("report/figures/table_descriptives.md")
cat("# Table: Descriptive Information of Variables under Study \n\n", file=fn)
cat(table2, file=fn, sep="\n", append=T)

methodnames <- setNames(as.list(descr$name), descr$name)
table <- purrr::map(descr, .f= ".") 
#render_j2("src/analysis/table_descriptives.tex.j2", "report/figures/table_descriptives.tex", data=list(data=table, methods=methodnames))
```

## Gender Hypothesis 
```{r "h1", fig.align="center", fig.height=8, fig.width=8, eval = F}
source(here("src/analysis/h1.R"))
```

## Migration Hypothesis
```{r "h2", fig.align="center", fig.height=8, fig.width=8, eval = F}
source(here("src/analysis/h2.R"))
```

## Intersection Hypothesis
```{r "h3", fig.align="center", fig.height=8, fig.width=8, , eval = F}
source(here("src/analysis/h3.R"))
```

## Intersection Hypothesis -- Pooled
```{r "h3-pooled", fig.align="center", fig.height=8, fig.width=8, , eval = F}
source(here("src/analysis/h3-pooled.R"))
```

### 2021-04-23 src/analysis/data-for-analyses.R

@@ -1,0 +1,70 @@
+d <- d %>%
+  mutate(`PT-D1` = round((`PT-D1_1` + `PT-D1_2` + `PT-D1_3` + `PT-D1_4` + `PT-D1_5` + `PT-D1_6`)/6, 0),
+         `PT-E1` = round((`PT-E1_1` + `PT-E1_2` + `PT-E1_3` + `PT-E1_4` + `PT-E1_5` + `PT-E1_6`)/6, 0),
+         `PT-C1` = round((`PT-C1_1` + `PT-C1_2` + `PT-C1_3` + `PT-C1_4` + `PT-C1_5` + `PT-C1_6`)/6, 0),
+         `PT-I1` = round((`PT-I1_1` + `PT-I1_2` + `PT-I1_3` + `PT-I1_4` + `PT-I1_5` + `PT-I1_6`)/6, 0),
+         PreT5 = round((PreT5_1 + PreT5_2 + PreT5_3 + PreT5_4)/4,0),
+         PreT7 = round((PreT7_1 + PreT7_2 + PreT7_3 + PreT7_4 + PreT7_5 + PreT7_6 + PreT7_7)/7,0)) %>%
+  pivot_longer(cols = c(`name-D`, `name-I`, `name-E`, `name-C`),
+               values_to = "name",
+               names_to = "issue") %>%
+  drop_na(name) %>%
+  mutate(issue = recode(issue, 
+                        `name-C` = "COVID-19",
+                        `name-D` = "Defense",
+                        `name-E` = "Education",
+                        `name-I` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D1`, `PT-E1`, `PT-C1`, `PT-I1`),
+               values_to = "PT1",
+               names_to = "issue1") %>%
+  drop_na(PT1) %>%
+  mutate(issue1 = recode(issue1, 
+                        `PT-C1` = "COVID-19",
+                        `PT-D1` = "Defense",
+                        `PT-E1` = "Education",
+                        `PT-I1` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D2`, `PT-E2`, `PT-C2`, `PT-I2`),
+               values_to = "PT2",
+               names_to = "issue2") %>%
+  mutate(issue2 = recode(issue2, 
+                        `PT-C2` = "COVID-19",
+                        `PT-D2` = "Defense",
+                        `PT-E2` = "Education",
+                        `PT-I2` = "Immigration")) %>%
[…]

### 2021-04-23 src/analysis/descriptive-information-overview.R

@@ -1,0 +1,50 @@
+descr <- d %>%
+  select(-id, -issue) %>%
+  mutate(F1 = recode(F1, `999` = 0, `2` = 0)) %>%
+  pivot_longer(cols = everything()) %>%
+  group_by(name) %>%
+  summarise(means = mean(value, na.rm = T),
+            stdev = sd(value, na.rm = T),
+            minvalue = min(value, na.rm = T),
+            maxvalue = max(value, na.rm = T)) %>%
+  ungroup() %>%
+  mutate(name = recode(name,
+                       `F1` = "Gender",
+                       `F2` = "Age",
+                       `F3` = "Education",
+                       `F4` = "Urbanness",
+                       `F5` = "Migration Background",
+                       `F6`  = "Party Preference",
+                       `F7`  = "Employment",
+                       `F8`  = "Income",
+                       `PreT1`  = "Immigration (%)",
+                       `PreT2`  = "Position: Immigration",
+                       `PreT3`  = "Position: Defense",
+                       `PreT4`  = "Position: Education",
+                       `PreT5`  = "Attitude: Women in Politics",
+                       `PreT6`  = "Ideology",
+                       `PreT7` = "Political Efficacy",
+                       `PreT8` = "Position: COVID-19",
+                       `gender` = "Treatment: Gender Politician",
+                       `immigration` = "Treatment: Immigration Background Politician",
+                       `intersection` = "Treatment: Women Politician with Immigration Background",
+                       `compromise` = "Treatment: Striking Compromise",
+                       `PT1` = "DV: Trait Evaluation",
+                       `PT2` = "DV: Favorability",
+                       `PT3` = "DV: Representation",
+                       `PT4` = "DV: Career Prospects"),
+         name = factor(name,
+                         levels = c("DV: Trait Evaluation","DV: Favorability",
+                                   "DV: Representation", "DV: Career Prospects",
+                                   "Treatment: Gender Politician",
+                                   "Treatment: Immigration Background Politician",
+                                   "Treatment: Women Politician with Immigration Background",
+                                   "Treatment: Striking Compromise",
+                                   "Immigration (%)","Position: Immigration",
+                                   "Position: Defense", "Position: Education",
+                                   "Position: COVID-19", "Attitude: Women in Politics",
+                                   "Ideology","Political Efficacy",
+                                   "Gender","Age","Education","Urbanness",
+                                   "Migration Background","Party Preference",
+                                   "Employment", "Income")))
+

### 2021-04-23 src/analysis/h1.R

@@ -1,0 +1,63 @@
+# H1a & H1b
+issues <- unique(d$issue)
+for(i in 1:length(issues)){
+  df <- d %>% select(a = gender, compromise, PT1:PT4, issue) %>%
+    filter(issue == issues[i]) %>%
+    select(-issue)
+  if(i==1){
+    h1a <- regression(df, a, compromise, 1) %>%
+    mutate(issue = issues[i])
+  }  
+  else{
+    tmp <- regression(df, a, compromise, 1) %>%
+      mutate(issue = issues[i])
+    h1a <- h1a %>% add_case(tmp)
+  }
+}
+
+for(i in 1:length(issues)){
+  df <- d %>% select(a = gender, compromise, PT1:PT4, issue) %>%
+    filter(issue == issues[i]) %>%
+    select(-issue)
+  if(i==1){
+    h1b <- regression(df, a, compromise, 0) %>%
+      mutate(issue = issues[i])
+  }  
+  else{
+    tmp <- regression(df, a, compromise, 0) %>%
+      mutate(issue = issues[i])
+    h1b <- h1b %>% add_case(tmp)
+  }
+}
+
+h1a %>% add_case(h1b) %>%
+  mutate(y = recode(y,
+                    `PT1` = "DV: Trait Evaluation",
+                    `PT2` = "DV: Favorability",
+                    `PT3` = "DV: Representation",
+                    `PT4` = "DV: Career Prospects"),
+         n = recode(n,
+                    `1` = "Compromise (H1a)",
+                    `0` = "No Compromise (H1b)"),
+         id = 1:(dim(h1a)[1]+dim(h1b)[1])) %>%
+  ggplot(aes(x = reorder(id, AME), 
+             y = AME,
+             color = y,
+             ymin = lower,
+             ymax = upper)) +
+  geom_point(position = ) + geom_errorbar(width = 0) +
+  theme_bw() +
+  labs(x = "", y = "Average Marginal Effects of Being a Women Politician") +
+  facet_grid(issue~n, scales = "free_y") +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5),
+        axis.title.y=element_blank(),
+        axis.text.y=element_blank(),
+        legend.position="bottom",
+        legend.title = element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.ticks.y = element_blank()) +
[…]

### 2021-04-23 src/analysis/h2.R

@@ -1,0 +1,48 @@
+## H2
+issues <- unique(d$issue)
+for(i in 1:length(issues)){
+  df <- d %>% select(a = immigration, compromise, PT1:PT4, issue) %>%
+    filter(issue == issues[i]) %>%
+    select(-issue)
+  if(i==1){
+    h2 <- regression(df, a, compromise, 1) %>%
+      mutate(issue = issues[i])
+  }  
+  else{
+    tmp <- regression(df, a, compromise, 1) %>%
+      mutate(issue = issues[i])
+    h2 <- h2 %>% add_case(tmp)
+  }
+}
+
+h2 %>%
+  mutate(y = recode(y,
+                    `PT1` = "DV: Trait Evaluation",
+                    `PT2` = "DV: Favorability",
+                    `PT3` = "DV: Representation",
+                    `PT4` = "DV: Career Prospects"),
+         n = recode(n,
+                    `1` = "Compromise (H2)",
+                    `0` = "No Compromise (H1b)"),
+         id = 1:(dim(h1a)[1]+dim(h1b)[1])) %>%
+  ggplot(aes(x = reorder(id, AME), 
+             y = AME,
+             color = y,
+             ymin = lower,
+             ymax = upper)) +
+  geom_point(position = ) + geom_errorbar(width = 0) +
+  theme_bw() +
+  labs(x = "", y = "Average Marginal Effects of Being a Politician with a Migration Background") +
+  facet_grid(issue~n, scales = "free_y") +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5),
+        axis.title.y=element_blank(),
+        axis.text.y=element_blank(),
+        legend.position="bottom",
+        legend.title = element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.ticks.y = element_blank()) +
+  scale_color_viridis_d() +
+  geom_hline(yintercept = 0, size = .2, linetype = "dashed") +
+  guides(color=guide_legend(nrow=1,byrow=TRUE)) +
+  coord_flip()

### 2021-04-23 src/analysis/h3-pooled.R

@@ -1,0 +1,38 @@
+## H3
+df <- d %>% select(a = intersection, compromise, PT1:PT4, issue)
+h3ap <- pooled_regression(df, a, compromise, issue, 1) %>%
+  mutate(n = 1)
+h3bp <- pooled_regression(df, a, compromise, issue, 0) %>%
+  mutate(n = 0)
+
+h3ap %>% add_case(h3bp) %>%
+  mutate(y = recode(y,
+                    `PT1` = "DV: Trait Evaluation",
+                    `PT2` = "DV: Favorability",
+                    `PT3` = "DV: Representation",
+                    `PT4` = "DV: Career Prospects"),
+         n = recode(n,
+                    `1` = "Compromise (H3a - Pooled)",
+                    `0` = "No Compromise (H3b - Pooled)"),
+         id = 1:(dim(h3ap)[1]+dim(h3bp)[1])) %>%
+  ggplot(aes(x = reorder(id, AME), 
+             y = AME,
+             color = y,
+             ymin = lower,
+             ymax = upper)) +
+  geom_point(position = ) + geom_errorbar(width = 0) +
+  theme_bw() +
+  labs(x = "", y = "Average Marginal Effects of Being a Women Politician with a Migration Background") +
+  facet_grid(.~n, scales = "free_y") +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5),
+        axis.title.y=element_blank(),
+        axis.text.y=element_blank(),
+        legend.position="bottom",
+        legend.title = element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.ticks.y = element_blank()) +
+  scale_color_viridis_d() +
+  geom_hline(yintercept = 0, size = .2, linetype = "dashed") +
+  guides(color=guide_legend(nrow=1,byrow=TRUE)) +
+  coord_flip()

### 2021-04-23 src/analysis/h3.R

@@ -1,0 +1,63 @@
+## H3
+issues <- unique(d$issue)
+for(i in 1:length(issues)){
+  df <- d %>% select(a = intersection, compromise, PT1:PT4, issue) %>%
+    filter(issue == issues[i]) %>%
+    select(-issue)
+  if(i==1){
+    h3a <- regression(df, a, compromise, 1) %>%
+      mutate(issue = issues[i])
+  }  
+  else{
+    tmp <- regression(df, a, compromise, 1) %>%
+      mutate(issue = issues[i])
+    h3a <- h3a %>% add_case(tmp)
+  }
+}
+
+for(i in 1:length(issues)){
+  df <- d %>% select(a = intersection, compromise, PT1:PT4, issue) %>%
+    filter(issue == issues[i]) %>%
+    select(-issue)
+  if(i==1){
+    h3b <- regression(df, a, compromise, 0) %>%
+      mutate(issue = issues[i])
+  }  
+  else{
+    tmp <- regression(df, a, compromise, 0) %>%
+      mutate(issue = issues[i])
+    h3b <- h3b %>% add_case(tmp)
+  }
+}
+
+h3a %>% add_case(h3b) %>%
+  mutate(y = recode(y,
+                    `PT1` = "DV: Trait Evaluation",
+                    `PT2` = "DV: Favorability",
+                    `PT3` = "DV: Representation",
+                    `PT4` = "DV: Career Prospects"),
+         n = recode(n,
+                    `1` = "Compromise (H3a)",
+                    `0` = "No Compromise (H3b)"),
+         id = 1:(dim(h3a)[1]+dim(h3b)[1])) %>%
+  ggplot(aes(x = reorder(id, AME), 
+             y = AME,
+             color = y,
+             ymin = lower,
+             ymax = upper)) +
+  geom_point(position = ) + geom_errorbar(width = 0) +
+  theme_bw() +
+  labs(x = "", y = "Average Marginal Effects of Being a Women Politician with a Migration Background") +
+  facet_grid(issue~n, scales = "free_y") +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5),
+        axis.title.y=element_blank(),
+        axis.text.y=element_blank(),
+        legend.position="bottom",
+        legend.title = element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.ticks.y = element_blank()) +
[…]

### 2021-04-23 src/lib/functions.R

@@ -7,27 +7,29 @@ library(scales)
 library(margins)
 library(lme4)
 
-regression <- function(data, a, b){
+regression <- function(df, a, compromise, n){
   
-  depVarList <- data %>% select(matches("PT[0-9]"))
-  indepVarList <- data %>% select(a, b) 
-  allModels <- apply(depVarList,2,function(xl)lm(xl ~ a*b, data= indepVarList))
-  depVarList <- data %>% select(matches("PT[0-9]")) %>% colnames()
+  depVarList <- df %>% select(matches("PT[0-9]"))
+  indepVarList <- df %>% select(a, compromise) 
+  allModels <- apply(depVarList,2,function(xl)lm(xl ~ a * compromise, data= indepVarList))
+  depVarList <- df %>% select(matches("PT[0-9]")) %>% colnames()
   
   for(i in 1:length(depVarList)){
     if(i==1){
-      m <- summary(margins(allModels[[i]]), at = list(b = 1))[2,] %>%
+      m <- summary(margins(allModels[[i]]), at = list(compromise = n))[2,] %>%
         mutate(y = depVarList[i],
+               n = n,
                lower = AME - (1.645 * SE),
                upper = AME + (1.645 * SE)) %>%
-        select(AME, upper, lower, y)
+        select(AME, upper, lower, y, n)
     }
     else{
-      tmp <- summary(margins(allModels[[i]]), at = list(b = 1))[2,] %>%
+      tmp <- summary(margins(allModels[[i]]), at = list(compromise = n))[2,] %>%
         mutate(y = depVarList[i],
+               n = n,
                lower = AME - (1.645 * SE),
                upper = AME + (1.645 * SE)) %>%
-        select(AME, upper, lower, y)
+        select(AME, upper, lower, y, n)
       m <- m %>%
         add_case(tmp)
       
@@ -35,28 +37,30 @@ regression <- function(data, a, b){
   }
   return(m)
 }
-pooled_regression <- function(data, a, b, c){
+
+pooled_regression <- function(df, a, compromise, issue, n){
   
-  depVarList <- data %>% select(matches("PT[0-9]"))
-  indepVarList <- data %>% select(a, b, c)
-  allModels <- apply(depVarList,2,function(xl)lmer(xl ~ a * b + (1 | c),data= indepVarList))
-  
-  depVarList <- data %>% select(matches("PT[0-9]")) %>% colnames()
+  depVarList <- df %>% select(matches("PT[0-9]"))
[…]

### 2021-04-23 src/analysis/Analysis.Rmd
add scripts for analyses

@@
 - [Analyses](#analyses)
+  - [Balance Checks](#balance-checks)
+  - [Gender Hypothesis](#gender-hypothesis)
+  - [Migration Hypothesis](#migration-hypothesis)
+  - [Intersection Hypothesis](#intersection-hypothesis)
+  - [Intersection Hypothesis -- Pooled](#intersection-hypothesis--pooled)
 
@@
 # Analyses
-
 ```{r "data for analyses"}
@@
 
+## Balance Checks
+```{r "balance-checks", eval = F}
+source(here("src/analysis/balance-test.R"))
+```
+
 ## Gender Hypothesis 

### 2021-04-24 src/lib/functions.R
adapt compendium structure

@@ -68,3 +68,9 @@ pooled_regression <- function(df, a, compromise, issue, n){
   }
   return(m)
 }
+
+#' Render a template using jinja2 command line tool
+render_j2 = function(template, output, data, auto_unbox=TRUE, na="string") {
+  data = jsonlite::toJSON(data, pretty=TRUE, auto_unbox=auto_unbox, na=na)
+  system(glue::glue("env/bin/j2 --format json {template} -o {output}"), input=data)
+}

### 2021-04-24 src/analysis/Analysis.Rmd
update analysis file

@@
 table2 <- knitr::kable(descr, digits=2)
-fn <- here("report/figures/table_descriptives.md")
+fn <- here("report/figures/table_descriptives.tex")
 cat("# Table: Descriptive Information of Variables under Study \n\n", file=fn)
@@
 ## Intersection Hypothesis
-```{r "h3", fig.align="center", fig.height=8, fig.width=8, , eval = F}
+```{r "h3", fig.align="center", fig.height=8, fig.width=8, eval = F}
 source(here("src/analysis/h3.R"))
@@
 ## Intersection Hypothesis -- Pooled
-```{r "h3-pooled", fig.align="center", fig.height=8, fig.width=8, , eval = F}
+```{r "h3-pooled", fig.align="center", fig.height=8, fig.width=8, eval = F}
 source(here("src/analysis/h3-pooled.R"))
 ```
+
+## Exploration

### 2021-04-24 src/analysis/h2.R

@@ -24,7 +24,7 @@ h2 %>%
          n = recode(n,
                     `1` = "Compromise (H2)",
                     `0` = "No Compromise (H1b)"),
-         id = 1:(dim(h1a)[1]+dim(h1b)[1])) %>%
+         id = 1:(dim(h2)[1])) %>%
   ggplot(aes(x = reorder(id, AME), 
              y = AME,
              color = y,

### 2021-05-01 src/data-processing/prep_data.Rmd
update files with code for visuals

@@
 ```{r "Dependent Variable", echo=F}
+d %>%
+  mutate(`PT-D1` = round((`PT-D1_1` + `PT-D1_2` + `PT-D1_3` + `PT-D1_4` + `PT-D1_5` + `PT-D1_6`)/6, 0),
+         `PT-E1` = round((`PT-E1_1` + `PT-E1_2` + `PT-E1_3` + `PT-E1_4` + `PT-E1_5` + `PT-E1_6`)/6, 0),
+         `PT-C1` = round((`PT-C1_1` + `PT-C1_2` + `PT-C1_3` + `PT-C1_4` + `PT-C1_5` + `PT-C1_6`)/6, 0),
+         `PT-I1` = round((`PT-I1_1` + `PT-I1_2` + `PT-I1_3` + `PT-I1_4` + `PT-I1_5` + `PT-I1_6`)/6, 0),
+         PreT5 = round((PreT5_1 + PreT5_2 + PreT5_3 + PreT5_4)/4,0),
+         PreT7 = round((PreT7_1 + PreT7_2 + PreT7_3 + PreT7_4 + PreT7_5 + PreT7_6 + PreT7_7)/7,0)) %>%
+  pivot_longer(cols = c(`name-D`, `name-I`, `name-E`, `name-C`),
+               values_to = "name",
+               names_to = "issue") %>%
+  drop_na(name) %>%
+  mutate(issue = recode(issue, 
+                        `name-C` = "COVID-19",
+                        `name-D` = "Defense",
+                        `name-E` = "Education",
+                        `name-I` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D1`, `PT-E1`, `PT-C1`, `PT-I1`),
+               values_to = "PT1",
+               names_to = "issue1") %>%
+  drop_na(PT1) %>%
+  mutate(issue1 = recode(issue1, 
+                        `PT-C1` = "COVID-19",
+                        `PT-D1` = "Defense",
+                        `PT-E1` = "Education",
+                        `PT-I1` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D2`, `PT-E2`, `PT-C2`, `PT-I2`),
+               values_to = "PT2",
+               names_to = "issue2") %>%
+  mutate(issue2 = recode(issue2, 
+                        `PT-C2` = "COVID-19",
+                        `PT-D2` = "Defense",
+                        `PT-E2` = "Education",
+                        `PT-I2` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D3`, `PT-E3`, `PT-C3`, `PT-I3`),
+               values_to = "PT3",
+               names_to = "issue3") %>%
+  mutate(issue3 = recode(issue3, 
+                         `PT-C3` = "COVID-19",
+                         `PT-D3` = "Defense",
+                         `PT-E3` = "Education",
+                         `PT-I3` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D4`, `PT-E4`, `PT-C4`, `PT-I4`),
+               values_to = "PT4",
+               names_to = "issue4") %>%
+  mutate(issue4 = recode(issue4, 
+                         `PT-C4` = "COVID-19",
+                         `PT-D4` = "Defense",
+                         `PT-E4` = "Education",
+                         `PT-I4` = "Immigration"),
+        check = if_else(issue == issue1 & issue == issue2 & issue == issue3 & issue == issue4, 1,0)) %>%
+  filter(check == 1) %>%
+  select(PT1, PT2, PT3, PT4, issue = issue1) %>%
+  pivot_longer(cols = PT1:PT4) %>%
+  mutate(name = recode(name,
+                       `PT1` = "DV: Trait Evaluation",
+                       `PT2` = "DV: Favorability",
+                       `PT3` = "DV: Representation",
+                       `PT4` = "DV: Career Prospects")) %>%
+  group_by(issue, name) %>%
+  summarise(means = mean(value, na.rm=T),
+            stdev = sd(value, na.rm=T)) %>%
+  mutate(lower = means - (1.56 * stdev),
+         upper = means + (1.56 * stdev)) %>%
+  ggplot(aes(x = name, y = means, colour = issue,
+             ymin = lower, ymax = upper)) +
+  geom_point(position = position_dodge(.2)) + 
+  geom_errorbar(position = position_dodge(.2), width = 0) +
+  labs(y = "0 (negative) - 10 (positive)", 
+       x = "", title = "Evaluation of Politicians") +
+  geom_hline(yintercept = 5, linetype = "dotted", color = "darkgrey") +
+  theme_minimal() +
+  scale_color_manual(values = c("#0C5BB0CC", "#15983DCC", "#FA6B09CC", "#A1C720CC" )) +
+  coord_flip() +
+  theme(plot.title = element_text(hjust = 0.5),
+        #axis.text.x = element_text(angle=45),
+        legend.position="bottom",
+        legend.title = element_blank()) 
 ```
 
-### Independent Variable
+### Treatment Conditions
 ```{r "Independent Variables", echo=F, message=FALSE, warning=FALSE,fig.width=10, fig.height=10}
 
+d %>%
+  mutate(`PT-D1` = round((`PT-D1_1` + `PT-D1_2` + `PT-D1_3` + `PT-D1_4` + `PT-D1_5` + `PT-D1_6`)/6, 0),
+         `PT-E1` = round((`PT-E1_1` + `PT-E1_2` + `PT-E1_3` + `PT-E1_4` + `PT-E1_5` + `PT-E1_6`)/6, 0),
+         `PT-C1` = round((`PT-C1_1` + `PT-C1_2` + `PT-C1_3` + `PT-C1_4` + `PT-C1_5` + `PT-C1_6`)/6, 0),
+         `PT-I1` = round((`PT-I1_1` + `PT-I1_2` + `PT-I1_3` + `PT-I1_4` + `PT-I1_5` + `PT-I1_6`)/6, 0),
+         PreT5 = round((PreT5_1 + PreT5_2 + PreT5_3 + PreT5_4)/4,0),
+         PreT7 = round((PreT7_1 + PreT7_2 + PreT7_3 + PreT7_4 + PreT7_5 + PreT7_6 + PreT7_7)/7,0)) %>%
+  pivot_longer(cols = c(`name-D`, `name-I`, `name-E`, `name-C`),
+               values_to = "name",
+               names_to = "issue") %>%
+  drop_na(name) %>%
+  mutate(issue = recode(issue, 
+                        `name-C` = "COVID-19",
+                        `name-D` = "Defense",
+                        `name-E` = "Education",
+                        `name-I` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D1`, `PT-E1`, `PT-C1`, `PT-I1`),
+               values_to = "PT1",
+               names_to = "issue1") %>%
+  drop_na(PT1) %>%
+  mutate(issue1 = recode(issue1, 
+                        `PT-C1` = "COVID-19",
+                        `PT-D1` = "Defense",
+                        `PT-E1` = "Education",
+                        `PT-I1` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D2`, `PT-E2`, `PT-C2`, `PT-I2`),
+               values_to = "PT2",
+               names_to = "issue2") %>%
+  mutate(issue2 = recode(issue2, 
+                        `PT-C2` = "COVID-19",
+                        `PT-D2` = "Defense",
+                        `PT-E2` = "Education",
+                        `PT-I2` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D3`, `PT-E3`, `PT-C3`, `PT-I3`),
+               values_to = "PT3",
+               names_to = "issue3") %>%
+  mutate(issue3 = recode(issue3, 
+                         `PT-C3` = "COVID-19",
+                         `PT-D3` = "Defense",
+                         `PT-E3` = "Education",
+                         `PT-I3` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D4`, `PT-E4`, `PT-C4`, `PT-I4`),
+               values_to = "PT4",
+               names_to = "issue4") %>%
+  mutate(issue4 = recode(issue4, 
+                         `PT-C4` = "COVID-19",
+                         `PT-D4` = "Defense",
+                         `PT-E4` = "Education",
+                         `PT-I4` = "Immigration"),
+        check = if_else(issue == issue1 & issue == issue2 & issue == issue3 & issue == issue4, 1,0)) %>%
+  filter(check == 1) %>%
+  mutate(gender = recode(name,
+                         `Karel van der Kleijn` = 0,
+                         `Karin van der Kleijn` = 1,
+                         `Rachid Amezian` = 0,
+                         `Rachida Amezian` = 1),
+         immigration = recode(name,
+                              `Karel van der Kleijn` = 0,
+                              `Karin van der Kleijn` = 0,
+                              `Rachid Amezian` = 1,
+                              `Rachida Amezian` = 1),
+         intersection = recode(name,
+                               `Karel van der Kleijn` = 0,
+                               `Karin van der Kleijn` = 0,
+                               `Rachid Amezian` = 0,
+                               `Rachida Amezian` = 1),
+         compromise = if_else(compromis == "een compromis", "Compromise", "No Compromise"))%>%
+  unite("treatment", c("name", "compromise"), sep = ": ") %>%
+  select(treatment, issue) %>%
+  group_by(issue, treatment) %>%
+  summarise(n = n()) %>%
+  mutate(perc = round(n/sum(n),2),
+         perc2 = paste0(perc*100, "%")) %>%
+  ggplot(aes(x = perc, y = issue, fill = treatment, label = perc2)) +
+  geom_col(position = 'fill') + 
+  geom_text(aes(label=perc2), position = position_fill(vjust=0.5),
+            color = "white", fontface = "bold") +
+  labs(y = "", 
+       x = "", title = "Distribution of Treatments") +
+  scale_x_continuous(labels=scales::percent) +
+  theme_minimal() +
+  scale_fill_manual(values = c("#0C5BB0CC", "#EE0011CC", "#15983DCC", "#EC579ACC", "#FA6B09CC", "#149BEDCC", "#A1C720CC", "#FEC10BCC" )) +
+  theme(plot.title = element_text(hjust = 0.5),
+        legend.position="bottom",
+        legend.title = element_blank()) +
+  guides(fill=guide_legend(ncol=2,byrow=TRUE))
 ```
@@
 
+d %>%
+  mutate(`PT-D1` = round((`PT-D1_1` + `PT-D1_2` + `PT-D1_3` + `PT-D1_4` + `PT-D1_5` + `PT-D1_6`)/6, 0),
+         `PT-E1` = round((`PT-E1_1` + `PT-E1_2` + `PT-E1_3` + `PT-E1_4` + `PT-E1_5` + `PT-E1_6`)/6, 0),
+         `PT-C1` = round((`PT-C1_1` + `PT-C1_2` + `PT-C1_3` + `PT-C1_4` + `PT-C1_5` + `PT-C1_6`)/6, 0),
+         `PT-I1` = round((`PT-I1_1` + `PT-I1_2` + `PT-I1_3` + `PT-I1_4` + `PT-I1_5` + `PT-I1_6`)/6, 0),
+         PreT5 = round((PreT5_1 + PreT5_2 + PreT5_3 + PreT5_4)/4,0),
+         PreT7 = round((PreT7_1 + PreT7_2 + PreT7_3 + PreT7_4 + PreT7_5 + PreT7_6 + PreT7_7)/7,0)) %>%
+  pivot_longer(cols = c(`name-D`, `name-I`, `name-E`, `name-C`),
+               values_to = "name",
+               names_to = "issue") %>%
+  drop_na(name) %>%
+  mutate(issue = recode(issue, 
+                        `name-C` = "COVID-19",
+                        `name-D` = "Defense",
+                        `name-E` = "Education",
+                        `name-I` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D1`, `PT-E1`, `PT-C1`, `PT-I1`),
+               values_to = "PT1",
+               names_to = "issue1") %>%
+  drop_na(PT1) %>%
+  mutate(issue1 = recode(issue1, 
+                        `PT-C1` = "COVID-19",
+                        `PT-D1` = "Defense",
+                        `PT-E1` = "Education",
+                        `PT-I1` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D2`, `PT-E2`, `PT-C2`, `PT-I2`),
+               values_to = "PT2",
+               names_to = "issue2") %>%
+  mutate(issue2 = recode(issue2, 
+                        `PT-C2` = "COVID-19",
+                        `PT-D2` = "Defense",
+                        `PT-E2` = "Education",
+                        `PT-I2` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D3`, `PT-E3`, `PT-C3`, `PT-I3`),
+               values_to = "PT3",
+               names_to = "issue3") %>%
+  mutate(issue3 = recode(issue3, 
+                         `PT-C3` = "COVID-19",
+                         `PT-D3` = "Defense",
+                         `PT-E3` = "Education",
+                         `PT-I3` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D4`, `PT-E4`, `PT-C4`, `PT-I4`),
+               values_to = "PT4",
+               names_to = "issue4") %>%
+  mutate(issue4 = recode(issue4, 
+                         `PT-C4` = "COVID-19",
+                         `PT-D4` = "Defense",
+                         `PT-E4` = "Education",
+                         `PT-I4` = "Immigration"),
+        check = if_else(issue == issue1 & issue == issue2 & issue == issue3 & issue == issue4, 1,0)) %>%
+  filter(check == 1) %>%
+  select(`Gender` = F1,
+         `Age` = F2,
+         #`Education` = F9,
+         `Region`  = F3,
+         `Urbanness`  = F4,
+         `Migration Background`  = F5,
+         `Vote Recall`  = F6,
+         `Job`  = F7,
+         `Income`  = F8,
+         `Percentage - Immigration`  = PreT1,
+         `Position - Immigration`  = PreT2,
+         `Position - Defense`  = PreT3,
+         `Position - Education`  = PreT4,
+         `Attitudes towards Women in Politics`  = PreT5,
+         `Ideology`  = PreT6,
+         `Political Efficacy` = PreT7, 
+         `Position - COVID-19 Policy` = PreT8,
+         `DV: Trait Evaluation` = PT1,
+         `DV: Favorability` = PT2,
+         `DV: Representation` = PT3,
+         `DV: Career Prospects` = PT4) %>%
+  ggcorrmat(
+  type = "robust", # correlation method
+  cor.vars = c(everything()), # a range of variables can be selected
+  colors = c("#0C5BB0CC", "#EC579ACC", "#EE0011CC"),
+  title = "Correlalogram for Variables under Study"
+)
 ```

### 2021-05-01 src/lib/functions.R

@@ -6,6 +6,11 @@ library(ggpubr)
 library(scales)
 library(margins)
 library(lme4)
+library(yarrr)
+library(ggstatsplot)
+
+fig_cols <- piratepal(palette = "basel", 
+             trans = .2)
 
 regression <- function(df, a, compromise, n){
   

### 2021-05-01 src/data-processing/prep_data.Rmd
add scripts for data preparations and visualization

--- 2021-04-14 src/data-processing/prep_data.Rmd
@@
   - [Dependent Variable](#dependent-variable)
-  - [Independent Variable](#independent-variable)
-  - [Control Variables](#control-variables)
+  - [Treatment Conditions](#treatment-conditions)
   - [Correlations Matrix](#correlations-matrix)
@@
 
-## Save Data for Analysis
-```{r "save data"}
-save(d, file = here("data/intermediate/cleaned_data.RData"))
-```
-
 ## Check Missing Values
@@
 
+## Save Data for Analysis
+```{r "save data",eval=FALSE}
+save(d, file = here("data/intermediate/cleaned_data.RData"))
+```
+
 ## Visualization of Data
@@
 ```{r "Dependent Variable", echo=F}
+load(here("data/intermediate/cleaned_data.RData"))
+d %>%
+  mutate(`PT-D1` = round((`PT-D1_1` + `PT-D1_2` + `PT-D1_3` + `PT-D1_4` + `PT-D1_5` + `PT-D1_6`)/6, 0),
+         `PT-E1` = round((`PT-E1_1` + `PT-E1_2` + `PT-E1_3` + `PT-E1_4` + `PT-E1_5` + `PT-E1_6`)/6, 0),
+         `PT-C1` = round((`PT-C1_1` + `PT-C1_2` + `PT-C1_3` + `PT-C1_4` + `PT-C1_5` + `PT-C1_6`)/6, 0),
+         `PT-I1` = round((`PT-I1_1` + `PT-I1_2` + `PT-I1_3` + `PT-I1_4` + `PT-I1_5` + `PT-I1_6`)/6, 0),
+         PreT5 = round((PreT5_1 + PreT5_2 + PreT5_3 + PreT5_4)/4,0),
+         PreT7 = round((PreT7_1 + PreT7_2 + PreT7_3 + PreT7_4 + PreT7_5 + PreT7_6 + PreT7_7)/7,0)) %>%
+  pivot_longer(cols = c(`name-D`, `name-I`, `name-E`, `name-C`),
+               values_to = "name",
+               names_to = "issue") %>%
+  drop_na(name) %>%
+  mutate(issue = recode(issue, 
+                        `name-C` = "COVID-19",
+                        `name-D` = "Defense",
+                        `name-E` = "Education",
+                        `name-I` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D1`, `PT-E1`, `PT-C1`, `PT-I1`),
+               values_to = "PT1",
+               names_to = "issue1") %>%
+  drop_na(PT1) %>%
+  mutate(issue1 = recode(issue1, 
+                        `PT-C1` = "COVID-19",
+                        `PT-D1` = "Defense",
+                        `PT-E1` = "Education",
+                        `PT-I1` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D2`, `PT-E2`, `PT-C2`, `PT-I2`),
+               values_to = "PT2",
+               names_to = "issue2") %>%
+  mutate(issue2 = recode(issue2, 
+                        `PT-C2` = "COVID-19",
+                        `PT-D2` = "Defense",
+                        `PT-E2` = "Education",
+                        `PT-I2` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D3`, `PT-E3`, `PT-C3`, `PT-I3`),
+               values_to = "PT3",
+               names_to = "issue3") %>%
+  mutate(issue3 = recode(issue3, 
+                         `PT-C3` = "COVID-19",
+                         `PT-D3` = "Defense",
+                         `PT-E3` = "Education",
+                         `PT-I3` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D4`, `PT-E4`, `PT-C4`, `PT-I4`),
+               values_to = "PT4",
+               names_to = "issue4") %>%
+  mutate(issue4 = recode(issue4, 
+                         `PT-C4` = "COVID-19",
+                         `PT-D4` = "Defense",
+                         `PT-E4` = "Education",
+                         `PT-I4` = "Immigration"),
+        check = if_else(issue == issue1 & issue == issue2 & issue == issue3 & issue == issue4, 1,0)) %>%
+  filter(check == 1) %>%
+  select(PT1, PT2, PT3, PT4, issue = issue1) %>%
+  pivot_longer(cols = PT1:PT4) %>%
+  mutate(name = recode(name,
+                       `PT1` = "DV: Trait Evaluation",
+                       `PT2` = "DV: Favorability",
+                       `PT3` = "DV: Representation",
+                       `PT4` = "DV: Career Prospects")) %>%
+  group_by(issue, name) %>%
+  summarise(means = mean(value, na.rm=T),
+            stdev = sd(value, na.rm=T)) %>%
+  mutate(lower = means - (1.56 * stdev),
+         upper = means + (1.56 * stdev)) %>%
+  ggplot(aes(x = name, y = means, colour = issue,
+             ymin = lower, ymax = upper)) +
+  geom_point(position = position_dodge(.2)) + 
+  geom_errorbar(position = position_dodge(.2), width = 0) +
+  labs(y = "0 (negative) - 10 (positive)", 
+       x = "", title = "Evaluation of Politicians") +
+  geom_hline(yintercept = 5, linetype = "dotted", color = "darkgrey") +
+  theme_minimal() +
+  scale_color_manual(values = fig_cols) +
+  coord_flip() +
+  theme(plot.title = element_text(hjust = 0.5),
+        #axis.text.x = element_text(angle=45),
+        legend.position="bottom",
+        legend.title = element_blank()) 
 ```
 
-### Independent Variable
+### Treatment Conditions
 ```{r "Independent Variables", echo=F, message=FALSE, warning=FALSE,fig.width=10, fig.height=10}
 
+d %>%
+  mutate(`PT-D1` = round((`PT-D1_1` + `PT-D1_2` + `PT-D1_3` + `PT-D1_4` + `PT-D1_5` + `PT-D1_6`)/6, 0),
+         `PT-E1` = round((`PT-E1_1` + `PT-E1_2` + `PT-E1_3` + `PT-E1_4` + `PT-E1_5` + `PT-E1_6`)/6, 0),
+         `PT-C1` = round((`PT-C1_1` + `PT-C1_2` + `PT-C1_3` + `PT-C1_4` + `PT-C1_5` + `PT-C1_6`)/6, 0),
+         `PT-I1` = round((`PT-I1_1` + `PT-I1_2` + `PT-I1_3` + `PT-I1_4` + `PT-I1_5` + `PT-I1_6`)/6, 0),
+         PreT5 = round((PreT5_1 + PreT5_2 + PreT5_3 + PreT5_4)/4,0),
+         PreT7 = round((PreT7_1 + PreT7_2 + PreT7_3 + PreT7_4 + PreT7_5 + PreT7_6 + PreT7_7)/7,0)) %>%
+  pivot_longer(cols = c(`name-D`, `name-I`, `name-E`, `name-C`),
+               values_to = "name",
+               names_to = "issue") %>%
+  drop_na(name) %>%
+  mutate(issue = recode(issue, 
+                        `name-C` = "COVID-19",
+                        `name-D` = "Defense",
+                        `name-E` = "Education",
+                        `name-I` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D1`, `PT-E1`, `PT-C1`, `PT-I1`),
+               values_to = "PT1",
+               names_to = "issue1") %>%
+  drop_na(PT1) %>%
+  mutate(issue1 = recode(issue1, 
+                        `PT-C1` = "COVID-19",
+                        `PT-D1` = "Defense",
+                        `PT-E1` = "Education",
+                        `PT-I1` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D2`, `PT-E2`, `PT-C2`, `PT-I2`),
+               values_to = "PT2",
+               names_to = "issue2") %>%
+  mutate(issue2 = recode(issue2, 
+                        `PT-C2` = "COVID-19",
+                        `PT-D2` = "Defense",
+                        `PT-E2` = "Education",
+                        `PT-I2` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D3`, `PT-E3`, `PT-C3`, `PT-I3`),
+               values_to = "PT3",
+               names_to = "issue3") %>%
+  mutate(issue3 = recode(issue3, 
+                         `PT-C3` = "COVID-19",
+                         `PT-D3` = "Defense",
+                         `PT-E3` = "Education",
+                         `PT-I3` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D4`, `PT-E4`, `PT-C4`, `PT-I4`),
+               values_to = "PT4",
+               names_to = "issue4") %>%
+  mutate(issue4 = recode(issue4, 
+                         `PT-C4` = "COVID-19",
+                         `PT-D4` = "Defense",
+                         `PT-E4` = "Education",
+                         `PT-I4` = "Immigration"),
+        check = if_else(issue == issue1 & issue == issue2 & issue == issue3 & issue == issue4, 1,0)) %>%
+  filter(check == 1) %>%
+  mutate(gender = recode(name,
+                         `Karel van der Kleijn` = 0,
+                         `Karin van der Kleijn` = 1,
+                         `Rachid Amezian` = 0,
+                         `Rachida Amezian` = 1),
+         immigration = recode(name,
+                              `Karel van der Kleijn` = 0,
+                              `Karin van der Kleijn` = 0,
+                              `Rachid Amezian` = 1,
+                              `Rachida Amezian` = 1),
+         intersection = recode(name,
+                               `Karel van der Kleijn` = 0,
+                               `Karin van der Kleijn` = 0,
+                               `Rachid Amezian` = 0,
+                               `Rachida Amezian` = 1),
+         compromise = if_else(compromis == "een compromis", "Compromise", "No Compromise"))%>%
+  unite("treatment", c("name", "compromise"), sep = ": ") %>%
+  select(treatment, issue) %>%
+  group_by(issue, treatment) %>%
+  summarise(n = n()) %>%
+  mutate(perc = round(n/sum(n),2),
+         perc2 = paste0(perc*100, "%")) %>%
+  ggplot(aes(x = perc, y = issue, fill = treatment, label = perc2)) +
+  geom_col(position = 'fill') + 
+  geom_text(aes(label=perc2), position = position_fill(vjust=0.5),
+            color = "white", fontface = "bold") +
+  labs(y = "", 
+       x = "", title = "Distribution of Treatments") +
+  scale_x_continuous(labels=scales::percent) +
+  theme_minimal() +
+  scale_fill_manual(values = fig_cols) +
+  theme(plot.title = element_text(hjust = 0.5),
+        legend.position="bottom",
+        legend.title = element_blank()) +
+  guides(fill=guide_legend(ncol=2,byrow=TRUE))
 ```
@@
 
+d %>%
+  mutate(`PT-D1` = round((`PT-D1_1` + `PT-D1_2` + `PT-D1_3` + `PT-D1_4` + `PT-D1_5` + `PT-D1_6`)/6, 0),
+         `PT-E1` = round((`PT-E1_1` + `PT-E1_2` + `PT-E1_3` + `PT-E1_4` + `PT-E1_5` + `PT-E1_6`)/6, 0),
+         `PT-C1` = round((`PT-C1_1` + `PT-C1_2` + `PT-C1_3` + `PT-C1_4` + `PT-C1_5` + `PT-C1_6`)/6, 0),
+         `PT-I1` = round((`PT-I1_1` + `PT-I1_2` + `PT-I1_3` + `PT-I1_4` + `PT-I1_5` + `PT-I1_6`)/6, 0),
+         PreT5 = round((PreT5_1 + PreT5_2 + PreT5_3 + PreT5_4)/4,0),
+         PreT7 = round((PreT7_1 + PreT7_2 + PreT7_3 + PreT7_4 + PreT7_5 + PreT7_6 + PreT7_7)/7,0)) %>%
+  pivot_longer(cols = c(`name-D`, `name-I`, `name-E`, `name-C`),
+               values_to = "name",
+               names_to = "issue") %>%
+  drop_na(name) %>%
+  mutate(issue = recode(issue, 
+                        `name-C` = "COVID-19",
+                        `name-D` = "Defense",
+                        `name-E` = "Education",
+                        `name-I` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D1`, `PT-E1`, `PT-C1`, `PT-I1`),
+               values_to = "PT1",
+               names_to = "issue1") %>%
+  drop_na(PT1) %>%
+  mutate(issue1 = recode(issue1, 
+                        `PT-C1` = "COVID-19",
+                        `PT-D1` = "Defense",
+                        `PT-E1` = "Education",
+                        `PT-I1` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D2`, `PT-E2`, `PT-C2`, `PT-I2`),
+               values_to = "PT2",
+               names_to = "issue2") %>%
+  mutate(issue2 = recode(issue2, 
+                        `PT-C2` = "COVID-19",
+                        `PT-D2` = "Defense",
+                        `PT-E2` = "Education",
+                        `PT-I2` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D3`, `PT-E3`, `PT-C3`, `PT-I3`),
+               values_to = "PT3",
+               names_to = "issue3") %>%
+  mutate(issue3 = recode(issue3, 
+                         `PT-C3` = "COVID-19",
+                         `PT-D3` = "Defense",
+                         `PT-E3` = "Education",
+                         `PT-I3` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D4`, `PT-E4`, `PT-C4`, `PT-I4`),
+               values_to = "PT4",
+               names_to = "issue4") %>%
+  mutate(issue4 = recode(issue4, 
+                         `PT-C4` = "COVID-19",
+                         `PT-D4` = "Defense",
+                         `PT-E4` = "Education",
+                         `PT-I4` = "Immigration"),
+        check = if_else(issue == issue1 & issue == issue2 & issue == issue3 & issue == issue4, 1,0)) %>%
+  filter(check == 1) %>%
+  select(`Gender` = F1,
+         `Age` = F2,
+         #`Education` = F9,
+         `Region`  = F3,
+         `Urbanness`  = F4,
+         `Migration Background`  = F5,
+         `Job`  = F7,
+         `Income`  = F8,
+         `Percentage - Immigration`  = PreT1,
+         `Position - Immigration`  = PreT2,
+         `Position - Defense`  = PreT3,
+         `Position - Education`  = PreT4,
+         `Attitudes towards Women in Politics`  = PreT5,
+         `Ideology`  = PreT6,
+         `Political Efficacy` = PreT7, 
+         `Position - COVID-19 Policy` = PreT8,
+         `DV: Trait Evaluation` = PT1,
+         `DV: Favorability` = PT2,
+         `DV: Representation` = PT3,
+         `DV: Career Prospects` = PT4) %>%
+  ggcorrmat(
+  type = "robust", # correlation method
+  cor.vars = c(everything()), # a range of variables can be selected
+  colors = c(fig_cols),
+  title = "Correlalogram for Variables under Study"
+)
 ```

### 2021-05-01 src/lib/functions.R

@@ -11,6 +11,7 @@ library(ggstatsplot)
 
 fig_cols <- piratepal(palette = "basel", 
              trans = .2)
+fig_cols <- as.character(fig_cols)
 
 regression <- function(df, a, compromise, n){
   

### 2021-05-03 src/analysis/Analysis.Rmd
finalize scripts

@@
 
+## Descriptive Results
+```{r "descriptive-results", echo=FALSE}
+d %>%
+  select(PT1, PT2, PT3, PT4, issue, name, compromise) %>%
+  pivot_longer(cols = PT1:PT4,
+               names_to = "dvs") %>%
+  mutate(dvs = recode(dvs,
+                      `PT1` = "DV: Trait Evaluation",
+                      `PT2` = "DV: Favorability",
+                      `PT3` = "DV: Representation",
+                      `PT4` = "DV: Career Prospects"),
+         compromise = if_else(compromise==1, "Compromise", "No Compromise")) %>%
+  group_by(issue, dvs, name, compromise) %>%
+  summarise(means = mean(value, na.rm=T),
+            stdev = sd(value, na.rm=T)) %>%
+  mutate(lower = means - (1.56 * stdev),
+         upper = means + (1.56 * stdev)) %>%
+  ggplot(aes(x = reorder(dvs, means), y = means, colour = issue,
+             ymin = lower, ymax = upper, label = issue)) +
+  geom_point(position = position_dodge(.2)) + 
+  geom_errorbar(position = position_dodge(.2), width = 0) +
+  labs(y = "0 (negative) - 10 (positive)", 
+       x = "", title = "Bend or Break?") +
+  geom_hline(yintercept = 5, linetype = "dotted", color = "darkgrey") +
+  theme_minimal() +
+  facet_grid(name~compromise, scales = "free") +
+  scale_color_manual(values = fig_cols) +
+  coord_flip() +
+  theme(plot.title = element_text(hjust = 0.5),
+        legend.position="bottom",
+        legend.title = element_blank()) 
+```
+
 ## Balance Checks

### 2021-05-03 src/data-processing/prep_data.Rmd
finalize scripts

--- 2021-04-14 src/data-processing/prep_data.Rmd
@@
 ```{r "Dependent Variable", echo=F}
+load(here("data/intermediate/cleaned_data.RData"))
+d %>%
+  mutate(`PT-D1` = round((`PT-D1_1` + `PT-D1_2` + `PT-D1_3` + `PT-D1_4` + `PT-D1_5` + `PT-D1_6`)/6, 0),
+         `PT-E1` = round((`PT-E1_1` + `PT-E1_2` + `PT-E1_3` + `PT-E1_4` + `PT-E1_5` + `PT-E1_6`)/6, 0),
+         `PT-C1` = round((`PT-C1_1` + `PT-C1_2` + `PT-C1_3` + `PT-C1_4` + `PT-C1_5` + `PT-C1_6`)/6, 0),
+         `PT-I1` = round((`PT-I1_1` + `PT-I1_2` + `PT-I1_3` + `PT-I1_4` + `PT-I1_5` + `PT-I1_6`)/6, 0),
+         PreT5 = round((PreT5_1 + PreT5_2 + PreT5_3 + PreT5_4)/4,0),
+         PreT7 = round((PreT7_1 + PreT7_2 + PreT7_3 + PreT7_4 + PreT7_5 + PreT7_6 + PreT7_7)/7,0)) %>%
+  pivot_longer(cols = c(`name-D`, `name-I`, `name-E`, `name-C`),
+               values_to = "name",
+               names_to = "issue") %>%
+  drop_na(name) %>%
+  mutate(issue = recode(issue, 
+                        `name-C` = "COVID-19",
+                        `name-D` = "Defense",
+                        `name-E` = "Education",
+                        `name-I` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D1`, `PT-E1`, `PT-C1`, `PT-I1`),
+               values_to = "PT1",
+               names_to = "issue1") %>%
+  drop_na(PT1) %>%
+  mutate(issue1 = recode(issue1, 
+                        `PT-C1` = "COVID-19",
+                        `PT-D1` = "Defense",
+                        `PT-E1` = "Education",
+                        `PT-I1` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D2`, `PT-E2`, `PT-C2`, `PT-I2`),
+               values_to = "PT2",
+               names_to = "issue2") %>%
+  mutate(issue2 = recode(issue2, 
+                        `PT-C2` = "COVID-19",
+                        `PT-D2` = "Defense",
+                        `PT-E2` = "Education",
+                        `PT-I2` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D3`, `PT-E3`, `PT-C3`, `PT-I3`),
+               values_to = "PT3",
+               names_to = "issue3") %>%
+  mutate(issue3 = recode(issue3, 
+                         `PT-C3` = "COVID-19",
+                         `PT-D3` = "Defense",
+                         `PT-E3` = "Education",
+                         `PT-I3` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D4`, `PT-E4`, `PT-C4`, `PT-I4`),
+               values_to = "PT4",
+               names_to = "issue4") %>%
+  mutate(issue4 = recode(issue4, 
+                         `PT-C4` = "COVID-19",
+                         `PT-D4` = "Defense",
+                         `PT-E4` = "Education",
+                         `PT-I4` = "Immigration"),
+        check = if_else(issue == issue1 & issue == issue2 & issue == issue3 & issue == issue4, 1,0)) %>%
+  filter(check == 1) %>%
+  select(PT1, PT2, PT3, PT4, issue = issue1) %>%
+  pivot_longer(cols = PT1:PT4,
+               names_to = "dvs") %>%
+  mutate(dvs = recode(dvs,
+                       `PT1` = "DV: Trait Evaluation",
+                       `PT2` = "DV: Favorability",
+                       `PT3` = "DV: Representation",
+                       `PT4` = "DV: Career Prospects")) %>%
+  group_by(issue, dvs) %>%
+  summarise(means = mean(value, na.rm=T),
+            stdev = sd(value, na.rm=T)) %>%
+  mutate(lower = means - (1.56 * stdev),
+         upper = means + (1.56 * stdev)) %>%
+  ggplot(aes(x = dvs, y = means, colour = issue,
+             ymin = lower, ymax = upper, label = issue)) +
+  geom_point(position = position_dodge(.2)) + 
+  geom_errorbar(position = position_dodge(.2), width = 0) +
+  geom_label_repel(nudge_x = 0.35,nudge_y = 0.5, size = 4) + 
+  labs(y = "0 (negative) - 10 (positive)", 
+       x = "", title = "Evaluation of Politicians") +
+  geom_hline(yintercept = 5, linetype = "dotted", color = "darkgrey") +
+  theme_minimal() +
+  scale_color_manual(values = fig_cols) +
+  coord_flip() +
+  theme(plot.title = element_text(hjust = 0.5),
+        legend.position="none",
+        legend.title = element_blank()) 
 ```
 
-### Independent Variable
+### Treatment Conditions
 ```{r "Independent Variables", echo=F, message=FALSE, warning=FALSE,fig.width=10, fig.height=10}
 
+d %>%
+  mutate(`PT-D1` = round((`PT-D1_1` + `PT-D1_2` + `PT-D1_3` + `PT-D1_4` + `PT-D1_5` + `PT-D1_6`)/6, 0),
+         `PT-E1` = round((`PT-E1_1` + `PT-E1_2` + `PT-E1_3` + `PT-E1_4` + `PT-E1_5` + `PT-E1_6`)/6, 0),
+         `PT-C1` = round((`PT-C1_1` + `PT-C1_2` + `PT-C1_3` + `PT-C1_4` + `PT-C1_5` + `PT-C1_6`)/6, 0),
+         `PT-I1` = round((`PT-I1_1` + `PT-I1_2` + `PT-I1_3` + `PT-I1_4` + `PT-I1_5` + `PT-I1_6`)/6, 0),
+         PreT5 = round((PreT5_1 + PreT5_2 + PreT5_3 + PreT5_4)/4,0),
+         PreT7 = round((PreT7_1 + PreT7_2 + PreT7_3 + PreT7_4 + PreT7_5 + PreT7_6 + PreT7_7)/7,0)) %>%
+  pivot_longer(cols = c(`name-D`, `name-I`, `name-E`, `name-C`),
+               values_to = "name",
+               names_to = "issue") %>%
+  drop_na(name) %>%
+  mutate(issue = recode(issue, 
+                        `name-C` = "COVID-19",
+                        `name-D` = "Defense",
+                        `name-E` = "Education",
+                        `name-I` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D1`, `PT-E1`, `PT-C1`, `PT-I1`),
+               values_to = "PT1",
+               names_to = "issue1") %>%
+  drop_na(PT1) %>%
+  mutate(issue1 = recode(issue1, 
+                        `PT-C1` = "COVID-19",
+                        `PT-D1` = "Defense",
+                        `PT-E1` = "Education",
+                        `PT-I1` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D2`, `PT-E2`, `PT-C2`, `PT-I2`),
+               values_to = "PT2",
+               names_to = "issue2") %>%
+  mutate(issue2 = recode(issue2, 
+                        `PT-C2` = "COVID-19",
+                        `PT-D2` = "Defense",
+                        `PT-E2` = "Education",
+                        `PT-I2` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D3`, `PT-E3`, `PT-C3`, `PT-I3`),
+               values_to = "PT3",
+               names_to = "issue3") %>%
+  mutate(issue3 = recode(issue3, 
+                         `PT-C3` = "COVID-19",
+                         `PT-D3` = "Defense",
+                         `PT-E3` = "Education",
+                         `PT-I3` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D4`, `PT-E4`, `PT-C4`, `PT-I4`),
+               values_to = "PT4",
+               names_to = "issue4") %>%
+  mutate(issue4 = recode(issue4, 
+                         `PT-C4` = "COVID-19",
+                         `PT-D4` = "Defense",
+                         `PT-E4` = "Education",
+                         `PT-I4` = "Immigration"),
+        check = if_else(issue == issue1 & issue == issue2 & issue == issue3 & issue == issue4, 1,0)) %>%
+  filter(check == 1) %>%
+  mutate(gender = recode(name,
+                         `Karel van der Kleijn` = 0,
+                         `Karin van der Kleijn` = 1,
+                         `Rachid Amezian` = 0,
+                         `Rachida Amezian` = 1),
+         immigration = recode(name,
+                              `Karel van der Kleijn` = 0,
+                              `Karin van der Kleijn` = 0,
+                              `Rachid Amezian` = 1,
+                              `Rachida Amezian` = 1),
+         intersection = recode(name,
+                               `Karel van der Kleijn` = 0,
+                               `Karin van der Kleijn` = 0,
+                               `Rachid Amezian` = 0,
+                               `Rachida Amezian` = 1),
+         compromise = if_else(compromis == "geen compromis", "Compromise", "No Compromise"))%>%
+  unite("treatment", c("name", "compromise"), sep = "\n ") %>%
+  select(treatment, issue) %>%
+  group_by(issue, treatment) %>%
+  summarise(n = n()) %>%
+  mutate(perc = round(n/sum(n),2),
+         perc2 = paste0(perc*100, "%")) %>%
+  ggplot(aes(x = perc, y = issue, fill = treatment, label = perc2)) +
+  geom_col(position = 'fill', width=0.75) + 
+  geom_text(position = position_fill(vjust=0.5), color = "white", fontface = "bold") +
+  labs(y = "", x = "", title = "Distribution of Treatments") +
+  scale_x_continuous(labels=scales::percent) +
+  theme_minimal() +
+  scale_fill_manual(values = fig_cols) +
+  theme(plot.title = element_text(hjust = 0.5),
+        legend.position="bottom",
+        legend.title = element_blank()) +
+  guides(fill=guide_legend(ncol=4,byrow=TRUE))
 ```
@@
 ```{r "Correlations Matrix", echo=F, message=T, warning=T, fig.width=15, fig.height=15}
-
+d %>%
+  mutate(`PT-D1` = round((`PT-D1_1` + `PT-D1_2` + `PT-D1_3` + `PT-D1_4` + `PT-D1_5` + `PT-D1_6`)/6, 0),
+         `PT-E1` = round((`PT-E1_1` + `PT-E1_2` + `PT-E1_3` + `PT-E1_4` + `PT-E1_5` + `PT-E1_6`)/6, 0),
+         `PT-C1` = round((`PT-C1_1` + `PT-C1_2` + `PT-C1_3` + `PT-C1_4` + `PT-C1_5` + `PT-C1_6`)/6, 0),
+         `PT-I1` = round((`PT-I1_1` + `PT-I1_2` + `PT-I1_3` + `PT-I1_4` + `PT-I1_5` + `PT-I1_6`)/6, 0),
+         PreT5 = round((PreT5_1 + PreT5_2 + PreT5_3 + PreT5_4)/4,0),
+         PreT7 = round((PreT7_1 + PreT7_2 + PreT7_3 + PreT7_4 + PreT7_5 + PreT7_6 + PreT7_7)/7,0)) %>%
+  pivot_longer(cols = c(`name-D`, `name-I`, `name-E`, `name-C`),
+               values_to = "name",
+               names_to = "issue") %>%
+  drop_na(name) %>%
+  mutate(issue = recode(issue, 
+                        `name-C` = "COVID-19",
+                        `name-D` = "Defense",
+                        `name-E` = "Education",
+                        `name-I` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D1`, `PT-E1`, `PT-C1`, `PT-I1`),
+               values_to = "PT1",
+               names_to = "issue1") %>%
+  drop_na(PT1) %>%
+  mutate(issue1 = recode(issue1, 
+                        `PT-C1` = "COVID-19",
+                        `PT-D1` = "Defense",
+                        `PT-E1` = "Education",
+                        `PT-I1` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D2`, `PT-E2`, `PT-C2`, `PT-I2`),
+               values_to = "PT2",
+               names_to = "issue2") %>%
+  mutate(issue2 = recode(issue2, 
+                        `PT-C2` = "COVID-19",
+                        `PT-D2` = "Defense",
+                        `PT-E2` = "Education",
+                        `PT-I2` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D3`, `PT-E3`, `PT-C3`, `PT-I3`),
+               values_to = "PT3",
+               names_to = "issue3") %>%
+  mutate(issue3 = recode(issue3, 
+                         `PT-C3` = "COVID-19",
+                         `PT-D3` = "Defense",
+                         `PT-E3` = "Education",
+                         `PT-I3` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT-D4`, `PT-E4`, `PT-C4`, `PT-I4`),
+               values_to = "PT4",
+               names_to = "issue4") %>%
+  mutate(issue4 = recode(issue4, 
+                         `PT-C4` = "COVID-19",
+                         `PT-D4` = "Defense",
+                         `PT-E4` = "Education",
+                         `PT-I4` = "Immigration"),
+        check = if_else(issue == issue1 & issue == issue2 & issue == issue3 & issue == issue4, 1,0)) %>%
+  filter(check == 1) %>%
+  select(`Gender` = F1,
+         `Age` = F2,
+         `Education` = F9,
+         `Region`  = F3,
+         `Urbanness`  = F4,
+         `Migration Background`  = F5,
+         `Job`  = F7,
+         `Income`  = F8,
+         `Position: Immigration (%)`  = PreT1,
+         `Position: Immigration`  = PreT2,
+         `Position: Defense`  = PreT3,
+         `Position: Education`  = PreT4,
+         `Position: Attitude Women in Politics`  = PreT5,
+         `Ideology`  = PreT6,
+         `Political Efficacy` = PreT7, 
+         `Position: COVID-19 Policy` = PreT8,
+         `DV: Trait Evaluation` = PT1,
+         `DV: Favorability` = PT2,
+         `DV: Representation` = PT3,
+         `DV: Career Prospects` = PT4) %>%
+  ggcorrmat(
+  type = "robust", # correlation method
+  cor.vars = c(everything()), # a range of variables can be selected
+  colors = c(fig_cols[1], fig_cols[4], fig_cols[8]),
+  title = "Correlalogram for Variables under Study"
+)
 ```

### 2021-05-03 src/analysis/data-for-analyses.R

@@ -65,6 +65,6 @@ d <- d %>%
                                `Rachid Amezian` = 0,
                                `Rachida Amezian` = 1),
          compromise = if_else(compromis == "een compromis",1, 0)) %>%
-  select(id:F8, PreT1:PreT4, PreT5, PreT6, PreT7, PreT8, gender, immigration, intersection, compromise,
-         issue, PT1, PT2, PT3, PT4)
-  
+  select(id:F8, PreT1:PreT4, PreT5, PreT6, PreT7, PreT8, name, gender, immigration, intersection, compromise,
+         issue, PT1, PT2, PT3, PT4) %>%
+  distinct(id, .keep_all = TRUE)

### 2021-05-03 src/lib/functions.R

@@ -8,10 +8,11 @@ library(margins)
 library(lme4)
 library(yarrr)
 library(ggstatsplot)
+library(ggrepel)
 
 fig_cols <- piratepal(palette = "basel", 
              trans = .2)
-fig_cols <- as.character(fig_cols)
+fig_cols <- as.character(fig_cols[1:8])
 
 regression <- function(df, a, compromise, n){
   

### 2021-05-06 report/figures/table_descriptives.tex
add figures data and analyses

# Table: Descriptive Information of Variables under Study

<table>
 <thead>
  <tr>
   <th style="text-align:left;"> name </th>
   <th style="text-align:right;"> Mean Value </th>
   <th style="text-align:right;"> St. Dev </th>
   <th style="text-align:right;"> Min. Value </th>
   <th style="text-align:right;"> Max. Value </th>
  </tr>
 </thead>
<tbody>
  <tr>
   <td style="text-align:left;"> Treatment: Striking Compromise </td>
   <td style="text-align:right;"> 0.50 </td>
   <td style="text-align:right;"> 0.50 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 1 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Gender </td>
   <td style="text-align:right;"> 0.38 </td>
   <td style="text-align:right;"> 0.49 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 1 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Age </td>
   <td style="text-align:right;"> 33.80 </td>
   <td style="text-align:right;"> 16.34 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 72 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Region </td>
   <td style="text-align:right;"> 2.92 </td>
   <td style="text-align:right;"> 1.39 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Urbanness </td>
   <td style="text-align:right;"> 2.27 </td>
   <td style="text-align:right;"> 1.45 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Migration Background </td>
   <td style="text-align:right;"> 1.30 </td>
   <td style="text-align:right;"> 0.90 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Employment </td>
   <td style="text-align:right;"> 3.35 </td>
   <td style="text-align:right;"> 2.62 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 8 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Income </td>
   <td style="text-align:right;"> 9.76 </td>
   <td style="text-align:right;"> 2.68 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 14 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Education </td>
   <td style="text-align:right;"> 1.28 </td>
   <td style="text-align:right;"> 0.54 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 3 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Treatment: Gender Politician </td>
   <td style="text-align:right;"> 0.50 </td>
   <td style="text-align:right;"> 0.50 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 1 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Treatment: Immigration Background Politician </td>
   <td style="text-align:right;"> 0.50 </td>
   <td style="text-align:right;"> 0.50 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 1 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Treatment: Women Politician with Immigration Background </td>
   <td style="text-align:right;"> 0.25 </td>
   <td style="text-align:right;"> 0.43 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 1 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Immigration (%) </td>
   <td style="text-align:right;"> 22.82 </td>
   <td style="text-align:right;"> 12.82 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 100 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Position: Immigration </td>
   <td style="text-align:right;"> 5.91 </td>
   <td style="text-align:right;"> 2.03 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 10 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Position: Defense </td>
   <td style="text-align:right;"> 2.50 </td>
   <td style="text-align:right;"> 1.05 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 4 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Position: Education </td>
   <td style="text-align:right;"> 3.12 </td>
   <td style="text-align:right;"> 0.83 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 4 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Attitude: Women in Politics </td>
   <td style="text-align:right;"> 3.41 </td>
   <td style="text-align:right;"> 0.92 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Ideology </td>
   <td style="text-align:right;"> 4.48 </td>
   <td style="text-align:right;"> 2.20 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 10 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Political Efficacy (1) </td>
   <td style="text-align:right;"> 3.13 </td>
   <td style="text-align:right;"> 1.03 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Political Efficacy (2) </td>
   <td style="text-align:right;"> 2.06 </td>
   <td style="text-align:right;"> 0.85 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Political Efficacy (3) </td>
   <td style="text-align:right;"> 3.15 </td>
   <td style="text-align:right;"> 0.95 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Political Efficacy (4) </td>
   <td style="text-align:right;"> 2.86 </td>
   <td style="text-align:right;"> 0.97 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Political Efficacy (5) </td>
   <td style="text-align:right;"> 2.83 </td>
   <td style="text-align:right;"> 1.00 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Political Efficacy (6) </td>
   <td style="text-align:right;"> 3.60 </td>
   <td style="text-align:right;"> 1.05 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Political Efficacy (7) </td>
   <td style="text-align:right;"> 3.26 </td>
   <td style="text-align:right;"> 1.19 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Position: COVID-19 </td>
   <td style="text-align:right;"> 2.88 </td>
   <td style="text-align:right;"> 1.18 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> DV: Trait Evaluation </td>
   <td style="text-align:right;"> 3.21 </td>
   <td style="text-align:right;"> 0.64 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> DV: Favorability </td>
   <td style="text-align:right;"> 5.41 </td>
   <td style="text-align:right;"> 2.01 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 10 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> DV: Representation </td>
   <td style="text-align:right;"> 5.85 </td>
   <td style="text-align:right;"> 1.78 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 10 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> DV: Career Prospects </td>
   <td style="text-align:right;"> 4.64 </td>
   <td style="text-align:right;"> 1.97 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 10 </td>
  </tr>
</tbody>
</table>

### 2021-05-06 src/data-processing/prep_data.Rmd
update data prep when data was available

@@
 source(here("src/data-processing/tidy_data.R"))
-```
-
-## Check Missing Values
-
-We employ the following criteria:
-
-- If 10% or less of the values on the dimension are missing, then we re-code the missing values to the overall mean.
-- If 11% or more of the values on the dimension are missing, then we re-code the missing values to a constant (for instance 0) and include a dummy variable indicating whether the response on the covariate was missing or not.
-
-```{r "check missings"}
-
+source(here("src/data-processing/Urbaness.R"))
 ```
@@
 ```{r "Dependent Variable", echo=F}
-load(here("data/intermediate/cleaned_data.RData"))
 d %>%
-  mutate(`PT-D1` = round((`PT-D1_1` + `PT-D1_2` + `PT-D1_3` + `PT-D1_4` + `PT-D1_5` + `PT-D1_6`)/6, 0),
-         `PT-E1` = round((`PT-E1_1` + `PT-E1_2` + `PT-E1_3` + `PT-E1_4` + `PT-E1_5` + `PT-E1_6`)/6, 0),
-         `PT-C1` = round((`PT-C1_1` + `PT-C1_2` + `PT-C1_3` + `PT-C1_4` + `PT-C1_5` + `PT-C1_6`)/6, 0),
-         `PT-I1` = round((`PT-I1_1` + `PT-I1_2` + `PT-I1_3` + `PT-I1_4` + `PT-I1_5` + `PT-I1_6`)/6, 0),
+  mutate(PT_D1 = round((PT_D1_1 + PT_D1_2 + PT_D1_3 + PT_D1_4 + PT_D1_5 + PT_D1_6)/6, 0),
+         PT_E1 = round((PT_E1_1 + PT_E1_2 + PT_E1_3 + PT_E1_4 + PT_E1_5 + PT_E1_6)/6, 0),
+         PT_C1 = round((PT_C1_1 + PT_C1_2 + PT_C1_3 + PT_C1_4 + PT_C1_5 + PT_C1_6)/6, 0),
+         PT_I1 = round((PT_I1_1 + PT_I1_2 + PT_I1_3 + PT_I1_4 + PT_I1_5 + PT_I1_6)/6, 0),
          PreT5 = round((PreT5_1 + PreT5_2 + PreT5_3 + PreT5_4)/4,0),
          PreT7 = round((PreT7_1 + PreT7_2 + PreT7_3 + PreT7_4 + PreT7_5 + PreT7_6 + PreT7_7)/7,0)) %>%
-  pivot_longer(cols = c(`name-D`, `name-I`, `name-E`, `name-C`),
+  pivot_longer(cols = c(name_D, name_I, name_E, name_C),
                values_to = "name",
@@
   mutate(issue = recode(issue, 
-                        `name-C` = "COVID-19",
-                        `name-D` = "Defense",
-                        `name-E` = "Education",
-                        `name-I` = "Immigration")) %>%
-  pivot_longer(cols = c(`PT-D1`, `PT-E1`, `PT-C1`, `PT-I1`),
+                        name_C = "COVID_19",
+                        name_D = "Defense",
+                        name_E = "Education",
+                        name_I = "Immigration")) %>%
+  pivot_longer(cols = c(PT_D1, PT_E1, PT_C1, PT_I1),
                values_to = "PT1",
@@
   mutate(issue1 = recode(issue1, 
-                        `PT-C1` = "COVID-19",
-                        `PT-D1` = "Defense",
-                        `PT-E1` = "Education",
-                        `PT-I1` = "Immigration")) %>%
-  pivot_longer(cols = c(`PT-D2`, `PT-E2`, `PT-C2`, `PT-I2`),
+                        PT_C1 = "COVID_19",
+                        PT_D1 = "Defense",
+                        PT_E1 = "Education",
+                        PT_I1 = "Immigration")) %>%
+  pivot_longer(cols = c(PT_D2, PT_E2, PT_C2, PT_I2),
                values_to = "PT2",
@@
   mutate(issue2 = recode(issue2, 
-                        `PT-C2` = "COVID-19",
-                        `PT-D2` = "Defense",
-                        `PT-E2` = "Education",
-                        `PT-I2` = "Immigration")) %>%
-  pivot_longer(cols = c(`PT-D3`, `PT-E3`, `PT-C3`, `PT-I3`),
+                        PT_C2 = "COVID_19",
+                        PT_D2 = "Defense",
+                        PT_E2 = "Education",
+                        PT_I2 = "Immigration")) %>%
+  pivot_longer(cols = c(PT_D3, PT_E3, PT_C3, PT_I3),
                values_to = "PT3",
@@
   mutate(issue3 = recode(issue3, 
-                         `PT-C3` = "COVID-19",
-                         `PT-D3` = "Defense",
-                         `PT-E3` = "Education",
-                         `PT-I3` = "Immigration")) %>%
-  pivot_longer(cols = c(`PT-D4`, `PT-E4`, `PT-C4`, `PT-I4`),
+                         PT_C3 = "COVID_19",
+                         PT_D3 = "Defense",
+                         PT_E3 = "Education",
+                         PT_I3 = "Immigration")) %>%
+  pivot_longer(cols = c(PT_D4, PT_E4, PT_C4, PT_I4),
                values_to = "PT4",
@@
   mutate(issue4 = recode(issue4, 
-                         `PT-C4` = "COVID-19",
-                         `PT-D4` = "Defense",
-                         `PT-E4` = "Education",
-                         `PT-I4` = "Immigration"),
+                         PT_C4 = "COVID_19",
+                         PT_D4 = "Defense",
+                         PT_E4 = "Education",
+                         PT_I4 = "Immigration"),
         check = if_else(issue == issue1 & issue == issue2 & issue == issue3 & issue == issue4, 1,0)) %>%
@@
   mutate(dvs = recode(dvs,
-                       `PT1` = "DV: Trait Evaluation",
-                       `PT2` = "DV: Favorability",
-                       `PT3` = "DV: Representation",
-                       `PT4` = "DV: Career Prospects")) %>%
+                       PT1 = "DV: Trait Evaluation",
+                       PT2 = "DV: Favorability",
+                       PT3 = "DV: Representation",
+                       PT4 = "DV: Career Prospects")) %>%
   group_by(issue, dvs) %>%
@@
 d %>%
-  mutate(`PT-D1` = round((`PT-D1_1` + `PT-D1_2` + `PT-D1_3` + `PT-D1_4` + `PT-D1_5` + `PT-D1_6`)/6, 0),
-         `PT-E1` = round((`PT-E1_1` + `PT-E1_2` + `PT-E1_3` + `PT-E1_4` + `PT-E1_5` + `PT-E1_6`)/6, 0),
-         `PT-C1` = round((`PT-C1_1` + `PT-C1_2` + `PT-C1_3` + `PT-C1_4` + `PT-C1_5` + `PT-C1_6`)/6, 0),
-         `PT-I1` = round((`PT-I1_1` + `PT-I1_2` + `PT-I1_3` + `PT-I1_4` + `PT-I1_5` + `PT-I1_6`)/6, 0),
+  mutate(PT_D1 = round((PT_D1_1 + PT_D1_2 + PT_D1_3 + PT_D1_4 + PT_D1_5 + PT_D1_6)/6, 0),
+         PT_E1 = round((PT_E1_1 + PT_E1_2 + PT_E1_3 + PT_E1_4 + PT_E1_5 + PT_E1_6)/6, 0),
+         PT_C1 = round((PT_C1_1 + PT_C1_2 + PT_C1_3 + PT_C1_4 + PT_C1_5 + PT_C1_6)/6, 0),
+         PT_I1 = round((PT_I1_1 + PT_I1_2 + PT_I1_3 + PT_I1_4 + PT_I1_5 + PT_I1_6)/6, 0),
          PreT5 = round((PreT5_1 + PreT5_2 + PreT5_3 + PreT5_4)/4,0),
          PreT7 = round((PreT7_1 + PreT7_2 + PreT7_3 + PreT7_4 + PreT7_5 + PreT7_6 + PreT7_7)/7,0)) %>%
-  pivot_longer(cols = c(`name-D`, `name-I`, `name-E`, `name-C`),
+  pivot_longer(cols = c(name_D, name_I, name_E, name_C),
                values_to = "name",
@@
                                `Rachida Amezian` = 1),
-         compromise = if_else(compromis == "geen compromis", "Compromise", "No Compromise"))%>%
+         compromise = if_else(compromis == "geen compromis", "Compromise", "No Compromise")) %>%
   unite("treatment", c("name", "compromise"), sep = "\n ") %>%
@@
   mutate(issue = recode(issue, 
-                        `name-C` = "COVID-19",
-                        `name-D` = "Defense",
-                        `name-E` = "Education",
-                        `name-I` = "Immigration")) %>%
-  pivot_longer(cols = c(`PT-D1`, `PT-E1`, `PT-C1`, `PT-I1`),
+                        `name_C` = "COVID_19",
+                        `name_D` = "Defense",
+                        `name_E` = "Education",
+                        `name_I` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT_D1`, `PT_E1`, `PT_C1`, `PT_I1`),
                values_to = "PT1",
@@
   mutate(issue1 = recode(issue1, 
-                        `PT-C1` = "COVID-19",
-                        `PT-D1` = "Defense",
-                        `PT-E1` = "Education",
-                        `PT-I1` = "Immigration")) %>%
-  pivot_longer(cols = c(`PT-D2`, `PT-E2`, `PT-C2`, `PT-I2`),
+                        `PT_C1` = "COVID_19",
+                        `PT_D1` = "Defense",
+                        `PT_E1` = "Education",
+                        `PT_I1` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT_D2`, `PT_E2`, `PT_C2`, `PT_I2`),
                values_to = "PT2",
@@
   mutate(issue2 = recode(issue2, 
-                        `PT-C2` = "COVID-19",
-                        `PT-D2` = "Defense",
-                        `PT-E2` = "Education",
-                        `PT-I2` = "Immigration")) %>%
-  pivot_longer(cols = c(`PT-D3`, `PT-E3`, `PT-C3`, `PT-I3`),
+                        `PT_C2` = "COVID_19",
+                        `PT_D2` = "Defense",
+                        `PT_E2` = "Education",
+                        `PT_I2` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT_D3`, `PT_E3`, `PT_C3`, `PT_I3`),
                values_to = "PT3",
@@
   mutate(issue3 = recode(issue3, 
-                         `PT-C3` = "COVID-19",
-                         `PT-D3` = "Defense",
-                         `PT-E3` = "Education",
-                         `PT-I3` = "Immigration")) %>%
-  pivot_longer(cols = c(`PT-D4`, `PT-E4`, `PT-C4`, `PT-I4`),
+                         `PT_C3` = "COVID_19",
+                         `PT_D3` = "Defense",
+                         `PT_E3` = "Education",
+                         `PT_I3` = "Immigration")) %>%
+  pivot_longer(cols = c(`PT_D4`, `PT_E4`, `PT_C4`, `PT_I4`),
                values_to = "PT4",
@@
   mutate(issue4 = recode(issue4, 
-                         `PT-C4` = "COVID-19",
-                         `PT-D4` = "Defense",
-                         `PT-E4` = "Education",
-                         `PT-I4` = "Immigration"),
+                         `PT_C4` = "COVID_19",
+                         `PT_D4` = "Defense",
+                         `PT_E4` = "Education",
+                         `PT_I4` = "Immigration"),
         check = if_else(issue == issue1 & issue == issue2 & issue == issue3 & issue == issue4, 1,0)) %>%

### 2021-05-06 src/data-processing/Urbaness.R

@@ -1,0 +1,12 @@
+#codes <- read_sav(here("data/raw-private-encrypted/experiment.sav")) %>%
+#  filter(Consent == 1, Attention2_3 ==1, Attention2_5==1) %>%
+#  select(F4_1_TEXT) %>%
+#  distinct() %>%
+#  write_csv(here("data/raw-private-encrypted/Urbaness_NL.csv"))
+
+codes <- read_csv(here("data/raw-private-encrypted/Urbaness_NL.csv")) %>%
+  select(Urbaness = F4, F4 = F4_1_TEXT)
+
+d <- left_join(d, codes, by = "F4") %>%
+  select(-F4) %>%
+  select(id:F3, F4 = Urbaness, F5:order_PT_I)

### 2021-05-06 src/data-processing/tidy_data.R

@@ -1,54 +1,66 @@
 # Tidy Qualtrics Data
-pret <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
-                     force_request = TRUE, verbose = TRUE,
-                     label = FALSE, convert = FALSE) %>%
-  filter(Consent == 1)  %>%
+pret <- read_sav(here("data/raw-private-encrypted/experiment.sav")) %>%
+  remove_all_labels() %>%
+  filter(Consent == 1, Attention2_3 ==1, Attention2_5==1) %>%
   select(matches("PreT\\d"), id = ResponseId) %>%
   select(-matches("PreT[26]_NPS_GROUP")) %>%
   unite(order_PreT5, matches("PreT5_DO_\\d+"), sep="|", na.rm = TRUE) %>%
   unite(order_PreT7, matches("PreT7_DO_\\d+"), sep="|", na.rm = TRUE) %>%
-  unite(order_PreT, matches("Pre-Treatment_DO_PreT\\d+"), sep="|", na.rm = TRUE) %>%
+  unite(order_PreT, matches("Pre_Treatment_DO_PreT\\d+"), sep="|", na.rm = TRUE) %>%
   select(id, PreT1:PreT5_4, PreT6:PreT7_7, PreT8, 
          order_PreT5, order_PreT7, order_PreT) %>%
   mutate(across(matches("PreT5_\\d+"), 
                 ~recode(., `15` = 5, `14` = 4, `13` = 3,
-                        `12` = 2, `11` = 1))) 
+                        `12` = 2, `11` = 1))) %>%
+  drop_na()
 
-tr <- fetch_survey(surveyID = "SV_7aEiPm6fLzSon4O",
-                   force_request = TRUE, verbose = TRUE,
-                   label = FALSE, convert = FALSE) %>%
-  filter(Consent == 1) %>%
-  select(matches("name-[A-Z]"), compromis, id = ResponseId)
+tr <- read_sav(here("data/raw-private-encrypted/experiment.sav")) %>%
+  remove_all_labels() %>%
+  filter(Consent == 1, Attention2_3 ==1, Attention2_5==1) %>%
+  select(matches("name_[A-Z]"), compromis, id = ResponseId) %>%
[…]

### 2021-05-06 src/analysis/Analysis.Rmd
add analyses

--- 2021-04-24 src/analysis/Analysis.Rmd
@@
   github_document:
-    toc: yes
+  always_allow_html: true
 editor_options: 
@@
                       fig.path=('../../report/figures/'))
-library(printr)
-options(digits = 2)
 library(rmarkdown)
-library(here)
 ```
@@
 - [Analyses](#analyses)
+  - [Descriptive Results](#descriptive-results)
   - [Balance Checks](#balance-checks)
@@
 rm(list=ls())
-source(here("src/lib/functions.R"))
+source(here::here("src/lib/functions.R"))
 ```
@@
 # Analyses
+```{r "scaling variables"}
+load(here("data/intermediate/cleaned_data.RData"))
+source(here("src/analysis/scales.R"))
+#kable(scales, digits = 2) %>%
+#  kable_styling(full_width = F, position = "center")
+```
+
 ```{r "data for analyses"}
-load(here("data/intermediate/cleaned_data.RData"))
 source(here("src/analysis/data-for-analyses.R"))
+```
+
+## Check Missing Values
+I employ the following criteria:
+
+- If 10% or less of the values on the dimension are missing, then we re-code the missing values to the overall mean.
+- If 11% or more of the values on the dimension are missing, then we re-code the missing values to a constant (for instance 0) and include a dummy variable indicating whether the response on the covariate was missing or not.
+
+```{r "check missings"}
+descr <- d %>%
+  summarise(`DV: Trait Evaluation` = round(sum(is.na(PT1))/n(),2),
+            `DV: Favorability` = round(sum(is.na(PT2))/n(),2),
+            `DV: Representation` = round(sum(is.na(PT3))/n(),2),
+            `DV: Career Prospects` = round(sum(is.na(PT4))/n(),2),
+            `Immigration (%)` = round(sum(is.na(PreT1))/n(),2),
+            `Position: Immigration` = round(sum(is.na(PreT2))/n(),2),
+            `Position: Defense` = round(sum(is.na(PreT3))/n(),2),
+            `Position: Education` = round(sum(is.na(PreT4))/n(),2),
+            `Attitude: Women in Politics` = round(sum(is.na(PreT5))/n(),2),
+            `Ideology` = round(sum(is.na(PreT6))/n(),2),
+            `Political Efficacy (1)` = round(sum(is.na(PreT7_1))/n(),2),
+            `Political Efficacy (2)` = round(sum(is.na(PreT7_2))/n(),2),
+            `Political Efficacy (3)` = round(sum(is.na(PreT7_3))/n(),2),
+            `Political Efficacy (4)` = round(sum(is.na(PreT7_4))/n(),2),
+            `Political Efficacy (5)` = round(sum(is.na(PreT7_5))/n(),2),
+            `Political Efficacy (6)` = round(sum(is.na(PreT7_6))/n(),2),
+            `Political Efficacy (7)` = round(sum(is.na(PreT7_7))/n(),2),
+            `Position: COVID-19` = round(sum(is.na(PreT8))/n(),2),
+            `Gender` = round(sum(is.na(F1))/n(),2),
+            `Age` = round(sum(is.na(F2))/n(),2),
+            `Region` = round(sum(is.na(F3))/n(),2),
+            `Urbaness` = round(sum(is.na(F4))/n(),2),
+            `Migration Background` = round(sum(is.na(F5))/n(),2),
+            `Party Preference` = round(sum(is.na(F6))/n(),2),
+            `Employment` = round(sum(is.na(F7))/n(),2),
+            `Income` = round(sum(is.na(F8))/n(),2),
+            `Education` = round(sum(is.na(F9))/n(),2)) %>%
+  pivot_longer(cols = `DV: Trait Evaluation`:`Education`,
+              names_to = "Variables", values_to = "% Missing Values") %>%
+  filter(`% Missing Values` > 0)
+
+#kable(descr) %>%
+#  kable_styling(full_width = F, position = "center")
+```
+
+I recode the missing values of the variables `Urbaness`, `Party Preference`, `Employment`, and `Income` to the mean value of the respective variables -- median for `Party Precerence`.
+For Income, I also include a dummy indicating whether the missing value was imputed.
+
+```{r "add missings"}
+means <- d %>%
+  summarise(F4 = round(mean(F4, na.rm = T),0),
+            F5 = round(mean(F5, na.rm = T), 0),
+            F6 = max(names(table(F6))),
+            F7 = round(mean(F7, na.rm = T),0),
+            F8 = round(mean(F8, na.rm = T),0),
+            F9 = round(mean(F9, na.rm = T),0))
+
+d <- d %>%
+  mutate(F4 = replace_na(F4, means$F4),
+         F5 = replace_na(F5, means$F5),
+         F6 = replace_na(F6, means$F6),
+         F7 = replace_na(F7, means$F7),
+         missing_F8 = if_else(is.na(F8), 1, 0),
+         F8 = replace_na(F8, means$F8),
+         F9 = replace_na(F9, means$F9))
+rm(means, descr, scales)
 ```
@@
 table <- purrr::map(descr, .f= ".") 
-#render_j2("src/analysis/table_descriptives.tex.j2", "report/figures/table_descriptives.tex", data=list(data=table, methods=methodnames))
+#render_j2("src/analysis/table_descriptives.tex.j2", "report/figures/table_descriptives.tex", data=list(data=table, methods=methodnames)
+rm(descr, methodnames, table, fn, table2)
+```
+
+## Descriptive Results
+```{r "descriptive-results", echo=FALSE, fig.height=10, fig.width=6}
+d %>%
+  select(PT1, PT2, PT3, PT4, issue, name, compromise) %>%
+  mutate(PT1 = PT1 * 2) %>%
+  pivot_longer(cols = PT1:PT4,
+               names_to = "dvs") %>%
+  mutate(dvs = recode(dvs,
+                      `PT1` = "DV: Trait Evaluation",
+                      `PT2` = "DV: Favorability",
+                      `PT3` = "DV: Representation",
+                      `PT4` = "DV: Career Prospects"),
+         compromise = if_else(compromise==1, "Compromise", "No Compromise"),
+         compromise = factor(compromise,
+                             level = c("No Compromise", "Compromise"))) %>%
+  unite("treatment", c("issue", "name"), sep = ": ") %>%
+  group_by(treatment, compromise, dvs) %>%
+  summarise(means = round(mean(value, na.rm=T),1),
+            stdev = sd(value, na.rm=T)) %>%
+  mutate(lower = means - (1.56 * stdev),
+         upper = means + (1.56 * stdev),
+         type = if_else(means <= 5, "below", "above")) %>%
+  ggplot(aes(x = treatment, 
+             y =means, label = means, color=type,
+             ymin = lower, ymax = upper)) +
+  geom_point(stat='identity', size=6)  +
+  scale_color_manual(values = c("above"=fig_cols[3],
+                                "below"=fig_cols[2])) +
+  geom_errorbar(width = 0) +
+  geom_text(color="white", size=2) +
+  facet_grid(dvs~compromise) +
+  labs(y = "0 (negative) - 10 (positive)", 
+       x = "", title = "Bend or Break") +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5),
+        legend.position="none",
+        legend.title = element_blank(),
+        axis.text=element_text(size=8)) +
+  geom_hline(yintercept = 5, linetype = "dotted", color = "darkgrey") +
+  coord_flip() 
 ```
@@
 ## Balance Checks
-```{r "balance-checks", eval = F}
+
+The figure below shows that the data is unbalanced for the variables: `Income`, `Employment`, `Urbaness`, `Age`, `Position: COVID`, `Political Efficacy`, `Ideology`,
+`Attitudes: Women in Politics`, `Position: Education`, `Position: Defense`, `Position: Immigration`.
+As described in the Pre-Analysis Plan (p.10), I will add these covariates to the analyses as controls.
+```{r "balance-checks"}
 source(here("src/analysis/balance-test.R"))
+df
 ```
@@
 ## Gender Hypothesis 
-```{r "h1", fig.align="center", fig.height=8, fig.width=8, eval = F}
+```{r "h1", fig.align="center", fig.height=8, fig.width=8}
 source(here("src/analysis/h1.R"))
+h1
 ```
@@
 ## Migration Hypothesis
-```{r "h2", fig.align="center", fig.height=8, fig.width=8, eval = F}
+```{r "h2", fig.align="center", fig.height=8, fig.width=8}
 source(here("src/analysis/h2.R"))
+h2
 ```
@@
 ## Intersection Hypothesis
-```{r "h3", fig.align="center", fig.height=8, fig.width=8, eval = F}
+```{r "h3", fig.align="center", fig.height=8, fig.width=8}
 source(here("src/analysis/h3.R"))
+h3
 ```
@@
 ## Intersection Hypothesis -- Pooled
-```{r "h3-pooled", fig.align="center", fig.height=8, fig.width=8, eval = F}
+```{r "h3-pooled", fig.align="center", fig.height=8, fig.width=8}
 source(here("src/analysis/h3-pooled.R"))
+h3p
 ```

### 2021-05-06 src/analysis/balance-test.R

@@ -1,39 +1,89 @@
 covs <- d %>%
-  mutate(treatment = paste(name, compromis, sep = "-")) %>%
+  mutate(compromise = if_else(compromise == 0, "No Compromise", "Compromise"),
+         treatment = paste(name, compromise, sep = "-")) %>%
   select(treatment, PreT1:PreT8, F1:F9) 
 
-balanced <-bal.tab(Treatment ~ PreT1 + PreT2 + PreT3 + PreT4 +
-                     PreT5 + PreT6 + PreT7 + PreT8 +
-                     factor(F1) + F2 + factor(F9) + factor(F3) +
-                     factor(F4) + factor(F5) + factor(F6) + F7 + F8,
-                   Age + Education + factor(Sex_str), data = covs,
+balanced <-bal.tab(treatment ~ PreT1 + PreT2 + PreT3 + PreT4 +
+                     PreT5 + PreT6 + PreT7_1 + PreT7_2 +
+                     PreT7_3 + PreT7_4 + PreT7_5 + PreT7_6 + 
+                     PreT7_7 + PreT8 +
+                     factor(F1) + F2 +  factor(F3) +
+                     F4 + factor(F5) + factor(F6) +
+                     F7 + F8 + factor(F9),
+                   data = covs,
                    thresholds = c(m = 0.05))[[1]] 
 
-balanced <- balanced %>%
-  mutate(variable = c("Immigration (%)", "Immigration", "Defense", "Education", "Sexism",
-                      "Ideology", "Poltical Efficacy", "COVID-19",
-                      "Gender: Male", "Age", "Education: Middle", "Education: High",
-                      "Region: West", "Region: North", "Region: East", "Region: South",
-                      "Little Urban", "Moderatly Urban", "Highly Urban", 
-                      "Very Highly Urban", "Migration Background", "Bij1","CDA",
-                      "ChristenUnie", "D66", "Denk", "Forum for Democracy",
-                      "GroenLinks", "JA21", "PvdA", "Animal Rights Party", "PVV", 
-                      "SGP", "SP", "VOLT","VVD", "50Plus Party", "Employment",
-                      "Income"),
+df <- balanced[1]$`Karel van der Kleijn-No Compromise vs. Karel van der Kleijn-Compromise`$Balance %>%
+  add_case(balanced[2]$`Karin van der Kleijn-Compromise vs. Karel van der Kleijn-Compromise`$Balance) %>%
[…]

### 2021-05-06 src/analysis/data-for-analyses.R

@@ -1,52 +1,54 @@
 d <- d %>%
-  mutate(`PT-D1` = round((`PT-D1_1` + `PT-D1_2` + `PT-D1_3` + `PT-D1_4` + `PT-D1_5` + `PT-D1_6`)/6, 0),
-         `PT-E1` = round((`PT-E1_1` + `PT-E1_2` + `PT-E1_3` + `PT-E1_4` + `PT-E1_5` + `PT-E1_6`)/6, 0),
-         `PT-C1` = round((`PT-C1_1` + `PT-C1_2` + `PT-C1_3` + `PT-C1_4` + `PT-C1_5` + `PT-C1_6`)/6, 0),
-         `PT-I1` = round((`PT-I1_1` + `PT-I1_2` + `PT-I1_3` + `PT-I1_4` + `PT-I1_5` + `PT-I1_6`)/6, 0),
+  mutate(PT_D1 = round((PT_D1_1 + PT_D1_2 + PT_D1_3 + PT_D1_4 + PT_D1_5 + PT_D1_6)/6, 0),
+         PT_E1 = round((PT_E1_1 + PT_E1_2 + PT_E1_3 + PT_E1_4 + PT_E1_5 + PT_E1_6)/6, 0),
+         PT_C1 = round((PT_C1_1 + PT_C1_2 + PT_C1_3 + PT_C1_4 + PT_C1_5 + PT_C1_6)/6, 0),
+         PT_I1 = round((PT_I1_1 + PT_I1_2 + PT_I1_3 + PT_I1_4 + PT_I1_5 + PT_I1_6)/6, 0),
          PreT5 = round((PreT5_1 + PreT5_2 + PreT5_3 + PreT5_4)/4,0),
-         PreT7 = round((PreT7_1 + PreT7_2 + PreT7_3 + PreT7_4 + PreT7_5 + PreT7_6 + PreT7_7)/7,0)) %>%
-  pivot_longer(cols = c(`name-D`, `name-I`, `name-E`, `name-C`),
+         PreT7_2 = 6 - PreT7_2,
+         PreT7_6 = 6 - PreT7_6,
+         PreT7_7 = 6 - PreT7_7) %>%
+  pivot_longer(cols = c(`name_D`, `name_I`, `name_E`, `name_C`),
                values_to = "name",
                names_to = "issue") %>%
   drop_na(name) %>%
   mutate(issue = recode(issue, 
-                        `name-C` = "COVID-19",
-                        `name-D` = "Defense",
-                        `name-E` = "Education",
[…]

### 2021-05-06 src/analysis/descriptive-information-overview.R

@@ -1,29 +1,37 @@
 descr <- d %>%
-  select(-id, -issue) %>%
-  mutate(F1 = recode(F1, `999` = 0, `2` = 0)) %>%
+  select(-id, -issue, -name, -F6, -missing_F8) %>%
+  mutate(F1 = recode(F1, `999` = 0, `2` = 0),
+         F5 = as.numeric(F5)) %>%
   pivot_longer(cols = everything()) %>%
   group_by(name) %>%
-  summarise(means = mean(value, na.rm = T),
-            stdev = sd(value, na.rm = T),
-            minvalue = min(value, na.rm = T),
-            maxvalue = max(value, na.rm = T)) %>%
+  summarise(`Mean Value` = mean(value, na.rm = T),
+            `St. Dev` = sd(value, na.rm = T),
+            `Min. Value` = min(value, na.rm = T),
+            `Max. Value` = max(value, na.rm = T)) %>%
   ungroup() %>%
   mutate(name = recode(name,
                        `F1` = "Gender",
                        `F2` = "Age",
-                       `F3` = "Education",
+                       `F3` = "Region",
                        `F4` = "Urbanness",
                        `F5` = "Migration Background",
-                       `F6`  = "Party Preference",
+                       #`F6`  = "Party Preference",
                        `F7`  = "Employment",
                        `F8`  = "Income",
+                       `F9` = "Education",
                        `PreT1`  = "Immigration (%)",
                        `PreT2`  = "Position: Immigration",
                        `PreT3`  = "Position: Defense",
                        `PreT4`  = "Position: Education",
                        `PreT5`  = "Attitude: Women in Politics",
                        `PreT6`  = "Ideology",
-                       `PreT7` = "Political Efficacy",
+                       `PreT7_1` = "Political Efficacy (1)",
+                       `PreT7_2` = "Political Efficacy (2)",
+                       `PreT7_3` = "Political Efficacy (3)",
+                       `PreT7_4` = "Political Efficacy (4)",
+                       `PreT7_5` = "Political Efficacy (5)",
+                       `PreT7_6` = "Political Efficacy (6)",
+                       `PreT7_7` = "Political Efficacy (7)",
                        `PreT8` = "Position: COVID-19",
                        `gender` = "Treatment: Gender Politician",
                        `immigration` = "Treatment: Immigration Background Politician",
@@ -43,8 +51,11 @@ descr <- d %>%
                                    "Immigration (%)","Position: Immigration",
[…]

### 2021-05-06 src/analysis/h1.R

@@ -1,45 +1,32 @@
 # H1a & H1b
 issues <- unique(d$issue)
 for(i in 1:length(issues)){
-  df <- d %>% select(a = gender, compromise, PT1:PT4, issue) %>%
+  df <- d %>% select(a = gender, compromise, PT1:PT4, F2, F4, F7, F8, PreT2:PreT8, issue) %>%
     filter(issue == issues[i]) %>%
     select(-issue)
   if(i==1){
-    h1a <- regression(df, a, compromise, 1) %>%
+    h1 <- regression(df, a, compromise, 1) %>%
     mutate(issue = issues[i])
   }  
   else{
     tmp <- regression(df, a, compromise, 1) %>%
       mutate(issue = issues[i])
-    h1a <- h1a %>% add_case(tmp)
+    h1 <- h1 %>% add_case(tmp)
   }
 }
 
-for(i in 1:length(issues)){
-  df <- d %>% select(a = gender, compromise, PT1:PT4, issue) %>%
-    filter(issue == issues[i]) %>%
-    select(-issue)
-  if(i==1){
-    h1b <- regression(df, a, compromise, 0) %>%
-      mutate(issue = issues[i])
-  }  
-  else{
-    tmp <- regression(df, a, compromise, 0) %>%
-      mutate(issue = issues[i])
-    h1b <- h1b %>% add_case(tmp)
-  }
-}
-
-h1a %>% add_case(h1b) %>%
-  mutate(y = recode(y,
+h1 <- h1 %>%
+  mutate(id = if_else(y == "PT1", 1,
+              if_else(y == "PT2", 2,
+              if_else(y == "PT4", 3, 4))),
+         y = recode(y,
                     `PT1` = "DV: Trait Evaluation",
                     `PT2` = "DV: Favorability",
                     `PT3` = "DV: Representation",
                     `PT4` = "DV: Career Prospects"),
-         n = recode(n,
+         compromise = recode(compromise,
                     `1` = "Compromise (H1a)",
-                    `0` = "No Compromise (H1b)"),
-         id = 1:(dim(h1a)[1]+dim(h1b)[1])) %>%
+                    `0` = "No Compromise (H1b)")) %>%
   ggplot(aes(x = reorder(id, AME), 
              y = AME,
              color = y,
@@ -48,7 +35,7 @@ h1a %>% add_case(h1b) %>%
   geom_point(position = ) + geom_errorbar(width = 0) +
   theme_bw() +
[…]

### 2021-05-06 src/analysis/h2.R

@@ -1,7 +1,7 @@
 ## H2
 issues <- unique(d$issue)
 for(i in 1:length(issues)){
-  df <- d %>% select(a = immigration, compromise, PT1:PT4, issue) %>%
+  df <- d %>% select(a = immigration, compromise, PT1:PT4, F2, F4, F7, F8, PreT2:PreT8, issue) %>%
     filter(issue == issues[i]) %>%
     select(-issue)
   if(i==1){
@@ -15,16 +15,19 @@ for(i in 1:length(issues)){
   }
 }
 
-h2 %>%
-  mutate(y = recode(y,
+h2 <- h2 %>%
+  mutate(id = if_else(y == "PT1", 1,
+              if_else(y == "PT2", 2,
+              if_else(y == "PT4", 3, 4))),
+         y = recode(y,
                     `PT1` = "DV: Trait Evaluation",
                     `PT2` = "DV: Favorability",
                     `PT3` = "DV: Representation",
                     `PT4` = "DV: Career Prospects"),
-         n = recode(n,
+         compromise = recode(compromise,
                     `1` = "Compromise (H2)",
-                    `0` = "No Compromise (H1b)"),
-         id = 1:(dim(h2)[1])) %>%
+                    `0` = "No Compromise (H1b)")) %>%
+  filter(compromise == "Compromise (H2)") %>%
   ggplot(aes(x = reorder(id, AME), 
              y = AME,
              color = y,
@@ -33,7 +36,7 @@ h2 %>%
   geom_point(position = ) + geom_errorbar(width = 0) +
   theme_bw() +
   labs(x = "", y = "Average Marginal Effects of Being a Politician with a Migration Background") +
-  facet_grid(issue~n, scales = "free_y") +
+  facet_grid(issue~compromise, scales = "free") +
   theme(plot.title = element_text(hjust = 0.5),
         plot.subtitle = element_text(hjust = 0.5),
         axis.title.y=element_blank(),
@@ -42,7 +45,7 @@ h2 %>%
         legend.title = element_blank(),
         axis.ticks.x=element_blank(),
         axis.ticks.y = element_blank()) +
-  scale_color_viridis_d() +
+  scale_color_manual(values = fig_cols) +
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") +
   guides(color=guide_legend(nrow=1,byrow=TRUE)) +
   coord_flip()

### 2021-05-06 src/analysis/h3-pooled.R

@@ -1,20 +1,20 @@
 ## H3
-df <- d %>% select(a = intersection, compromise, PT1:PT4, issue)
-h3ap <- pooled_regression(df, a, compromise, issue, 1) %>%
-  mutate(n = 1)
-h3bp <- pooled_regression(df, a, compromise, issue, 0) %>%
-  mutate(n = 0)
+df <- d %>% select(a = intersection, compromise, PT1:PT4,issue, F2, F4, F7, F8, PreT2:PreT8)
+h3p <- pooled_regression(df, a, compromise, issue, 1)
 
-h3ap %>% add_case(h3bp) %>%
-  mutate(y = recode(y,
+
+h3p <- h3p %>%
+  mutate(id = if_else(y == "PT1", 1,
+              if_else(y == "PT2", 2,
+              if_else(y == "PT4", 3, 4))),
+         y = recode(y,
                     `PT1` = "DV: Trait Evaluation",
                     `PT2` = "DV: Favorability",
                     `PT3` = "DV: Representation",
                     `PT4` = "DV: Career Prospects"),
-         n = recode(n,
-                    `1` = "Compromise (H3a - Pooled)",
-                    `0` = "No Compromise (H3b - Pooled)"),
-         id = 1:(dim(h3ap)[1]+dim(h3bp)[1])) %>%
+         compromise = recode(compromise,
+                             `1` = "Compromise (H3a)",
+                             `0` = "No Compromise (H3b)")) %>%
   ggplot(aes(x = reorder(id, AME), 
              y = AME,
              color = y,
@@ -23,7 +23,7 @@ h3ap %>% add_case(h3bp) %>%
   geom_point(position = ) + geom_errorbar(width = 0) +
   theme_bw() +
   labs(x = "", y = "Average Marginal Effects of Being a Women Politician with a Migration Background") +
-  facet_grid(.~n, scales = "free_y") +
+  facet_grid(.~compromise, scales = "free") +
   theme(plot.title = element_text(hjust = 0.5),
         plot.subtitle = element_text(hjust = 0.5),
         axis.title.y=element_blank(),
@@ -32,7 +32,7 @@ h3ap %>% add_case(h3bp) %>%
         legend.title = element_blank(),
         axis.ticks.x=element_blank(),
         axis.ticks.y = element_blank()) +
-  scale_color_viridis_d() +
+  scale_color_manual(values = fig_cols) +
[…]

### 2021-05-06 src/analysis/h3.R

@@ -1,45 +1,32 @@
 ## H3
 issues <- unique(d$issue)
 for(i in 1:length(issues)){
-  df <- d %>% select(a = intersection, compromise, PT1:PT4, issue) %>%
+  df <- d %>% select(a = intersection, compromise, PT1:PT4, F2, F4, F7, F8, PreT2:PreT8, issue) %>%
     filter(issue == issues[i]) %>%
     select(-issue)
   if(i==1){
-    h3a <- regression(df, a, compromise, 1) %>%
+    h3 <- regression(df, a, compromise, 1) %>%
       mutate(issue = issues[i])
   }  
   else{
     tmp <- regression(df, a, compromise, 1) %>%
       mutate(issue = issues[i])
-    h3a <- h3a %>% add_case(tmp)
+    h3 <- h3 %>% add_case(tmp)
   }
 }
 
-for(i in 1:length(issues)){
-  df <- d %>% select(a = intersection, compromise, PT1:PT4, issue) %>%
-    filter(issue == issues[i]) %>%
-    select(-issue)
-  if(i==1){
-    h3b <- regression(df, a, compromise, 0) %>%
-      mutate(issue = issues[i])
-  }  
-  else{
-    tmp <- regression(df, a, compromise, 0) %>%
-      mutate(issue = issues[i])
-    h3b <- h3b %>% add_case(tmp)
-  }
-}
-
-h3a %>% add_case(h3b) %>%
-  mutate(y = recode(y,
+h3 <- h3 %>%
+  mutate(id = if_else(y == "PT1", 1,
+              if_else(y == "PT2", 2,
+              if_else(y == "PT4", 3, 4))),
+         y = recode(y,
                     `PT1` = "DV: Trait Evaluation",
                     `PT2` = "DV: Favorability",
                     `PT3` = "DV: Representation",
                     `PT4` = "DV: Career Prospects"),
-         n = recode(n,
-                    `1` = "Compromise (H3a)",
-                    `0` = "No Compromise (H3b)"),
-         id = 1:(dim(h3a)[1]+dim(h3b)[1])) %>%
+         compromise = recode(compromise,
+                             `1` = "Compromise (H3a)",
+                             `0` = "No Compromise (H3b)")) %>%
   ggplot(aes(x = reorder(id, AME), 
              y = AME,
              color = y,
@@ -48,7 +35,7 @@ h3a %>% add_case(h3b) %>%
   geom_point(position = ) + geom_errorbar(width = 0) +
   theme_bw() +
[…]

### 2021-05-06 src/analysis/scales.R

@@ -1,0 +1,45 @@
+PT_D1 <- d %>%
+  select(matches("PT_D1_\\d")) %>%
+  drop_na() %>%
+  ltm::cronbach.alpha(probs = c(0.025, 0.975), B = 1000, na.rm = FALSE)
+
+PT_C1 <- d %>%
+  select(matches("PT_C1_\\d")) %>%
+  drop_na() %>%
+  ltm::cronbach.alpha(probs = c(0.025, 0.975), B = 1000, na.rm = FALSE)
+
+PT_E1 <- d %>%
+  select(matches("PT_E1_\\d")) %>%
+  drop_na() %>%
+  ltm::cronbach.alpha(probs = c(0.025, 0.975), B = 1000, na.rm = FALSE)
+
+
+PT_I1 <- d %>%
+  select(matches("PT_I1_\\d")) %>%
+  drop_na() %>%
+  ltm::cronbach.alpha(probs = c(0.025, 0.975), B = 1000, na.rm = FALSE)
+
+
+PreT5 <- d %>%
+  select(matches("PreT5_\\d")) %>%
+  drop_na() %>%
+  ltm::cronbach.alpha(probs = c(0.025, 0.975), B = 1000, na.rm = FALSE)
+
+PreT7 <- d %>%
+  select(matches("PreT7_\\d")) %>%
+  drop_na() %>%
+  mutate(PreT7_2 = 6 - PreT7_2,
+         PreT7_6 = 6 - PreT7_6,
+         PreT7_7 = 6 - PreT7_7) %>%
+  ltm::cronbach.alpha(probs = c(0.025, 0.975), B = 1000, na.rm = FALSE)
+
+scales <- tibble(Variable = c("DV: Trait Evaluation (Corona)",
+                              "DV: Trait Evaluation (Defense)",
+                              "DV: Trait Evaluation (Education)",
+                              "DV: Trait Evaluation (Immigration)",
+                              "Attitudes: Women in Politics",
+                              "Political  Efficacy"),
+                 `Cronbach's Alpha` = c(PT_C1[[1]], PT_D1[[1]], PT_E1[[1]],
+                                        PT_I1[[1]], PreT5[[1]], PreT7[[1]]))
+
+rm(PreT5, PreT7, PT_C1, PT_D1, PT_E1, PT_I1)

### 2021-05-06 src/lib/functions.R
update packages and functions

@@ -1,42 +1,48 @@
 library(here)
+library(kableExtra)
 library(tidyverse)
-library(qualtRics)
 library(DeclareDesign)
 library(ggpubr)
 library(scales)
+library(cobalt)
 library(margins)
 library(lme4)
-library(yarrr)
 library(ggstatsplot)
 library(ggrepel)
+library(haven)
+library(sjlabelled)
 
-fig_cols <- piratepal(palette = "basel", 
+fig_cols <- yarrr::piratepal(palette = "basel", 
              trans = .2)
 fig_cols <- as.character(fig_cols[1:8])
 
 regression <- function(df, a, compromise, n){
   
   depVarList <- df %>% select(matches("PT[0-9]"))
-  indepVarList <- df %>% select(a, compromise) 
-  allModels <- apply(depVarList,2,function(xl)lm(xl ~ a * compromise, data= indepVarList))
+  indepVarList <- df %>% select(a, compromise, F2, F4, F7, F8, PreT2:PreT8) 
+  allModels <- apply(depVarList,2,function(xl)lm(xl ~ a * compromise +
+                                                   factor(F2) + F4 + F7 + F8 +
+                                                   PreT2 + PreT3 + PreT4 + PreT5 +
+                                                   PreT6 + PreT7_1 + PreT7_2 +
+                                                   PreT7_3 + PreT7_4 + PreT7_5 + 
+                                                   PreT7_6 + PreT7_7 + PreT8, 
+                                                 data= indepVarList))
   depVarList <- df %>% select(matches("PT[0-9]")) %>% colnames()
   
   for(i in 1:length(depVarList)){
     if(i==1){
-      m <- summary(margins(allModels[[i]]), at = list(compromise = n))[2,] %>%
+      m <- summary(margins(allModels[[i]], variables = "a", at = list(compromise = 0:1))) %>%
         mutate(y = depVarList[i],
-               n = n,
-               lower = AME - (1.645 * SE),
-               upper = AME + (1.645 * SE)) %>%
-        select(AME, upper, lower, y, n)
+               lower = AME - (1.56 * SE),
+               upper = AME + (1.56 * SE)) %>%
+        select(AME, upper, lower, y, compromise)
     }
     else{
-      tmp <- summary(margins(allModels[[i]]), at = list(compromise = n))[2,] %>%
+      tmp <- summary(margins(allModels[[i]], variables = "a", at = list(compromise = 0:1))) %>%
         mutate(y = depVarList[i],
-               n = n,
[…]

### 2021-05-06 src/analysis/Analysis.Rmd
file with tables

@@
 ```{r "setup", include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
+library(knitr)
+opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                       fig.align = "center",
@@
 source(here("src/analysis/scales.R"))
-#kable(scales, digits = 2) %>%
-#  kable_styling(full_width = F, position = "center")
+kable(scales, digits = 2) %>%
+  kable_styling(full_width = F, position = "center")
 ```
@@
 
-#kable(descr) %>%
-#  kable_styling(full_width = F, position = "center")
+kable(descr) %>%
+  kable_styling(full_width = F, position = "center")
 ```
@@
 ## Descriptive Results
-```{r "descriptive-results", echo=FALSE, fig.height=10, fig.width=6}
+```{r "descriptive-results", echo=FALSE, fig.height=10, fig.width=8}
 d %>%
@@
 As described in the Pre-Analysis Plan (p.10), I will add these covariates to the analyses as controls.
-```{r "balance-checks"}
+```{r "balance-checks", fig.height=8, fig.width=8}
 source(here("src/analysis/balance-test.R"))
@@
 ## Intersection Hypothesis -- Pooled
-```{r "h3-pooled", fig.align="center", fig.height=8, fig.width=8}
+```{r "h3-pooled", fig.align="center", fig.height=5, fig.width=5}
 source(here("src/analysis/h3-pooled.R"))

### 2021-05-06 src/analysis/descriptive-information-overview.R
add labels to graphs of h's

@@ -2,14 +2,15 @@ descr <- d %>%
   select(-id, -issue, -name, -F6, -missing_F8) %>%
   mutate(F1 = recode(F1, `999` = 0, `2` = 0),
          F5 = as.numeric(F5)) %>%
-  pivot_longer(cols = everything()) %>%
-  group_by(name) %>%
+  pivot_longer(cols = everything(),
+               names_to = "Variables") %>%
+  group_by(Variables) %>%
   summarise(`Mean Value` = mean(value, na.rm = T),
             `St. Dev` = sd(value, na.rm = T),
             `Min. Value` = min(value, na.rm = T),
             `Max. Value` = max(value, na.rm = T)) %>%
   ungroup() %>%
-  mutate(name = recode(name,
+  mutate(Variables = recode(Variables,
                        `F1` = "Gender",
                        `F2` = "Age",
                        `F3` = "Region",
@@ -41,7 +42,7 @@ descr <- d %>%
                        `PT2` = "DV: Favorability",
                        `PT3` = "DV: Representation",
                        `PT4` = "DV: Career Prospects"),
-         name = factor(name,
+         Variables = factor(Variables,
                          levels = c("DV: Trait Evaluation","DV: Favorability",
                                    "DV: Representation", "DV: Career Prospects",
                                    "Treatment: Gender Politician",

### 2021-05-06 src/analysis/h1.R

@@ -31,8 +31,10 @@ h1 <- h1 %>%
              y = AME,
              color = y,
              ymin = lower,
-             ymax = upper)) +
+             ymax = upper,
+             label = y)) +
   geom_point(position = ) + geom_errorbar(width = 0) +
+  geom_label_repel(nudge_y = 0.5, size = 2) + 
   theme_bw() +
   labs(x = "", y = "Average Marginal Effects of Being a Women Politician") +
   facet_grid(issue~compromise, scales = "free") +
@@ -40,7 +42,7 @@ h1 <- h1 %>%
         plot.subtitle = element_text(hjust = 0.5),
         axis.title.y=element_blank(),
         axis.text.y=element_blank(),
-        legend.position="bottom",
+        legend.position="none",
         legend.title = element_blank(),
         axis.ticks.x=element_blank(),
         axis.ticks.y = element_blank()) +
@@ -48,3 +50,4 @@ h1 <- h1 %>%
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") +
   guides(color=guide_legend(nrow=1,byrow=TRUE)) +
   coord_flip()
+

### 2021-05-06 src/analysis/h2.R

@@ -32,8 +32,10 @@ h2 <- h2 %>%
              y = AME,
              color = y,
              ymin = lower,
-             ymax = upper)) +
+             ymax = upper,
+             label = y)) +
   geom_point(position = ) + geom_errorbar(width = 0) +
+  geom_label_repel(nudge_y = 0.5, size = 2) + 
   theme_bw() +
   labs(x = "", y = "Average Marginal Effects of Being a Politician with a Migration Background") +
   facet_grid(issue~compromise, scales = "free") +

### 2021-05-06 src/analysis/h3-pooled.R

@@ -19,8 +19,10 @@ h3p <- h3p %>%
              y = AME,
              color = y,
              ymin = lower,
-             ymax = upper)) +
+             ymax = upper,
+             label = y)) +
   geom_point(position = ) + geom_errorbar(width = 0) +
+  geom_label_repel(nudge_y = 0.5, size = 2) + 
   theme_bw() +
   labs(x = "", y = "Average Marginal Effects of Being a Women Politician with a Migration Background") +
   facet_grid(.~compromise, scales = "free") +

### 2021-05-06 src/analysis/h3.R

@@ -31,8 +31,10 @@ h3 <- h3 %>%
              y = AME,
              color = y,
              ymin = lower,
-             ymax = upper)) +
+             ymax = upper,
+             label = y)) +
   geom_point(position = ) + geom_errorbar(width = 0) +
+  geom_label_repel(nudge_y = 0.5, size = 2) + 
   theme_bw() +
   labs(x = "", y = "Average Marginal Effects of Being a Women Politician with a Migration Background") +
   facet_grid(issue~compromise, scales = "free") +

### 2021-05-06 report/draft.Rmd
add draft

---
title: "Bend or Break? Experimental Evidence of Voters' Punishment for Striking Political Compromises"
date: "`r format(Sys.time(), '%d %B, %Y - %X (%Z)')`"
output: 
  pdf_document:
    number_sections: true
editor_options: 
  chunk_output_type: console
bibliography: references.bib
urlcolor: blue
linkcolor: blue
header-includes:
   - \usepackage{floatrow}
   - \floatsetup[figure]{capposition=top}
   - \floatsetup[table]{capposition=top}
   - \usepackage{booktabs}
   - \usepackage{longtable}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{float}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{tabu}
   - \usepackage{threeparttable}
   - \usepackage{threeparttablex}
   - \usepackage[normalem]{ulem}
   - \usepackage{makecell}
   - \usepackage{xcolor}
---
```{r setup, include=FALSE}
## include this at top of your RMarkdown file for pretty output
## make sure to have the printr package installed: install.packages('printr')
library(knitr)
opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
library(tidyverse)
library(kableExtra)
options(kableExtra.latex.load_packages = FALSE)
library(here)
```

\newpage

# Introduction

# Acceptance of Political Compromises

# Data, Measurement & Method

```{r dv, fig.align = 'center', out.width = "75%", fig.cap = "Descriptive Overview Dependent Variable"}
include_graphics(here("report/figures", "Dependent Variable-1.png"))
```

```{r treatment, fig.align = 'center', out.width = "75%", fig.cap = "Treatment Distribution"}
include_graphics(here("report/figures", "Independent Variables-1.png"))
```

```{r balance, fig.align = 'center', out.width = "75%", fig.cap = "Balance Checks"}
include_graphics(here("report/figures", "balance-checks-1.png"))
```

```{r descriptive-table, echo = FALSE}
library(tidyverse)
load(here("data/intermediate/cleaned_data.RData"))
source(here("src/analysis/data-for-analyses.R"))
means <- d %>%
  summarise(F4 = round(mean(F4, na.rm = T),0),
            F5 = round(mean(F5, na.rm = T), 0),
            F6 = max(names(table(F6))),
            F7 = round(mean(F7, na.rm = T),0),
            F8 = round(mean(F8, na.rm = T),0),
            F9 = round(mean(F9, na.rm = T),0))

d <- d %>%
  mutate(F4 = replace_na(F4, means$F4),
         F5 = replace_na(F5, means$F5),
         F6 = replace_na(F6, means$F6),
         F7 = replace_na(F7, means$F7),
         missing_F8 = if_else(is.na(F8), 1, 0),
         F8 = replace_na(F8, means$F8),
         F9 = replace_na(F9, means$F9))
source(here("src/analysis/descriptive-information-overview.R"))
kbl(descr, booktabs =T, caption = "\\label{tab:descr}Descriptive Information",
    digits = 2) %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center")
rm(descr, d, means)  
```

# Bend or Break?

```{r h1, fig.align = 'center', out.width = "75%", fig.cap = "H1"}
include_graphics(here("report/figures", "h1-1.png"))
```

```{r h2, fig.align = 'center', out.width = "75%", fig.cap = "H2"}
include_graphics(here("report/figures", "h2-1.png"))
```

```{r h3, fig.align = 'center', out.width = "75%", fig.cap = "H3"}
include_graphics(here("report/figures", "h3-1.png"))
```

```{r h3p, fig.align = 'center', out.width = "75%", fig.cap = "H13 Pooled"}
include_graphics(here("report/figures", "h3-pooled-1.png"))
```

# Discussion

\newpage
# References

### 2021-05-06 report/draft.Rmd
add draft

@@
 linkcolor: blue
+abstract: "_ADD Abstract_"
 header-includes:

### 2021-05-06 report/draft.Rmd
updattes figures

--- 2021-05-06 report/draft.Rmd
@@
    number_sections: true
+   includes:
+      in_header: header.tex
 editor_options: 
@@
 opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
-library(tidyverse)
-library(kableExtra)
 options(kableExtra.latex.load_packages = FALSE)
-library(here)
+source(here::here("src/lib/functions.R"))
 ```
@@
 
-```{r treatment, fig.align = 'center', out.width = "75%", fig.cap = "Treatment Distribution"}
-include_graphics(here("report/figures", "Independent Variables-1.png"))
-```
-
-```{r balance, fig.align = 'center', out.width = "75%", fig.cap = "Balance Checks"}
-include_graphics(here("report/figures", "balance-checks-1.png"))
-```
-
 ```{r descriptive-table, echo = FALSE}
-library(tidyverse)
 load(here("data/intermediate/cleaned_data.RData"))
@@
                 full_width = F, fixed_thead = T, position = "center")
-rm(descr, d, means)  
+rm(descr, means)  
+```
+
+```{r balance, fig.align = 'center', out.width = "75%", fig.cap = "Balance Checks"}
+include_graphics(here("report/figures", "balance-checks-1.png"))
 ```
@@
 
-```{r h1, fig.align = 'center', out.width = "75%", fig.cap = "H1"}
-include_graphics(here("report/figures", "h1-1.png"))
+\newpage 
+\blandscape 
+```{r results-hs, fig.align = 'center', fig.cap = "Results"}
+include_graphics(here("report/figures", "save-patchwork-results-1.png"))
 ```
-
-```{r h2, fig.align = 'center', out.width = "75%", fig.cap = "H2"}
-include_graphics(here("report/figures", "h2-1.png"))
-```
-
-```{r h3, fig.align = 'center', out.width = "75%", fig.cap = "H3"}
-include_graphics(here("report/figures", "h3-1.png"))
-```
-
-```{r h3p, fig.align = 'center', out.width = "75%", fig.cap = "H13 Pooled"}
-include_graphics(here("report/figures", "h3-pooled-1.png"))
-```
+\elandscape
 

### 2021-05-06 src/analysis/Analysis.Rmd
updattes figures

@@
 ## Descriptive Results
-```{r "descriptive-results", echo=FALSE, fig.height=10, fig.width=8}
+```{r "descriptive-results", echo=FALSE, fig.height=15, fig.width=10}
 d %>%
@@
 As described in the Pre-Analysis Plan (p.10), I will add these covariates to the analyses as controls.
-```{r "balance-checks", fig.height=8, fig.width=8}
+
+```{r "balance-checks", fig.height=10, fig.width=10}
 source(here("src/analysis/balance-test.R"))
 df
+```
+
+```{r "visualize-unbalanced-vars", fig.height=10, fig.width=10}
+source(here("src/analysis/distribution_unbalanced_vars.R"))
+
+p1 + p2 + p3 + p4 + plot_layout(ncol=2)
 ```
@@
 ## Intersection Hypothesis -- Pooled
-```{r "h3-pooled", fig.align="center", fig.height=5, fig.width=5}
+```{r "h3-pooled", fig.align="center", fig.height=6, fig.width=6}
 source(here("src/analysis/h3-pooled.R"))
@@
 
+```{r "save-patchwork-results", echo = F, fig.show="hide", fig.height= 15, fig.width=15}
+h1 + h2 + h3 + h3p + plot_layout(ncol=2)
+```
+
 ## Exploration

### 2021-05-06 src/analysis/distribution_unbalanced_vars.R

@@ -1,0 +1,86 @@
+df <- d %>%
+  select(name, compromise, F2, F4, F7, F8, PreT2:PreT8,issue)  %>%
+  mutate(compromise = if_else(compromise==1, "Compromise", "No Compromise")) %>%
+  mutate_at(c("F2", "F4", "F7", "F8", "PreT2", "PreT3", "PreT4", "PreT5", "PreT6",
+              "PreT7_1", "PreT7_2", "PreT7_3", "PreT7_4", "PreT7_5", "PreT7_6",
+              "PreT7_7", "PreT8"), ~(scale(.) %>% as.vector)) %>%
+  pivot_longer(cols = F2:PreT8,
+               names_to = "variables") %>%
+  mutate(variables = recode(variables,
+                       `F2` = "Age",
+                       `F4` = "Urbaness",
+                       `F7` = "Employment",
+                       `F8` = "Income",
+                       `PreT2`  = "Position: Immigration",
+                       `PreT3`  = "Position: Defense",
+                       `PreT4`  = "Position: Education",
+                       `PreT5`  = "Attitude: Women in Politics",
+                       `PreT6`  = "Ideology",
+                       `PreT7_1` = "Political Efficacy (1)",
+                       `PreT7_2` = "Political Efficacy (2)",
+                       `PreT7_3` = "Political Efficacy (3)",
+                       `PreT7_4` = "Political Efficacy (4)",
+                       `PreT7_5` = "Political Efficacy (5)",
+                       `PreT7_6` = "Political Efficacy (6)",
+                       `PreT7_7` = "Political Efficacy (7)",
+                       `PreT8` = "Position: COVID-19")) 
+
+p1 <- df %>% filter(issue == "COVID") %>%
+ggplot(aes(x=variables, y=value, fill=name, color=name)) +
+  geom_violin(width=2.1, size=0.2) +
+  facet_grid(name~compromise, scales = "free") +
+  scale_fill_manual(values = fig_cols) +
+  scale_color_manual(values = fig_cols) +
+  labs(x = "", y = "", title = "COVID") +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5),
+        legend.position="none",
+        legend.title = element_blank(),
+        axis.text=element_text(size=8)) +
+  coord_flip() 
+
+p2 <- df %>% filter(issue == "Defense") %>%
[…]

### 2021-05-06 src/analysis/h1.R

@@ -16,10 +16,7 @@ for(i in 1:length(issues)){
 }
 
 h1 <- h1 %>%
-  mutate(id = if_else(y == "PT1", 1,
-              if_else(y == "PT2", 2,
-              if_else(y == "PT4", 3, 4))),
-         y = recode(y,
+  mutate(y = recode(y,
                     `PT1` = "DV: Trait Evaluation",
                     `PT2` = "DV: Favorability",
                     `PT3` = "DV: Representation",
@@ -27,27 +24,23 @@ h1 <- h1 %>%
          compromise = recode(compromise,
                     `1` = "Compromise (H1a)",
                     `0` = "No Compromise (H1b)")) %>%
-  ggplot(aes(x = reorder(id, AME), 
+  ggplot(aes(x = y, 
              y = AME,
-             color = y,
+             color = issue,
              ymin = lower,
              ymax = upper,
-             label = y)) +
-  geom_point(position = ) + geom_errorbar(width = 0) +
-  geom_label_repel(nudge_y = 0.5, size = 2) + 
-  theme_bw() +
+             label = issue)) +
+  geom_point(position = position_dodge(.2)) + 
+  geom_errorbar(position = position_dodge(.2), width = 0) +
+  geom_label_repel(nudge_x = 0.2,  nudge_y = 0.0, size = 4) + 
+  theme_minimal() +
   labs(x = "", y = "Average Marginal Effects of Being a Women Politician") +
-  facet_grid(issue~compromise, scales = "free") +
+  facet_grid(.~compromise, scales = "free") +
   theme(plot.title = element_text(hjust = 0.5),
         plot.subtitle = element_text(hjust = 0.5),
-        axis.title.y=element_blank(),
-        axis.text.y=element_blank(),
         legend.position="none",
-        legend.title = element_blank(),
-        axis.ticks.x=element_blank(),
-        axis.ticks.y = element_blank()) +
+        legend.title = element_blank()) +
   scale_color_manual(values = fig_cols) +
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") +
-  guides(color=guide_legend(nrow=1,byrow=TRUE)) +
   coord_flip()
 

### 2021-05-06 src/analysis/h2.R

@@ -16,38 +16,30 @@ for(i in 1:length(issues)){
 }
 
 h2 <- h2 %>%
-  mutate(id = if_else(y == "PT1", 1,
-              if_else(y == "PT2", 2,
-              if_else(y == "PT4", 3, 4))),
-         y = recode(y,
+  filter(compromise==1) %>%
+  mutate(y = recode(y,
                     `PT1` = "DV: Trait Evaluation",
                     `PT2` = "DV: Favorability",
                     `PT3` = "DV: Representation",
                     `PT4` = "DV: Career Prospects"),
          compromise = recode(compromise,
-                    `1` = "Compromise (H2)",
-                    `0` = "No Compromise (H1b)")) %>%
-  filter(compromise == "Compromise (H2)") %>%
-  ggplot(aes(x = reorder(id, AME), 
+                             `1` = "Compromise (H2)")) %>%
+  ggplot(aes(x = y, 
              y = AME,
-             color = y,
+             color = issue,
              ymin = lower,
              ymax = upper,
-             label = y)) +
-  geom_point(position = ) + geom_errorbar(width = 0) +
-  geom_label_repel(nudge_y = 0.5, size = 2) + 
-  theme_bw() +
+             label = issue)) +
+  geom_point(position = position_dodge(.2)) + 
+  geom_errorbar(position = position_dodge(.2), width = 0) +
+  geom_label_repel(nudge_x = 0.2,  nudge_y = 0.0, size = 4) + 
+  theme_minimal() +
   labs(x = "", y = "Average Marginal Effects of Being a Politician with a Migration Background") +
-  facet_grid(issue~compromise, scales = "free") +
+  facet_grid(.~compromise, scales = "free") +
   theme(plot.title = element_text(hjust = 0.5),
         plot.subtitle = element_text(hjust = 0.5),
-        axis.title.y=element_blank(),
-        axis.text.y=element_blank(),
-        legend.position="bottom",
-        legend.title = element_blank(),
-        axis.ticks.x=element_blank(),
-        axis.ticks.y = element_blank()) +
+        legend.position="none",
+        legend.title = element_blank()) +
   scale_color_manual(values = fig_cols) +
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") +
-  guides(color=guide_legend(nrow=1,byrow=TRUE)) +
   coord_flip()

### 2021-05-06 src/analysis/h3-pooled.R

@@ -2,12 +2,8 @@
 df <- d %>% select(a = intersection, compromise, PT1:PT4,issue, F2, F4, F7, F8, PreT2:PreT8)
 h3p <- pooled_regression(df, a, compromise, issue, 1)
 
-
 h3p <- h3p %>%
-  mutate(id = if_else(y == "PT1", 1,
-              if_else(y == "PT2", 2,
-              if_else(y == "PT4", 3, 4))),
-         y = recode(y,
+  mutate(y = recode(y,
                     `PT1` = "DV: Trait Evaluation",
                     `PT2` = "DV: Favorability",
                     `PT3` = "DV: Representation",
@@ -15,26 +11,20 @@ h3p <- h3p %>%
          compromise = recode(compromise,
                              `1` = "Compromise (H3a)",
                              `0` = "No Compromise (H3b)")) %>%
-  ggplot(aes(x = reorder(id, AME), 
+  ggplot(aes(x = y, 
              y = AME,
              color = y,
              ymin = lower,
              ymax = upper,
              label = y)) +
-  geom_point(position = ) + geom_errorbar(width = 0) +
-  geom_label_repel(nudge_y = 0.5, size = 2) + 
-  theme_bw() +
+  geom_point() + geom_errorbar(width = 0) +
+  theme_minimal() +
   labs(x = "", y = "Average Marginal Effects of Being a Women Politician with a Migration Background") +
   facet_grid(.~compromise, scales = "free") +
   theme(plot.title = element_text(hjust = 0.5),
         plot.subtitle = element_text(hjust = 0.5),
-        axis.title.y=element_blank(),
-        axis.text.y=element_blank(),
-        legend.position="bottom",
-        legend.title = element_blank(),
-        axis.ticks.x=element_blank(),
-        axis.ticks.y = element_blank()) +
+        legend.position="none",
+        legend.title = element_blank()) +
   scale_color_manual(values = fig_cols) +
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") +
-  guides(color=guide_legend(nrow=1,byrow=TRUE)) +
   coord_flip()

### 2021-05-06 src/analysis/h3.R

@@ -16,10 +16,7 @@ for(i in 1:length(issues)){
 }
 
 h3 <- h3 %>%
-  mutate(id = if_else(y == "PT1", 1,
-              if_else(y == "PT2", 2,
-              if_else(y == "PT4", 3, 4))),
-         y = recode(y,
+  mutate(y = recode(y,
                     `PT1` = "DV: Trait Evaluation",
                     `PT2` = "DV: Favorability",
                     `PT3` = "DV: Representation",
@@ -27,26 +24,22 @@ h3 <- h3 %>%
          compromise = recode(compromise,
                              `1` = "Compromise (H3a)",
                              `0` = "No Compromise (H3b)")) %>%
-  ggplot(aes(x = reorder(id, AME), 
+  ggplot(aes(x = y, 
              y = AME,
-             color = y,
+             color = issue,
              ymin = lower,
              ymax = upper,
-             label = y)) +
-  geom_point(position = ) + geom_errorbar(width = 0) +
-  geom_label_repel(nudge_y = 0.5, size = 2) + 
-  theme_bw() +
+             label = issue)) +
+  geom_point(position = position_dodge(.2)) + 
+  geom_errorbar(position = position_dodge(.2), width = 0) +
+  geom_label_repel(nudge_x = 0.2,  nudge_y = 0.0, size = 4) + 
+  theme_minimal() +
   labs(x = "", y = "Average Marginal Effects of Being a Women Politician with a Migration Background") +
-  facet_grid(issue~compromise, scales = "free") +
+  facet_grid(.~compromise, scales = "free") +
   theme(plot.title = element_text(hjust = 0.5),
         plot.subtitle = element_text(hjust = 0.5),
-        axis.title.y=element_blank(),
-        axis.text.y=element_blank(),
-        legend.position="bottom",
-        legend.title = element_blank(),
-        axis.ticks.x=element_blank(),
-        axis.ticks.y = element_blank()) +
+        legend.position="none",
+        legend.title = element_blank()) +
   scale_color_manual(values = fig_cols) +
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") +
-  guides(color=guide_legend(nrow=1,byrow=TRUE)) +
   coord_flip()

### 2021-05-06 src/lib/functions.R

@@ -11,7 +11,7 @@ library(ggstatsplot)
 library(ggrepel)
 library(haven)
 library(sjlabelled)
-
+library(patchwork)
 fig_cols <- yarrr::piratepal(palette = "basel", 
              trans = .2)
 fig_cols <- as.character(fig_cols[1:8])

### 2021-05-07 report/draft.Rmd
adapt figures

@@
 
+**Gender hypothesis** (_H1a_):  Women politicians are evaluated lower when striking a political compromise compared to men politicians.
+
+**Gender hypothesis** (_H1b_):  Women politicians are evaluated lower when not striking a political compromise compared to men politicians.
+
+**Migration hypothesis** (_H2_): Politicians with a migration background are evaluated lower when striking a political compromise compared to politicians without a migration background.
+
+**Intersection hypothesis** (_H3a_): Women politician with a migration background are evaluated lower when striking a political compromise compared to men politicians without a migration background.
+
+**Intersection hypothesis** (_H3b_): Women politician with a migration background are evaluated lower when not striking a political compromise compared to men politicians without a migration background.
+
 # Data, Measurement & Method
+The survey experiment is conducted in the Netherlands between the 21st of April 2021 and the 4th of May 2021.
+**WHY NL**
 
-```{r dv, fig.align = 'center', out.width = "75%", fig.cap = "Descriptive Overview Dependent Variable"}
+## Data
+Participants were told that they are taking part in a survey to get an overview of how Dutch people form their views on politics.
+The sample, recruited through [KiesKompas](https://www.kieskompas.nl/en/),  consists of 2,004 participants of 18 years and older.[^1]
+Because Kieskompas works with non-random opt-in respondents, I have measured many demographic and political background variables (described in [Section 3.2](#measurement) under _Covariates_).
+Balance checks are conducted to demonstrate whether certain categories are over represented in a certain experimental group (see [Section 3.3](#method), Figure \ref{fig:balance}).
+The study has been approved by the [Research Ethics Review Committee](https://fsw.vu.nl/nl/onderzoek/research-ethics-review/index.aspx) of the _Vrije Universiteit Amsterdam_ (see the approval [here](https://github.com/MarikenvdVelden/compromise-punish/blob/main/docs/EthicalApproval.pdf)).
+To ensure good quality of our data, two attention checks (discussed in more detail in [Section 3.3 of the Pre-Analysis Plan](https://github.com/MarikenvdVelden/bend-break-compromise/blob/main/docs/pap/compromise-punishment-pap.pdf)) are included.
+All respondents included in the analyses passed both attention checks.
+
+[^1]: The sample is calculated based on a power analysis presented in the [Pre-Analysis Plan](https://github.com/MarikenvdVelden/bend-break-compromise/blob/main/docs/pap/compromise-punishment-pap.pdf).
+
+## Measurement
+
+**_Dependent Variables_**
+I rely on four measures reflecting different aspects of how people judge politicians.
+The evaluation of politicians' character traits are statements deriving from @aaldering2016political.
+The other three neasures to evaluate the politician of the treatment are translated from @bauer2017punished -- i.e. favorability, representation, and career perspectives.
+General favorability is shown to be related to vote choice [@elis2010dynamics], perceptions of represenation are related to legislative compromise and cooperation [@doherty2013whom], and career perspective is included because critiques of women are typically manifested in their leadership skills [@eagly2007female].
+
+```{r dv, fig.align = 'center', out.width = "90%", fig.cap = "\\label{fig:descr_dv}Descriptive Overview Dependent Variable"}
 include_graphics(here("report/figures", "Dependent Variable-1.png"))
 ```
+
+**_Experimental Conditions_**
+The stimuli in the experiment are news messages in the same style as the Dutch news website [nu.nl](https://www.nu.nl/).
+In these news messages, we manipulate: a) the _gender_ of the politician (male vs.
+female); b) the _migration background_ of the politician (based on a Arabic sounding name (Rachid(a) Amezian) or a native Dutch sounding name (Karel/Karin van der Kleijn)); and c) whether the politician _striked a compromise or not_.
+This creates a full `2*2*2` factorial experiment with four rounds (see Table \ref{tab:treat}).
+Every round, the news message covers a new issue.
+The issues are: "defense" (increase cooperation of the defense units), "immigration" (immigration stop in western countries), "education" (expansion creative elementary school activities), "COVID-19" (emergency legislation to combat the COVID-19 pandemic).
+For every round, the politicians' name, and thereby gender and immigration background, are manipulated in the text and in the picture, as well as the decision to strike a compromise.
+
+```{r stimulus, topcaption=TRUE}
+d <- tibble(` ` = c(1:8),
+            `Name Politician` = c(rep("Rachid Amezian", 2), rep("Karel van der Kleijn", 2),
+                                  rep("Rachida Amezian", 2), rep("Karin van der Kleijn", 2)),
+            Gender = c(rep("Men",4), rep("Women", 4)),
+            `Migration Background` = c(rep("Yes", 2), rep("No", 2),
+                                  rep("Yes", 2), rep("No", 2)),
+            Compromise = c("Yes", "No", "Yes", "No", "Yes", "No", "Yes", "No"))
+
+kbl(d, booktabs =T, caption = "\\label{tab:treat}Experimental Conditions",
+    align = c("l", "l", "c", "c", "c")) %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = ".5cm") %>%
+  column_spec(2, width = "3.2cm") %>%
+  column_spec(3, width = "2.5cm")%>%
+  column_spec(4, width = "3.5cm")%>%
+  column_spec(5, width = "2.5cm")
+
+```
+
+The text of the treatment is a Dutch translation of the stimulus material developed by @bauer2017punished.
+The authors have pre-tested the text of the stimuli material several times [see the [Web Appendix](https://static-content.springer.com/esm/art%3A10.1007%2Fs11109-016-9356-6/MediaObjects/11109_2016_9356_MOESM1_ESM.docx) of @bauer2017punished].
+The photo's of their stimuli material can unfortunately not be used, because a) @bauer2017punished only investigate the difference between men and women politicians, using solely photo''s of caucasians; and b) the American flag was present in their material.
+Instead, I have used photo's from local politicians of the city of The Hague that are not know to the general public. 
+The men politicians are in real life representatives of the [liberal-progressive party D66](https://www.denhaag.nl/nl/bestuur-en-organisatie/gemeenteraad/raadsleden-en-fractievertegenwoordigers/boutkabout-a.-abid-fractievertegenwoordiger-d66.htm) (man with immigrant background) and of the [christian democratic party CDA](https://www.denhaag.nl/nl/bestuur-en-organisatie/gemeenteraad/raadsleden-en-fractievertegenwoordigers/groot-de-d.p.-daniel-fractievertegenwoordiger-cda.htm) (man without immigrant background).
+The women politicians are in real life representatives of a [right-wing populist party _Hart voor Den Haag/ Groep de Mos_](https://www.denhaag.nl/nl/bestuur-en-organisatie/gemeenteraad/raadsleden-en-fractievertegenwoordigers/davituliani-n.-nino-raadslid-hart-voor-den-haaggroep-de-mos.htm) (woman with migration background) and of the [social democratic party PvdA](https://www.denhaag.nl/nl/bestuur-en-organisatie/gemeenteraad/raadsleden-en-fractievertegenwoordigers/holman-j.-janneke-raadslid-pvda.htm) (woman without immigrant background).
+Thereby we have a spread over the ideological different parties present in Dutch politics.
+The names for the politicians without immigration background are _Karel_ (man) and _Karin_ (woman) _van der Kleijn_, which are typical native Dutch names.
+For the politicians with an immigration background, we picked _Rachid_ (man) and _Rachida_ (woman) _Amezian_.
+All stimulus material is developed by the [Network Institute of the _Vrije Universiteit Amsterdam_](https://networkinstitute.org/) and can be accessed [here](https://github.com/MarikenvdVelden/compromise-punish/tree/main/docs/pap/treatments).
+
+**_Covariates_**
 
@@
 
-```{r balance, fig.align = 'center', out.width = "75%", fig.cap = "Balance Checks"}
+## Method
+
+```{r balance, fig.align = 'center', out.width = "95%", fig.cap = "\\label{fig:balance}Balance Checks"}
 include_graphics(here("report/figures", "balance-checks-1.png"))
@@
 
+## Pre-Registered Hypotheses
 \newpage 
 \blandscape 
-```{r results-hs, fig.align = 'center', fig.cap = "Results"}
+```{r results-hs, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results}Results"}
 include_graphics(here("report/figures", "save-patchwork-results-1.png"))
@@
 \elandscape
+
+## Exploration
 

### 2021-05-07 src/analysis/Analysis.Rmd
adapt figures

@@
 
-```{r "visualize-unbalanced-vars", fig.height=10, fig.width=10}
+```{r "visualize-unbalanced-vars", fig.height=15, fig.width=20}
 source(here("src/analysis/distribution_unbalanced_vars.R"))
-
 p1 + p2 + p3 + p4 + plot_layout(ncol=2)
@@
 source(here("src/analysis/h1.R"))
-h1
+p1
 ```
@@
 source(here("src/analysis/h2.R"))
-h2
+p2
 ```
@@
 source(here("src/analysis/h3.R"))
-h3
+p3
 ```
@@
 source(here("src/analysis/h3-pooled.R"))
-h3p
+p3p
 ```
 
-```{r "save-patchwork-results", echo = F, fig.show="hide", fig.height= 15, fig.width=15}
-h1 + h2 + h3 + h3p + plot_layout(ncol=2)
+```{r "save-patchwork-results", echo = F, fig.show="hide", fig.height= 15, fig.width=20}
+p1 + p2 + p3 + p3p + plot_layout(ncol=2)
 ```

### 2021-05-07 src/data-processing/prep_data.Rmd
adapt figures

@@
 ### Dependent Variable
-```{r "Dependent Variable", echo=F}
+```{r "Dependent Variable", echo=F, fig.width=10, fig.height=8}
 d %>%
@@
   mutate(issue = recode(issue, 
-                        name_C = "COVID_19",
+                        name_C = "COVID",
                         name_D = "Defense",
@@
   mutate(issue1 = recode(issue1, 
-                        PT_C1 = "COVID_19",
+                        PT_C1 = "COVID",
                         PT_D1 = "Defense",
@@
   mutate(issue2 = recode(issue2, 
-                        PT_C2 = "COVID_19",
+                        PT_C2 = "COVID",
                         PT_D2 = "Defense",
@@
   mutate(issue3 = recode(issue3, 
-                         PT_C3 = "COVID_19",
+                         PT_C3 = "COVID",
                          PT_D3 = "Defense",
@@
   mutate(issue4 = recode(issue4, 
-                         PT_C4 = "COVID_19",
+                         PT_C4 = "COVID",
                          PT_D4 = "Defense",
@@
   select(PT1, PT2, PT3, PT4, issue = issue1) %>%
+  mutate(PT1 = PT1 * 2) %>%
+  #mutate_at(c("PT1", "PT2", "PT3", "PT4"), ~(scale(.) %>% as.vector)) %>%
   pivot_longer(cols = PT1:PT4,
@@
              ymin = lower, ymax = upper, label = issue)) +
-  geom_point(position = position_dodge(.2)) + 
-  geom_errorbar(position = position_dodge(.2), width = 0) +
-  geom_label_repel(nudge_x = 0.35,nudge_y = 0.5, size = 4) + 
+  geom_point(position = position_dodge(.5)) + 
+  geom_errorbar(position = position_dodge(.5), width = 0) +
+  geom_text(aes(y = upper +.5), 
+            position = position_dodge(.5),na.rm = TRUE) + 
   labs(y = "0 (negative) - 10 (positive)", 
-       x = "", title = "Evaluation of Politicians") +
+       x = "") +
   geom_hline(yintercept = 5, linetype = "dotted", color = "darkgrey") +

### 2021-05-07 src/analysis/balance-test.R

@@ -86,12 +86,17 @@ df <- df %>%
                                       "Income",  "Education: High", "Education: Middle", "Education: Low")),
          difference = Diff.Un,2) %>%
   select(variable, difference) %>%
-  ggplot(aes(x = variable, y = difference)) +
-  geom_point(size = 3, colour = "gray55") +
+  mutate(type = if_else(difference <= -.05, "below",
+                if_else(difference >= .05, "below", "above"))) %>%
+  ggplot(aes(x = variable, y = difference, color = type)) +
+  geom_point(size = 3) +
+  scale_color_manual(values = c("above"=fig_cols[3],
+                                "below"=fig_cols[2])) +
+  
   theme_bw() +
   labs(x="", y= "Standardized Mean Differences") +
-  ggtitle("Covariate Balance") +
-  theme(plot.title = element_text(hjust = 0.5)) +
+  theme(plot.title = element_text(hjust = 0.5),
+        legend.position="none",) +
   geom_hline(yintercept = 0) +
   geom_hline(yintercept = 0.05, linetype = "dashed") +
   geom_hline(yintercept = -0.05, linetype = "dashed") +

### 2021-05-07 src/analysis/h1.R

@@ -15,7 +15,7 @@ for(i in 1:length(issues)){
   }
 }
 
-h1 <- h1 %>%
+p1 <- h1 %>%
   mutate(y = recode(y,
                     `PT1` = "DV: Trait Evaluation",
                     `PT2` = "DV: Favorability",
@@ -30,12 +30,14 @@ h1 <- h1 %>%
              ymin = lower,
              ymax = upper,
              label = issue)) +
-  geom_point(position = position_dodge(.2)) + 
-  geom_errorbar(position = position_dodge(.2), width = 0) +
-  geom_label_repel(nudge_x = 0.2,  nudge_y = 0.0, size = 4) + 
+  geom_point(position = position_dodge(.5)) + 
+  geom_errorbar(position = position_dodge(.5), width = 0) +
+  geom_text(aes(y = upper +.12), position = position_dodge(.5),na.rm = TRUE) + 
   theme_minimal() +
-  labs(x = "", y = "Average Marginal Effects of Being a Women Politician") +
-  facet_grid(.~compromise, scales = "free") +
+  labs(x = "", y = "Average Marginal Effects of Being a Women Politician",
+       title = "Gender Hypothesis") +
+  facet_grid(.~compromise) +
+  ylim(c(-.3, .7)) +
   theme(plot.title = element_text(hjust = 0.5),
         plot.subtitle = element_text(hjust = 0.5),
         legend.position="none",

### 2021-05-07 src/analysis/h2.R

@@ -15,27 +15,29 @@ for(i in 1:length(issues)){
   }
 }
 
-h2 <- h2 %>%
-  filter(compromise==1) %>%
+p2 <- h2 %>%
   mutate(y = recode(y,
                     `PT1` = "DV: Trait Evaluation",
                     `PT2` = "DV: Favorability",
                     `PT3` = "DV: Representation",
                     `PT4` = "DV: Career Prospects"),
          compromise = recode(compromise,
-                             `1` = "Compromise (H2)")) %>%
+                             `1` = "Compromise (H2)",
+                             `0` = "No Compromise")) %>%
   ggplot(aes(x = y, 
              y = AME,
              color = issue,
              ymin = lower,
              ymax = upper,
              label = issue)) +
-  geom_point(position = position_dodge(.2)) + 
-  geom_errorbar(position = position_dodge(.2), width = 0) +
-  geom_label_repel(nudge_x = 0.2,  nudge_y = 0.0, size = 4) + 
+  geom_point(position = position_dodge(.5)) + 
+  geom_errorbar(position = position_dodge(.5), width = 0) +
+  geom_text(aes(y = upper +.15), position = position_dodge(.5),na.rm = TRUE) + 
   theme_minimal() +
-  labs(x = "", y = "Average Marginal Effects of Being a Politician with a Migration Background") +
-  facet_grid(.~compromise, scales = "free") +
+  labs(x = "", y = "Average Marginal Effects of Being a Politician with a Migration Background",
+       title = "Migration Hypothesis") +
+  facet_grid(.~compromise) +
+  ylim(c(-.7, .9)) +
   theme(plot.title = element_text(hjust = 0.5),
         plot.subtitle = element_text(hjust = 0.5),
         legend.position="none",

### 2021-05-07 src/analysis/h3-pooled.R

@@ -2,7 +2,7 @@
 df <- d %>% select(a = intersection, compromise, PT1:PT4,issue, F2, F4, F7, F8, PreT2:PreT8)
 h3p <- pooled_regression(df, a, compromise, issue, 1)
 
-h3p <- h3p %>%
+p3p <- h3p %>%
   mutate(y = recode(y,
                     `PT1` = "DV: Trait Evaluation",
                     `PT2` = "DV: Favorability",
@@ -19,8 +19,9 @@ h3p <- h3p %>%
              label = y)) +
   geom_point() + geom_errorbar(width = 0) +
   theme_minimal() +
-  labs(x = "", y = "Average Marginal Effects of Being a Women Politician with a Migration Background") +
-  facet_grid(.~compromise, scales = "free") +
+  labs(x = "", y = "Average Marginal Effects of Being a Women Politician with a Migration Background",
+       title = "Intersection Hypothesis (Pooled)") +
+  facet_grid(.~compromise) +
   theme(plot.title = element_text(hjust = 0.5),
         plot.subtitle = element_text(hjust = 0.5),
         legend.position="none",

### 2021-05-07 src/analysis/h3.R

@@ -15,7 +15,7 @@ for(i in 1:length(issues)){
   }
 }
 
-h3 <- h3 %>%
+p3 <- h3 %>%
   mutate(y = recode(y,
                     `PT1` = "DV: Trait Evaluation",
                     `PT2` = "DV: Favorability",
@@ -30,12 +30,14 @@ h3 <- h3 %>%
              ymin = lower,
              ymax = upper,
              label = issue)) +
-  geom_point(position = position_dodge(.2)) + 
-  geom_errorbar(position = position_dodge(.2), width = 0) +
-  geom_label_repel(nudge_x = 0.2,  nudge_y = 0.0, size = 4) + 
+  geom_point(position = position_dodge(.5)) + 
+  geom_errorbar(position = position_dodge(.5), width = 0) +
+  geom_text(aes(y = upper +.12), position = position_dodge(.5),na.rm = TRUE) + 
   theme_minimal() +
-  labs(x = "", y = "Average Marginal Effects of Being a Women Politician with a Migration Background") +
-  facet_grid(.~compromise, scales = "free") +
+  labs(x = "", y = "Average Marginal Effects of Being a Women Politician with a Migration Background",
+       title = "Intersection Hypothesis") +
+  facet_grid(.~compromise) +
+  ylim(c(-.7,.7)) +
   theme(plot.title = element_text(hjust = 0.5),
         plot.subtitle = element_text(hjust = 0.5),
         legend.position="none",

### 2021-05-07 src/data-processing/Urbaness.R

@@ -4,9 +4,10 @@
 #  distinct() %>%
 #  write_csv(here("data/raw-private-encrypted/Urbaness_NL.csv"))
 
-codes <- read_csv(here("data/raw-private-encrypted/Urbaness_NL.csv")) %>%
+codes <- read_csv(here("data/raw-private/Urbaness_NL.csv")) %>%
   select(Urbaness = F4, F4 = F4_1_TEXT)
 
 d <- left_join(d, codes, by = "F4") %>%
   select(-F4) %>%
   select(id:F3, F4 = Urbaness, F5:order_PT_I)
+rm(codes)

### 2021-05-07 src/data-processing/tidy_data.R

@@ -1,5 +1,5 @@
 # Tidy Qualtrics Data
-pret <- read_sav(here("data/raw-private-encrypted/experiment.sav")) %>%
+pret <- read_sav(here("data/raw-private/experiment.sav")) %>%
   remove_all_labels() %>%
   filter(Consent == 1, Attention2_3 ==1, Attention2_5==1) %>%
   select(matches("PreT\\d"), id = ResponseId) %>%
@@ -14,13 +14,13 @@ pret <- read_sav(here("data/raw-private-encrypted/experiment.sav")) %>%
                         `12` = 2, `11` = 1))) %>%
   drop_na()
 
-tr <- read_sav(here("data/raw-private-encrypted/experiment.sav")) %>%
+tr <- read_sav(here("data/raw-private/experiment.sav")) %>%
   remove_all_labels() %>%
   filter(Consent == 1, Attention2_3 ==1, Attention2_5==1) %>%
   select(matches("name_[A-Z]"), compromis, id = ResponseId) %>%
   drop_na(name_I, name_E)
 
-pt <- read_sav(here("data/raw-private-encrypted/experiment.sav")) %>%
+pt <- read_sav(here("data/raw-private/experiment.sav")) %>%
   remove_all_labels() %>%
   filter(Consent == 1, Attention2_3 ==1, Attention2_5==1) %>%
   select(matches("PT_[A-Z]\\d"), id = ResponseId) %>%
@@ -38,7 +38,7 @@ pt <- read_sav(here("data/raw-private-encrypted/experiment.sav")) %>%
          order_PT_C1, order_PT_C, order_PT_D1, order_PT_D,
          order_PT_E1, order_PT_E, order_PT_I1, order_PT_I)
 
-bg <- read_sav(here("data/raw-private-encrypted/experiment.sav")) %>%
+bg <- read_sav(here("data/raw-private/experiment.sav")) %>%
   remove_all_labels() %>%
   filter(Consent == 1, Attention2_3 ==1, Attention2_5==1) %>%
   select(id = ResponseId, matches("F\\d"), etnicity) %>%

### 2021-05-07 report/draft.Rmd
add exploratory results

@@
 \blandscape 
-```{r results-hs, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results}Results"}
+```{r results-main, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results}Results"}
 include_graphics(here("report/figures", "save-patchwork-results-1.png"))
@@
 
+**_Ideology_**
+\newpage 
+\blandscape 
+```{r results-ideology, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-ideology}Results: Interaction with Ideology"}
+include_graphics(here("report/figures", "explore-ideology-1.png"))
+```
+\elandscape
+
+**_Willingness to Accept Compromises_**
+\newpage 
+\blandscape 
+```{r results-wtac, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-wtac}Results: Interaction with Willingness to Accept Compromise"}
+include_graphics(here("report/figures", "explore-wtac-1.png"))
+```
+\elandscape
+
+**_Attitude towards Women in Politics_**
+\newpage 
+\blandscape 
+```{r results-women-politics, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-women-politics}Results: Interaction with Attitudes towards Women in Politics"}
+include_graphics(here("report/figures", "explore-women-politics-1.png"))
+```
+\elandscape
+
+**_Position on Political Issues_**
+\newpage 
+\blandscape 
+```{r results-covid, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-covid}Results: Interaction with Position on COVID-19"}
+include_graphics(here("report/figures", "explore-covid-1.png"))
+```
+\elandscape
+
+\newpage 
+\blandscape 
+```{r results-defense, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-defense}Results: Interaction with Position on Defense"}
+include_graphics(here("report/figures", "explore-defense-1.png"))
+```
+\elandscape
+
+\newpage 
+\blandscape 
+```{r results-education, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-education}Results: Interaction with Position on Education"}
+include_graphics(here("report/figures", "explore-education-1.png"))
+```
+\elandscape
+
+\newpage 
+\blandscape 
+```{r results-immigration, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-immigration}Results: Interaction with Position on Immigration"}
+include_graphics(here("report/figures", "explore-immigration-1.png"))
+```
+\elandscape
+
 # Discussion

### 2021-05-07 src/analysis/Analysis.Rmd
add exploratory results

@@
 ## Exploration
+
+### Ideology
+```{r "explore-ideology", echo = F, fig.height= 10, fig.width=20}
+source(here("src/analysis/explore_ideology.R"))
+p1e + p2e + p3e + plot_layout(ncol=3)
+```
+
+### Willingness to Accept Compromise
+```{r "explore-wtac", echo = F, fig.height= 10, fig.width=20}
+source(here("src/analysis/explore_wtac.R"))
+p1e + p2e + p3e + plot_layout(ncol=3)
+```
+
+### Attitude towards Women in Politics
+```{r "explore-women-politics", echo = F, fig.height= 10, fig.width=20}
+source(here("src/analysis/explore_women_politics.R"))
+p1e + p2e + p3e + plot_layout(ncol=3)
+```
+
+### Position on COVID-19
+```{r "explore-covid", echo = F, fig.height= 10, fig.width=20}
+source(here("src/analysis/explore_position_covid.R"))
+p1e + p2e + p3e + plot_layout(ncol=3)
+```
+
+### Position on Defense
+```{r "explore-defense", echo = F, fig.height= 10, fig.width=20}
+source(here("src/analysis/explore_position_defense.R"))
+p1e + p2e + p3e + plot_layout(ncol=3)
+```
+
+### Position on Education
+```{r "explore-education", echo = F, fig.height= 10, fig.width=20}
+source(here("src/analysis/explore_position_education.R"))
+p1e + p2e + p3e + plot_layout(ncol=3)
+```
+
+### Position on Immigration
+```{r "explore-immigration", echo = F, fig.height= 20, fig.width=20}
+source(here("src/analysis/explore_position_immigration.R"))
+p1e + p2e + p3e + p4e + p5e + p6e + plot_layout(ncol=3)
+```

### 2021-05-07 src/analysis/explore_ideology.R

@@ -1,0 +1,117 @@
+regression_explore <- function(df, a, b, compromise, issue){
+  
+  depVarList <- df %>% select(matches("PT[0-9]"))
+  indepVarList <- df %>% select(a, b, compromise, F2, F4, F7, F8, 
+                                PreT2:PreT5, PreT7_1:PreT8, issue)   
+  allModels <- apply(depVarList,2,function(xl)lmer(xl ~ a * compromise * b +
+                                                     F2 + F4 + F7 + F8 +
+                                                     PreT2 + PreT3 + PreT4 + PreT5 +
+                                                     PreT7_1 + PreT7_2 +
+                                                     PreT7_3 + PreT7_4 + PreT7_5 + 
+                                                     PreT7_6 + PreT7_7 + PreT8  +
+                                                     (1 | issue), 
+                                                   data= indepVarList))
+  depVarList <- df %>% select(matches("PT[0-9]")) %>% colnames()
+  
+  for(i in 1:length(depVarList)){
+    if(i==1){
+      m <- summary(margins(allModels[[i]], variables = "a", at = list(compromise = 0:1, b = fivenum(df$b)))) %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.56 * SE),
+               upper = AME + (1.56 * SE)) %>%
+        select(AME, upper, lower, y, compromise, b)
+    }
+    else{
+      tmp <- summary(margins(allModels[[i]], variables = "a", at = list(compromise = 0:1, b = fivenum(df$b)))) %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.56 * SE),
+               upper = AME + (1.56 * SE)) %>%
+        select(AME, upper, lower, y, compromise, b)
+      m <- m %>%
+        add_case(tmp)
+      
+    }
+  }
+  return(m)
+}
+
+df <- d %>% select(a = gender, b = PreT6, compromise, 
+                   PT1:PT4, F2, F4, F7, F8, PreT2:PreT5, 
+                   PreT7_1:PreT8, issue) 
+e1 <- regression_explore(df, a, b, compromise)
+
+p1e <- e1 %>%
+  mutate(y = recode(y,
+                    `PT1` = "DV: Trait Evaluation",
+                    `PT2` = "DV: Favorability",
+                    `PT3` = "DV: Representation",
+                    `PT4` = "DV: Career Prospects"),
[…]

### 2021-05-07 src/analysis/explore_position_covid.R

@@ -1,0 +1,117 @@
+regression_explore <- function(df, a, b, compromise, issue){
+  
+  depVarList <- df %>% select(matches("PT[0-9]"))
+  indepVarList <- df %>% select(a, b, compromise, F2, F4, F7, F8, 
+                                PreT2:PreT7_7, issue)   
+  allModels <- apply(depVarList,2,function(xl)lmer(xl ~ a * compromise * b +
+                                                     F2 + F4 + F7 + F8 +
+                                                     PreT2 + PreT3 + PreT4 + PreT5 +
+                                                     PreT6 + PreT7_1 + PreT7_2 +
+                                                     PreT7_3 + PreT7_4 + PreT7_5 + 
+                                                     PreT7_6 + PreT7_7 +
+                                                     (1 | issue), 
+                                                   data= indepVarList))
+  depVarList <- df %>% select(matches("PT[0-9]")) %>% colnames()
+  
+  for(i in 1:length(depVarList)){
+    if(i==1){
+      m <- summary(margins(allModels[[i]], variables = "a", at = list(compromise = 0:1, b = fivenum(df$b)))) %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.56 * SE),
+               upper = AME + (1.56 * SE)) %>%
+        select(AME, upper, lower, y, compromise, b)
+    }
+    else{
+      tmp <- summary(margins(allModels[[i]], variables = "a", at = list(compromise = 0:1, b = fivenum(df$b)))) %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.56 * SE),
+               upper = AME + (1.56 * SE)) %>%
+        select(AME, upper, lower, y, compromise, b)
+      m <- m %>%
+        add_case(tmp)
+      
+    }
+  }
+  return(m)
+}
+
+df <- d %>% select(a = gender, b = PreT8, compromise, 
+                   PT1:PT4, F2, F4, F7, F8, PreT2:PreT7_7, issue) 
+e1 <- regression_explore(df, a, b, compromise)
+
+p1e <- e1 %>%
+  mutate(y = recode(y,
+                    `PT1` = "DV: Trait Evaluation",
+                    `PT2` = "DV: Favorability",
+                    `PT3` = "DV: Representation",
+                    `PT4` = "DV: Career Prospects"),
+         compromise = recode(compromise,
[…]

### 2021-05-07 src/analysis/explore_position_defense.R

@@ -1,0 +1,117 @@
+regression_explore <- function(df, a, b, compromise, issue){
+  
+  depVarList <- df %>% select(matches("PT[0-9]"))
+  indepVarList <- df %>% select(a, b, compromise, F2, F4, F7, F8, 
+                                PreT2, PreT4:PreT8, issue)   
+  allModels <- apply(depVarList,2,function(xl)lmer(xl ~ a * compromise * b +
+                                                     F2 + F4 + F7 + F8 +
+                                                     PreT2 + PreT4 + PreT5 +
+                                                     PreT6 + PreT7_1 + PreT7_2 +
+                                                     PreT7_3 + PreT7_4 + PreT7_5 + 
+                                                     PreT7_6 + PreT7_7 + PreT8 +
+                                                     (1 | issue), 
+                                                   data= indepVarList))
+  depVarList <- df %>% select(matches("PT[0-9]")) %>% colnames()
+  
+  for(i in 1:length(depVarList)){
+    if(i==1){
+      m <- summary(margins(allModels[[i]], variables = "a", at = list(compromise = 0:1, b = fivenum(df$b)))) %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.56 * SE),
+               upper = AME + (1.56 * SE)) %>%
+        select(AME, upper, lower, y, compromise, b)
+    }
+    else{
+      tmp <- summary(margins(allModels[[i]], variables = "a", at = list(compromise = 0:1, b = fivenum(df$b)))) %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.56 * SE),
+               upper = AME + (1.56 * SE)) %>%
+        select(AME, upper, lower, y, compromise, b)
+      m <- m %>%
+        add_case(tmp)
+      
+    }
+  }
+  return(m)
+}
+
+df <- d %>% select(a = gender, b = PreT3, compromise, 
+                   PT1:PT4, F2, F4, F7, F8, PreT2, PreT4:PreT8, issue) 
+e1 <- regression_explore(df, a, b, compromise)
+
+p1e <- e1 %>%
+  mutate(y = recode(y,
+                    `PT1` = "DV: Trait Evaluation",
+                    `PT2` = "DV: Favorability",
+                    `PT3` = "DV: Representation",
+                    `PT4` = "DV: Career Prospects"),
+         compromise = recode(compromise,
[…]

### 2021-05-07 src/analysis/explore_position_education.R

@@ -1,0 +1,117 @@
+regression_explore <- function(df, a, b, compromise, issue){
+  
+  depVarList <- df %>% select(matches("PT[0-9]"))
+  indepVarList <- df %>% select(a, b, compromise, F2, F4, F7, F8, 
+                                PreT2, PreT3, PreT5:PreT8, issue)   
+  allModels <- apply(depVarList,2,function(xl)lmer(xl ~ a * compromise * b +
+                                                     F2 + F4 + F7 + F8 +
+                                                     PreT2 + PreT3 + PreT5 +
+                                                     PreT6 + PreT7_1 + PreT7_2 +
+                                                     PreT7_3 + PreT7_4 + PreT7_5 + 
+                                                     PreT7_6 + PreT7_7 + PreT8 +
+                                                     (1 | issue), 
+                                                   data= indepVarList))
+  depVarList <- df %>% select(matches("PT[0-9]")) %>% colnames()
+  
+  for(i in 1:length(depVarList)){
+    if(i==1){
+      m <- summary(margins(allModels[[i]], variables = "a", at = list(compromise = 0:1, b = fivenum(df$b)))) %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.56 * SE),
+               upper = AME + (1.56 * SE)) %>%
+        select(AME, upper, lower, y, compromise, b)
+    }
+    else{
+      tmp <- summary(margins(allModels[[i]], variables = "a", at = list(compromise = 0:1, b = fivenum(df$b)))) %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.56 * SE),
+               upper = AME + (1.56 * SE)) %>%
+        select(AME, upper, lower, y, compromise, b)
+      m <- m %>%
+        add_case(tmp)
+      
+    }
+  }
+  return(m)
+}
+
+df <- d %>% select(a = gender, b = PreT4, compromise, 
+                   PT1:PT4, F2, F4, F7, F8, PreT2, PreT3, PreT5:PreT8, issue) 
+e1 <- regression_explore(df, a, b, compromise)
+
+p1e <- e1 %>%
+  mutate(y = recode(y,
+                    `PT1` = "DV: Trait Evaluation",
+                    `PT2` = "DV: Favorability",
+                    `PT3` = "DV: Representation",
+                    `PT4` = "DV: Career Prospects"),
[…]

### 2021-05-07 src/analysis/explore_position_immigration.R

@@ -1,0 +1,235 @@
+regression_explore <- function(df, a, b, compromise, issue){
+  
+  depVarList <- df %>% select(matches("PT[0-9]"))
+  indepVarList <- df %>% select(a, b, compromise, F2, F4, F7, F8, 
+                                PreT2:PreT8, issue)   
+  allModels <- apply(depVarList,2,function(xl)lmer(xl ~ a * compromise * b +
+                                                     F2 + F4 + F7 + F8 +
+                                                     PreT2 + PreT3 + PreT4 + PreT5 +
+                                                     PreT6 + PreT7_1 + PreT7_2 +
+                                                     PreT7_3 + PreT7_4 + PreT7_5 + 
+                                                     PreT7_6 + PreT7_7 + PreT8  +
+                                                     (1 | issue), 
+                                                   data= indepVarList))
+  depVarList <- df %>% select(matches("PT[0-9]")) %>% colnames()
+  
+  for(i in 1:length(depVarList)){
+    if(i==1){
+      m <- summary(margins(allModels[[i]], variables = "a", at = list(compromise = 0:1, b = fivenum(df$b)))) %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.56 * SE),
+               upper = AME + (1.56 * SE)) %>%
+        select(AME, upper, lower, y, compromise, b)
+    }
+    else{
+      tmp <- summary(margins(allModels[[i]], variables = "a", at = list(compromise = 0:1, b = fivenum(df$b)))) %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.56 * SE),
+               upper = AME + (1.56 * SE)) %>%
+        select(AME, upper, lower, y, compromise, b)
+      m <- m %>%
+        add_case(tmp)
+      
+    }
+  }
+  return(m)
+}
+
+df <- d %>% select(a = gender, b = PreT1, compromise, 
+                   PT1:PT4, F2, F4, F7, F8, PreT2:PreT8, issue) 
+e1 <- regression_explore(df, a, b, compromise)
+
+p1e <- e1 %>%
+  mutate(y = recode(y,
+                    `PT1` = "DV: Trait Evaluation",
+                    `PT2` = "DV: Favorability",
+                    `PT3` = "DV: Representation",
+                    `PT4` = "DV: Career Prospects"),
+         compromise = recode(compromise,
[…]

### 2021-05-07 src/analysis/explore_women_politics.R

@@ -1,0 +1,120 @@
+regression_explore <- function(df, a, b, compromise, issue){
+  
+  depVarList <- df %>% select(matches("PT[0-9]"))
+  indepVarList <- df %>% select(a, b, compromise, F2, F4, F7, F8, 
+                                PreT2:PreT4, PreT6:PreT8, issue)   
+  allModels <- apply(depVarList,2,function(xl)lmer(xl ~ a * compromise * b +
+                                                     F2 + F4 + F7 + F8 +
+                                                     PreT2 + PreT3 + PreT4 + 
+                                                     PreT6 + PreT7_1 + PreT7_2 +
+                                                     PreT7_3 + PreT7_4 + PreT7_5 + 
+                                                     PreT7_6 + PreT7_7 + PreT8  +
+                                                     (1 | issue), 
+                                                   data= indepVarList))
+  depVarList <- df %>% select(matches("PT[0-9]")) %>% colnames()
+  
+  for(i in 1:length(depVarList)){
+    if(i==1){
+      m <- summary(margins(allModels[[i]], variables = "a", at = list(compromise = 0:1, b = fivenum(df$b)))) %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.56 * SE),
+               upper = AME + (1.56 * SE)) %>%
+        select(AME, upper, lower, y, compromise, b)
+    }
+    else{
+      tmp <- summary(margins(allModels[[i]], variables = "a", at = list(compromise = 0:1, b = fivenum(df$b)))) %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.56 * SE),
+               upper = AME + (1.56 * SE)) %>%
+        select(AME, upper, lower, y, compromise, b)
+      m <- m %>%
+        add_case(tmp)
+      
+    }
+  }
+  return(m)
+}
+
+df <- d %>% select(a = gender, b = PreT5, compromise, 
+                   PT1:PT4, F2, F4, F7, F8, PreT2:PreT4, 
+                   PreT6:PreT8, issue) 
+e1 <- regression_explore(df, a, b, compromise)
+
+p1e <- e1 %>%
+  mutate(y = recode(y,
+                    `PT1` = "DV: Trait Evaluation",
+                    `PT2` = "DV: Favorability",
+                    `PT3` = "DV: Representation",
+                    `PT4` = "DV: Career Prospects"),
[…]

### 2021-05-07 src/analysis/explore_wtac.R

@@ -1,0 +1,120 @@
+regression_explore <- function(df, a, b, compromise, issue){
+  
+  depVarList <- df %>% select(matches("PT[0-9]"))
+  indepVarList <- df %>% select(a, b, compromise, F2, F4, F7, F8, 
+                                PreT2:PreT7_5, PreT7_7:PreT8, issue)   
+  allModels <- apply(depVarList,2,function(xl)lmer(xl ~ a * compromise * b +
+                                                     F2 + F4 + F7 + F8 +
+                                                     PreT2 + PreT3 + PreT4 + PreT5 +
+                                                     PreT6 + PreT7_1 + PreT7_2 +
+                                                     PreT7_3 + PreT7_4 + PreT7_5 + 
+                                                     PreT7_7 + PreT8  +
+                                                     (1 | issue), 
+                                                   data= indepVarList))
+  depVarList <- df %>% select(matches("PT[0-9]")) %>% colnames()
+  
+  for(i in 1:length(depVarList)){
+    if(i==1){
+      m <- summary(margins(allModels[[i]], variables = "a", at = list(compromise = 0:1, b = fivenum(df$b)))) %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.56 * SE),
+               upper = AME + (1.56 * SE)) %>%
+        select(AME, upper, lower, y, compromise, b)
+    }
+    else{
+      tmp <- summary(margins(allModels[[i]], variables = "a", at = list(compromise = 0:1, b = fivenum(df$b)))) %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.56 * SE),
+               upper = AME + (1.56 * SE)) %>%
+        select(AME, upper, lower, y, compromise, b)
+      m <- m %>%
+        add_case(tmp)
+      
+    }
+  }
+  return(m)
+}
+
+df <- d %>% select(a = gender, b = PreT7_6, compromise, 
+                   PT1:PT4, F2, F4, F7, F8, PreT2:PreT7_5, 
+                   PreT7_7:PreT8, issue) 
+e1 <- regression_explore(df, a, b, compromise)
+
+p1e <- e1 %>%
+  mutate(y = recode(y,
+                    `PT1` = "DV: Trait Evaluation",
+                    `PT2` = "DV: Favorability",
+                    `PT3` = "DV: Representation",
+                    `PT4` = "DV: Career Prospects"),
[…]

### 2021-05-07 src/analysis/h1.R

@@ -5,11 +5,11 @@ for(i in 1:length(issues)){
     filter(issue == issues[i]) %>%
     select(-issue)
   if(i==1){
-    h1 <- regression(df, a, compromise, 1) %>%
+    h1 <- regression(df, a, compromise) %>%
     mutate(issue = issues[i])
   }  
   else{
-    tmp <- regression(df, a, compromise, 1) %>%
+    tmp <- regression(df, a, compromise) %>%
       mutate(issue = issues[i])
     h1 <- h1 %>% add_case(tmp)
   }

### 2021-05-07 src/analysis/h2.R

@@ -5,11 +5,11 @@ for(i in 1:length(issues)){
     filter(issue == issues[i]) %>%
     select(-issue)
   if(i==1){
-    h2 <- regression(df, a, compromise, 1) %>%
+    h2 <- regression(df, a, compromise) %>%
       mutate(issue = issues[i])
   }  
   else{
-    tmp <- regression(df, a, compromise, 1) %>%
+    tmp <- regression(df, a, compromise) %>%
       mutate(issue = issues[i])
     h2 <- h2 %>% add_case(tmp)
   }

### 2021-05-07 src/analysis/h3-pooled.R

@@ -1,6 +1,6 @@
 ## H3
 df <- d %>% select(a = intersection, compromise, PT1:PT4,issue, F2, F4, F7, F8, PreT2:PreT8)
-h3p <- pooled_regression(df, a, compromise, issue, 1)
+h3p <- pooled_regression(df, a, compromise, issue)
 
 p3p <- h3p %>%
   mutate(y = recode(y,

### 2021-05-07 src/analysis/h3.R

@@ -5,11 +5,11 @@ for(i in 1:length(issues)){
     filter(issue == issues[i]) %>%
     select(-issue)
   if(i==1){
-    h3 <- regression(df, a, compromise, 1) %>%
+    h3 <- regression(df, a, compromise) %>%
       mutate(issue = issues[i])
   }  
   else{
-    tmp <- regression(df, a, compromise, 1) %>%
+    tmp <- regression(df, a, compromise) %>%
       mutate(issue = issues[i])
     h3 <- h3 %>% add_case(tmp)
   }

### 2021-05-07 src/lib/functions.R

@@ -16,7 +16,7 @@ fig_cols <- yarrr::piratepal(palette = "basel",
              trans = .2)
 fig_cols <- as.character(fig_cols[1:8])
 
-regression <- function(df, a, compromise, n){
+regression <- function(df, a, compromise){
   
   depVarList <- df %>% select(matches("PT[0-9]"))
   indepVarList <- df %>% select(a, compromise, F2, F4, F7, F8, PreT2:PreT8) 
@@ -51,7 +51,7 @@ regression <- function(df, a, compromise, n){
   return(m)
 }
 
-pooled_regression <- function(df, a, compromise, issue, n){
+pooled_regression <- function(df, a, compromise, issue){
   
   depVarList <- df %>% select(matches("PT[0-9]"))
   indepVarList <- df %>% select(a, compromise, F2, F4, F7, F8, PreT2:PreT8, issue) 

### 2021-05-07 report/draft.Rmd
add exploratory results

@@
 
-```{r dv, fig.align = 'center', out.width = "90%", fig.cap = "\\label{fig:descr_dv}Descriptive Overview Dependent Variable"}
-include_graphics(here("report/figures", "Dependent Variable-1.png"))
-```
-
 **_Experimental Conditions_**
@@
 ## Pre-Registered Hypotheses
+
+**_Gender Hypothesis_**
+H1a states that women politicians are evaluated lower when striking a political compromise compared to men politicians. 
+I inspect this using four different measures of how people can judge the quality of a political representative. 
+The upper-left panel of Figure \ref{fig:results} demonstrates that people's evaluations of women politicians compared to men politicians differ between measures -- displayed on the y-axis of the figure -- and between issue areas -- displayed with different colors in the figure.
+
+- Looking at trait evaluation, only women who compromise on the issue migration are evaluated more negatively then men, yet the coefficient is not statistically significant.
+For the other three issues -- COVID, defense, and education -- the coefficients are positive, yet not statistically significant.
+- The same pattern is shown for how well people feel represented by the politician.
+Women, compared to men, are lower evaluated for the issue migration, but higher evaluated for the other three issues.
+Only the effect of education is statistically significant.
+This indicates that if female polticians compromise and vote in favor of the bill on extending extra-curricular activities at elementary schools, people feel better represented by this politician compared to if the same compromise was made by a male politician.
+- Regarding feelings of favorability towards the politician, there is no statistical significant difference between male or female politicians who strike a compromise.
+The same holds for the politicians' career prospects.
+
+H1b states that women politicians are evaluated lower when not striking a political compromise compared to men politicians. 
+The upper-center-left panel of Figure \ref{fig:results} demonstrates that almost all coefficients are positive -- i.e. going against the hypothesized directions.
+
+- When women politicians stand their grounds, they are evaluated higher on their leadership skills than their male counterparts.
+This finding holds accross issues, but is not statistically significant for the issue immigration.
+- In addition, compared to male politicians, female politicians that stand their ground make people feel better represented, except when this is about an education-related policy.
+This finding is statistically significant for the issues immigration and defense.
+- Moreover, female politicians are more favourable when standing their grounds.
+This finding is only statistically significant when women, compared to men, vote against a bill on intensifying cooperation of the army services.
+- Also, not striking a compromise is considered good for a women's career prospects, yet these findings are not statistically significant.
+
+**_Migration Hypothesis_**
+This hypothesis states that politicians with a migration background are evaluated lower when striking a political compromise compared to politicians without a migration background. 
+The upper-center-right panel of Figure \ref{fig:results} demonstrates that politicians with a migration background compared to politicians without a migration background are more positively evaluated on some measures, but more negatively evaluated on other measures.
+
+- Looking at their leadership skills (trait evaluation), we see that for the issues COVID-19, defense, and education, there is no difference between politicians with or without a migration background.
+However, for the issue of migration, we see that if politicians with a migration background compromise -- i.e.
+voting in favor of the bill proposing to put a stop to migration to Western countries -- they are considered better political leaders compared to politicians without a migration background.
+- Regarding how well people feel represented, there is no difference between politicians with and without a migration background.
+- Looking at how favorable people feel towards a politcian, we see that people feel more favorable towards politician with a migration background when they compromise on issues related to immigration and education compared to politicians without a migration background, but not for issues related to COVID-19 and defense.
+- For career perspectives, people rate the career prospects more negative when a politician with a migration background compromises on the issue migration.
+For the other issues, there is no difference between politicians with and without a migration background.
+
 \newpage 
@@
 \elandscape
+
+**_Intersection Hypothesis_** Hypothesis 3a states that women politician with a migration background are evaluated lower when striking a political compromise compared to men politicians without a migration background.
+This hypothesis is tested in the lower-left panel of Figure \ref{fig:results} for the separate issues, and in the lower-center-right panel of Figure \ref{fig:results} pooling the issues.
+
+- Trait: no differences for COVID-19 and immigration, insignificant positive effects for defense and education, pooling significant positive effect
+- Representation: Positive and signicant for education, nothing for the other issues, pooling significant positive effect
+- Favorability:  Positive and signicant for education, nothing for the other issues, pooling significant positive effect
+- Career prospects: negative and significant for immigration, nothing for the other issues or in the pooled analysis.
+
+Hypothesis 3b states that women politician with a migration background are evaluated lower when not striking a political compromise compared to men politicians without a migration background.
+This hypothesis is tested in the lower-center-left panel of Figure \ref{fig:results} for the separate issues, and in the lower-right panel of Figure \ref{fig:results} pooling the issues.
+
+- Trait: positive and significant for COVID-19, nothing for the other issues or in the pooled analysis.
+- Representation: no differences
+- Favorability: positive and significant for COVID-19, nothing for the other issues or in the pooled analysis.
+- Career prospects:negative and significant for defense,  nothing for the other issues or in the pooled analysis.
+
+Paragraph on what it means for theory, and justification for explorations (below).
 

### 2021-05-11 report/draft.Rmd
add interpretations

@@
   kable_styling(latex_options = c("striped", "hold_position"),
-                full_width = F, fixed_thead = T, position = "center")
+                full_width = F, fixed_thead = T, position = "center")  %>%
+   column_spec(1, width = "5.5cm") %>%
+   column_spec(2, width = "2cm") %>%
+   column_spec(3, width = "1.5cm") %>%
+   column_spec(4, width = "2cm") %>%
+   column_spec(5, width = "2cm")
 rm(descr, means)  
@@
 ## Exploration
+To explore hetereogeneous effects, I conduct pooled analyses.
 
 **_Ideology_**
+
+- H1a: People with left-wing ideological position (i.e.
+`value rile-self $<5$`) have higher evaluations for female politicians who compromise compared to male politicians who compromise.
+Compared to male politicians, they find women politicians who compromise more favorable, feel better represented and evaluate their leadershipskills higher (yet very small effect).
+For people with a right-wing ideological position (i.e.
+`value rile-self $>5$`), there is no statistical significant difference between female and male politicians who compromise.
+- H1b: The opposite holds for people with a right-wing ideological position when evaluating women who do not compromise, compared to male politicians: women who stick to their guns are considered more favorable and better leaders than men who stick to their guns.
+For people with a left-wing ideological position, there is no statistical significant difference between female and male politicians who do not compromise.
+- H2: Left-wing more favorable to people politicians with a migration background who compromise than towards politicians without a migration backgroound -- no effect for other three measures.
+For people with a right-wing ideological position, there is no statistical significant difference between politicians with and without a migration background who compromise.
+Looking at NOT compromising, we see remarkable differences between people with a left-wing and right-wing ideology.
+When politicians with a migration background not compromise, they're considered more favorable to left-wingers, but less favorable to right-wingers.
+Also, not compromising makes them have better leaders according to the left, and worse leaders according to the right.
+- H3a: Women with a migration background (compared to women without, and compared to men with and without) who compromise are considered more favorable, better representatives, and to have better career prospects by the left.
+No statistical difference for the right.
+- H3b: No statistical difference for the left of the right
+
+CHECK for DISCUSSION: left-wing over all more agreeable?
+```{r "ideology-agree",echo=FALSE}
+d %>% 
+   select(PreT6, PreT7_2, PreT7_6, PreT7_7) %>%
+   mutate(`Ideological Position` = if_else(PreT6>5, 
+                                           "Right-Wing", 
+                                           "Left-Wing")) %>%
+   group_by(`Ideological Position`) %>%
+   summarise(c1 = cor(PreT6,PreT7_2),
+             c2 = cor(PreT6,PreT7_6),
+             c3 = cor(PreT6,PreT7_7)) %>% 
+   pivot_longer(cols = c1:c3,
+                names_to = "Correlation with",
+                values_to = "Pearson's R") %>%
+   mutate(`Correlation with` = recode(`Correlation with`,
+                                      `c1` = "Against their better judgment, politicians promise more than they can deliver.",
+                                      `c2` = "What in politics is called `making compromises' is actually just betraying your principles.",
+                                      `c3` = "A strong head of government is good for the Netherlands, even if he stretches the rules a bit to get things done.")) %>%
+   kbl(booktabs =T, caption = "\\label{tab:cor_agree}Correlation ideology and agreebleness",
+    digits = 2) %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+   column_spec(1, width = "3cm") %>%
+   column_spec(2, width = "10cm") %>%
+   column_spec(3, width = "3cm")
+```
+
 \newpage 
 \blandscape 
-```{r results-ideology, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-ideology}Results: Interaction with Ideology"}
+```{r results-ideology, out.width = "100%", fig.align = 'center', fig.cap = "\\label{fig:results-ideology}Results: Interaction with Ideology"}
 include_graphics(here("report/figures", "explore-ideology-1.png"))
@@
 **_Willingness to Accept Compromises_**
+
+- H1a: people with low scores on WTAC, i.e.
+those who consider political compromise betraying your principles (`scores of 1-3` (inversly coded)), are more likely to consider female politicians who compromise favorable (compared to male politicians who compromise).
+Both people with high and low scores on WTAC consider female politcians who compromise to be better representatives than male politicians who compromise.
+People willing to accept compromise consider the career prosects of women who compromise more positive compared to male politicians who compromise.
+- H1b: People who are against political compromise rate female politicians who stick to their guns higher in terms of favorability than male politicians who do so.
+Both people with high and low scores on WTAC consider female politcians who compromise to be better representatives than male politicians who compromise.
+People willing to accept compromise consider the career prosects of women who compromise more positive compared to male politicians who compromise, also they consider female politicians who do not compromise less favorable, but better leaders.
+- H2: People who are against political compromise rate the career prospects of politicians with a migration background who compromise way more negative compared to politicians without a migration background, they are also slightly more negative about the represenation oof politicians with a migration background compared to those without that background.
+When you are willing to accept political compromises, you are more positive about politicians with a migration background in terms of career prospects, favorability, representatiion and leadership traits.
+When politicians with a migration background stick to their guns, both people who are and are not willing to accept compromise evaluate them lower compared to politicians without a migration bachground.
+Moreover, people against political compromises also find politicians with a migration background who stick to their guns less favorable than politicians without a migration background.
+- H3a: Female politicians with a migration background are considered more favorable by people who are willing to accept political compromises.
+- H3b: Female politicians with a migration background are considered more favorable by people who are not willing to accept political compromises, and less favorable by those who are willing to acceptt compromise.
+Also, people against political compromisee evaluate the prospects of female politicians with a migration backgound lower than the prospects of the other groups.
+
+CHECK: do people who are willing to accept compromise have higher trust in poltics?
+
+```{r "wtac-trust", echo=FALSE}
+d %>% 
+   select(PreT7_6, PreT7_1, PreT7_3, PreT7_4, PreT7_5) %>%
+   mutate(`Attitude towards Compromise` = if_else(PreT7_6>3, "Positive", 
+                         "Negative")) %>%
+   group_by(`Attitude towards Compromise`) %>%
+   summarise(c1 = cor(PreT7_6,PreT7_1),
+             c2 = cor(PreT7_6,PreT7_3),
+             c3 = cor(PreT7_6,PreT7_4),
+             c4 = cor(PreT7_6,PreT7_5)) %>% 
+   pivot_longer(cols = c1:c4,
+                names_to = "Correlation with",
+                values_to = "Pearson's R") %>%
+   mutate(`Correlation with` = recode(`Correlation with`,
+                                      `c1` = "The political parties are only interested in my vote and not in my opinion.",
+                                      `c2` = "Most politicians are skilled people who know what they are doing.",
+                                      `c3` = "Politicians are able to solve the most important problems.",
+                                      `c4` = "I feel well represented by Dutch politicians.")) %>%
+   kbl(booktabs =T, caption = "\\label{tab:cor_trust}Correlation WtAC and Other measures of Pol. Eff",
+    digits = 2) %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+   column_spec(1, width = "3cm") %>%
+   column_spec(2, width = "10cm") %>%
+   column_spec(3, width = "3cm")
+```
+
 \newpage 
 \blandscape 
-```{r results-wtac, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-wtac}Results: Interaction with Willingness to Accept Compromise"}
+```{r results-wtac, out.width = "100%", fig.align = 'center', fig.cap = "\\label{fig:results-wtac}Results: Interaction with Willingness to Accept Compromise"}
 include_graphics(here("report/figures", "explore-wtac-1.png"))
@@
 **_Attitude towards Women in Politics_**
+
+- H1a: Whether or not you're positive towards women in politics, female politicians who compromise are considered more favorable than male politicians -- the same holds for women who do not compromise.
+For those negative towards women in politics, they evaluate women politicians who compromise as having better career perspectives, being better representatives, yet having lower leadership skills.
+For those positive about women in politics, female politicians who compromise are seen as worse representatives than males who compromise.
+The opposte holds for leadership skills.
+- H1b: For those negative towards women in politics, they evaluate women politicians who do not compromise as having better career perspectives, yet being worse representatives.
+There is no difference in their leadership skills (effect of 0).
+For those positive about women in politics, female politicians who do not compromise are seen as better representatives than males who do not compromise.
+The same holds for leadership skills.
+- H3a: People who have a negative attitude towards women in politics evaluate female polticians with a migration background lower.
+They rate their career perspectives  and leadershipskills more negative.
+People with positive attitudes towards women in politics rate female politicians with a migration background who compromise -- relative to other groups -- higher in terms of career prospects, favorability and leadership skills.
+- H3b: When female politicians with a migration background do not compromise, they are lower evaluated on their career prospects, but are considered to be better representatives by those with a positive attitude towards women in politics.
+When female politicians with a migration background do not comprimse, their career perspectives are evaluated lower, but they are considered better representatives by people with positive attitudes towards women in politics.
+
 \newpage 
 \blandscape 
-```{r results-women-politics, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-women-politics}Results: Interaction with Attitudes towards Women in Politics"}
+```{r results-women-politics, out.width = "100%", fig.align = 'center', fig.cap = "\\label{fig:results-women-politics}Results: Interaction with Attitudes towards Women in Politics"}
 include_graphics(here("report/figures", "explore-women-politics-1.png"))
@@
 **_Position on Political Issues_**
+
+- H1a:
+   - COVID-19: When opposing COVID-19 policies, people rare female politicians who compromise as more favorable than male politicans who compromise.
+People who are infacor of the COVID-19 policies do not evaluate male and female politicians who compromise differently
+   - Defense: No difference between positive or negative towards defense, people always rate compromising female politicians as more favorable.
+When you are negative towards defense policies: find women who compromise better representatives, when positive about defense policies, you evaluate their career prosects more positive.
+   - Education: When negative position on education, you rate compromising female politicians higher than compromising male politicians in terms of favorability, as representatives, and in terms of their leadership skills.
+   - Immigratin: When estimaing low percentagees of immigration in the Netherlands, you're more positive towards compromising female politicians in terms of career prospects, favorability and representation.
+
+- H1b: 
+   - COVID-19: People who are negative towards COVID-19 policies find female politicians who stick to their guns better representatives and evaluate their leadership skills hiigher compared to male politicians who compromise.
+People who are positive towards COVID-19 politicies find female politicians who stick to their guns more likeable.
+   - Defense: People who are negative towards defense policies find female politicians who stick to their guns more favorable, and think they have better career prospects.
+People who are positive towards defense politicies find female politicians who stick to their guns better representatives.
+   - Education: Position on education has no effect for favorability and leadershipskills.
+For both hold that women sticking to their guns are higher evaluated than male politicians doing the same.
+If you're negative towards education, you rate the career prospects of women sticking to their guns higher, and when you're positive towards education, you find women sticking to their guns better representatives.
+   - Immigration: Positive on immigration coincides with
+
+- H2: 
+   - COVID-19:
+   - Defense:
+   - Education:
+   - Immigration:
+
+- H3a: 
+   - COVID-19:
+   - Defense:
+   - Education:
+   - Immigration:
+
+- H3b: 
+   - COVID-19:
+   - Defense:
+   - Education:
+   - Immigration:
+
 \newpage 
 \blandscape 
-```{r results-covid, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-covid}Results: Interaction with Position on COVID-19"}
+```{r results-covid, out.width = "100%", fig.align = 'center', fig.cap = "\\label{fig:results-covid}Results: Interaction with Position on COVID-19"}
 include_graphics(here("report/figures", "explore-covid-1.png"))
@@
 \blandscape 
-```{r results-defense, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-defense}Results: Interaction with Position on Defense"}
+```{r results-defense, out.width = "100%", fig.align = 'center', fig.cap = "\\label{fig:results-defense}Results: Interaction with Position on Defense"}
 include_graphics(here("report/figures", "explore-defense-1.png"))
@@
 \blandscape 
-```{r results-education, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-education}Results: Interaction with Position on Education"}
+```{r results-education, out.width = "100%", fig.align = 'center', fig.cap = "\\label{fig:results-education}Results: Interaction with Position on Education"}
 include_graphics(here("report/figures", "explore-education-1.png"))
@@
 \blandscape 
-```{r results-immigration, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-immigration}Results: Interaction with Position on Immigration"}
+```{r results-immigration, out.width = "100%", fig.align = 'center', fig.cap = "\\label{fig:results-immigration}Results: Interaction with Position on Immigration"}
 include_graphics(here("report/figures", "explore-immigration-1.png"))

### 2021-05-11 report/draft.Rmd
add description analysis

@@
 If you're negative towards education, you rate the career prospects of women sticking to their guns higher, and when you're positive towards education, you find women sticking to their guns better representatives.
-   - Immigration: Positive on immigration coincides with
+   - Immigration: Positive on immigration find compromising female politicians more favorable.
 
 - H2: 
-   - COVID-19:
-   - Defense:
-   - Education:
-   - Immigration:
+   - COVID-19: No differences between people pro- or con COVID-19 policies for the evaluation of compromising politicians with or without migratiton background.
+When politicians with a migration background do not compromise, however, people pro-COVID foresee a more negative career for them.
+   - Defense: Con-defense position rate compromising politicians with a migration background negatively regarding their career prospects -- they also do that when not compromising (same holds for pro-defense), yet positively in terms of favorability.
+Pro-defense, no differences are found in their evaluations.
+When politicians with a migration-background stick to their guns, people con-defense find them more favorable and peoeple pro-defense the opposite.
+   - Education: When politicians with a migration background compromise, they are seen as having worse career prospects, less favorable, being worse representatives, and have worse leadershipskills by people con-education.
+No differences for people pro-education.
+When sticking to their guns, they politicians are seen as less favorable by con-education, and worse career prospects by people pro-education.
+   - Immigration: Once you think that the population of people with an immigrant background in the Netherlands is bigger than 25%, you're more negative about the career prospects, the favorability and the leadership skills of a compromising politician with a migration background (compared to politicians without a migration background).
+Yet, when you're positive on migration, you're more likey to rate a compromising politician with a migration background as more favorable and better representative.
+When politicians with a migration background do not comrpomise, people who think that the population of people with an immigrant background in the Netherlands is smaller than 25% are more negative about their career prospects -- similar to people that are negative about immigration.
+Moreover, when people negative on immigration, they find them less favorable.
 
 - H3a: 
-   - COVID-19:
-   - Defense:
-   - Education:
-   - Immigration:
+   - COVID-19: No differences
+   - Defense: When female politicians with a migration background compromise, they're seen as better representatives by people con-defense
+   - Education: No differences
+   - Immigration: Once you think that the population of people with an immigrant background in the Netherlands is bigger than 25%, you're more negative about the career prospects, the favorability, representativeness, and the leadership skills of a compromising female politician with a migration background (compared to politicians without a migration background), yet when you think the population of people with an immigrant background in the Netherlands is smaller than 25%, you find compromising female politicians more favorable and better representatives.
+Moreover, having a positive attitude on migration leads to evaluating female politicians with a migration background who compromise higher in terms of career prospects, favorability and representativeness.
 
 - H3b: 
-   - COVID-19:
-   - Defense:
-   - Education:
-   - Immigration:
+   - COVID-19: No differences
+   - Defense: When female politicians with a migration background stick to their guns, they're seen as more favorable by people con-defense.
+   - Education: When female politicians with a migration background stick to their guns, they're evaluated to have better career-prospects by people con-education.
+   - Immigration: No differences
 

### 2021-05-11 src/analysis/data-for-analyses.R

@@ -6,7 +6,8 @@ d <- d %>%
          PreT5 = round((PreT5_1 + PreT5_2 + PreT5_3 + PreT5_4)/4,0),
          PreT7_2 = 6 - PreT7_2,
          PreT7_6 = 6 - PreT7_6,
-         PreT7_7 = 6 - PreT7_7) %>%
+         PreT7_7 = 6 - PreT7_7,
+         PreT2 = 10 - PreT2) %>%
   pivot_longer(cols = c(`name_D`, `name_I`, `name_E`, `name_C`),
                values_to = "name",
                names_to = "issue") %>%

### 2021-05-27 src/data-processing/tidy_data.R
change mistake in coding compromise in treatment

@@ -14,11 +14,118 @@ pret <- read_sav(here("data/raw-private/experiment.sav")) %>%
                         `12` = 2, `11` = 1))) %>%
   drop_na()
 
-tr <- read_sav(here("data/raw-private/experiment.sav")) %>%
+tmp <- read_sav(here("data/raw-private/experiment.sav")) %>%
   remove_all_labels() %>%
   filter(Consent == 1, Attention2_3 ==1, Attention2_5==1) %>%
-  select(matches("name_[A-Z]"), compromis, id = ResponseId) %>%
-  drop_na(name_I, name_E)
+  select(matches("FL_"),id = ResponseId)
+
+tr1 <- read_sav(here("data/raw-private/experiment.sav")) %>%
+  remove_all_labels() %>%
+  filter(Consent == 1, Attention2_3 == 1, Attention2_5 == 1) %>%
+  select(matches("FL_"),id = ResponseId) %>%
+  mutate(FL_32_DO_FL_104 = recode(FL_32_DO_FL_104, `1` = "Rachid Amezian", .default = "NO"),
+         FL_32_DO_FL_106 = recode(FL_32_DO_FL_106, `1` = "Rachid Amezian", .default = "NO"),
+         FL_32_DO_FL_108 = recode(FL_32_DO_FL_108, `1` = "Karel van der Kleijn", .default = "NO"),
+         FL_32_DO_FL_110 = recode(FL_32_DO_FL_110, `1` = "Karel van der Kleijn", .default = "NO"),
+         FL_32_DO_FL_112 = recode(FL_32_DO_FL_112, `1` = "Rachida Amezian", .default = "NO"),
+         FL_32_DO_FL_114 = recode(FL_32_DO_FL_114, `1` = "Rachida Amezian", .default = "NO"),
+         FL_32_DO_FL_116 = recode(FL_32_DO_FL_116, `1` = "Karin van der Kleijn", .default = "NO"),
+         FL_32_DO_FL_118 = recode(FL_32_DO_FL_118, `1` = "Karin van der Kleijn", .default = "NO"),
+         FL_78_DO_FL_123 = recode(FL_78_DO_FL_123, `1` = "Rachid Amezian", .default = "NO"),
+         FL_78_DO_FL_125 = recode(FL_78_DO_FL_125, `1` = "Rachid Amezian", .default = "NO"),
[…]

### 2021-05-27 report/figures/table_descriptives.tex
add labels to graphs of h's
add description analysis
rerun analyses

@@
   <tr>
-   <th style="text-align:left;"> name </th>
+   <th style="text-align:left;"> Variables </th>
    <th style="text-align:right;"> Mean Value </th>
@@
    <td style="text-align:left;"> Age </td>
-   <td style="text-align:right;"> 33.80 </td>
-   <td style="text-align:right;"> 16.34 </td>
+   <td style="text-align:right;"> 33.64 </td>
+   <td style="text-align:right;"> 16.37 </td>
    <td style="text-align:right;"> 0 </td>
@@
    <td style="text-align:left;"> Region </td>
-   <td style="text-align:right;"> 2.92 </td>
+   <td style="text-align:right;"> 2.93 </td>
    <td style="text-align:right;"> 1.39 </td>
@@
    <td style="text-align:left;"> Urbanness </td>
-   <td style="text-align:right;"> 2.27 </td>
+   <td style="text-align:right;"> 2.28 </td>
    <td style="text-align:right;"> 1.45 </td>
@@
    <td style="text-align:right;"> 1.30 </td>
-   <td style="text-align:right;"> 0.90 </td>
+   <td style="text-align:right;"> 0.89 </td>
    <td style="text-align:right;"> 1 </td>
@@
    <td style="text-align:left;"> Employment </td>
-   <td style="text-align:right;"> 3.35 </td>
-   <td style="text-align:right;"> 2.62 </td>
+   <td style="text-align:right;"> 3.36 </td>
+   <td style="text-align:right;"> 2.67 </td>
    <td style="text-align:right;"> 1 </td>
@@
    <td style="text-align:left;"> Income </td>
-   <td style="text-align:right;"> 9.76 </td>
-   <td style="text-align:right;"> 2.68 </td>
+   <td style="text-align:right;"> 9.75 </td>
+   <td style="text-align:right;"> 2.74 </td>
    <td style="text-align:right;"> 1 </td>
@@
    <td style="text-align:left;"> Education </td>
-   <td style="text-align:right;"> 1.28 </td>
-   <td style="text-align:right;"> 0.54 </td>
+   <td style="text-align:right;"> 1.27 </td>
+   <td style="text-align:right;"> 0.53 </td>
    <td style="text-align:right;"> 1 </td>
@@
    <td style="text-align:left;"> Immigration (%) </td>
-   <td style="text-align:right;"> 22.82 </td>
-   <td style="text-align:right;"> 12.82 </td>
+   <td style="text-align:right;"> 22.76 </td>
+   <td style="text-align:right;"> 12.78 </td>
    <td style="text-align:right;"> 1 </td>
@@
    <td style="text-align:left;"> Position: Immigration </td>
-   <td style="text-align:right;"> 5.91 </td>
-   <td style="text-align:right;"> 2.03 </td>
+   <td style="text-align:right;"> 5.88 </td>
+   <td style="text-align:right;"> 2.04 </td>
    <td style="text-align:right;"> 0 </td>
@@
    <td style="text-align:right;"> 3.12 </td>
-   <td style="text-align:right;"> 0.83 </td>
+   <td style="text-align:right;"> 0.82 </td>
    <td style="text-align:right;"> 0 </td>
@@
    <td style="text-align:left;"> Ideology </td>
-   <td style="text-align:right;"> 4.48 </td>
+   <td style="text-align:right;"> 4.46 </td>
    <td style="text-align:right;"> 2.20 </td>
@@
    <td style="text-align:left;"> Political Efficacy (1) </td>
-   <td style="text-align:right;"> 3.13 </td>
+   <td style="text-align:right;"> 3.12 </td>
    <td style="text-align:right;"> 1.03 </td>
@@
    <td style="text-align:left;"> Political Efficacy (2) </td>
-   <td style="text-align:right;"> 2.06 </td>
+   <td style="text-align:right;"> 3.94 </td>
    <td style="text-align:right;"> 0.85 </td>
@@
    <td style="text-align:left;"> Political Efficacy (3) </td>
-   <td style="text-align:right;"> 3.15 </td>
+   <td style="text-align:right;"> 3.16 </td>
    <td style="text-align:right;"> 0.95 </td>
@@
    <td style="text-align:left;"> Political Efficacy (4) </td>
-   <td style="text-align:right;"> 2.86 </td>
+   <td style="text-align:right;"> 2.87 </td>
    <td style="text-align:right;"> 0.97 </td>
@@
    <td style="text-align:left;"> Political Efficacy (6) </td>
-   <td style="text-align:right;"> 3.60 </td>
-   <td style="text-align:right;"> 1.05 </td>
+   <td style="text-align:right;"> 2.39 </td>
+   <td style="text-align:right;"> 1.04 </td>
    <td style="text-align:right;"> 1 </td>
@@
    <td style="text-align:left;"> Political Efficacy (7) </td>
-   <td style="text-align:right;"> 3.26 </td>
+   <td style="text-align:right;"> 2.74 </td>
    <td style="text-align:right;"> 1.19 </td>
@@
    <td style="text-align:left;"> Position: COVID-19 </td>
-   <td style="text-align:right;"> 2.88 </td>
+   <td style="text-align:right;"> 2.86 </td>
    <td style="text-align:right;"> 1.18 </td>
@@
    <td style="text-align:left;"> DV: Representation </td>
-   <td style="text-align:right;"> 5.85 </td>
-   <td style="text-align:right;"> 1.78 </td>
+   <td style="text-align:right;"> 5.86 </td>
+   <td style="text-align:right;"> 1.77 </td>
    <td style="text-align:right;"> 0 </td>

### 2021-05-27 src/analysis/Analysis.Rmd
rerun analyses

@@
 descr <- d %>%
-  summarise(`DV: Trait Evaluation` = round(sum(is.na(PT1))/n(),2),
-            `DV: Favorability` = round(sum(is.na(PT2))/n(),2),
-            `DV: Representation` = round(sum(is.na(PT3))/n(),2),
-            `DV: Career Prospects` = round(sum(is.na(PT4))/n(),2),
-            `Immigration (%)` = round(sum(is.na(PreT1))/n(),2),
-            `Position: Immigration` = round(sum(is.na(PreT2))/n(),2),
-            `Position: Defense` = round(sum(is.na(PreT3))/n(),2),
-            `Position: Education` = round(sum(is.na(PreT4))/n(),2),
-            `Attitude: Women in Politics` = round(sum(is.na(PreT5))/n(),2),
-            `Ideology` = round(sum(is.na(PreT6))/n(),2),
-            `Political Efficacy (1)` = round(sum(is.na(PreT7_1))/n(),2),
-            `Political Efficacy (2)` = round(sum(is.na(PreT7_2))/n(),2),
-            `Political Efficacy (3)` = round(sum(is.na(PreT7_3))/n(),2),
-            `Political Efficacy (4)` = round(sum(is.na(PreT7_4))/n(),2),
-            `Political Efficacy (5)` = round(sum(is.na(PreT7_5))/n(),2),
-            `Political Efficacy (6)` = round(sum(is.na(PreT7_6))/n(),2),
-            `Political Efficacy (7)` = round(sum(is.na(PreT7_7))/n(),2),
-            `Position: COVID-19` = round(sum(is.na(PreT8))/n(),2),
-            `Gender` = round(sum(is.na(F1))/n(),2),
-            `Age` = round(sum(is.na(F2))/n(),2),
-            `Region` = round(sum(is.na(F3))/n(),2),
-            `Urbaness` = round(sum(is.na(F4))/n(),2),
-            `Migration Background` = round(sum(is.na(F5))/n(),2),
-            `Party Preference` = round(sum(is.na(F6))/n(),2),
-            `Employment` = round(sum(is.na(F7))/n(),2),
-            `Income` = round(sum(is.na(F8))/n(),2),
-            `Education` = round(sum(is.na(F9))/n(),2)) %>%
+  summarise(`DV: Trait Evaluation` = round(sum(is.na(PT1))/n(),4),
+            `DV: Favorability` = round(sum(is.na(PT2))/n(),4),
+            `DV: Representation` = round(sum(is.na(PT3))/n(),4),
+            `DV: Career Prospects` = round(sum(is.na(PT4))/n(),4),
+            `Immigration (%)` = round(sum(is.na(PreT1))/n(),4),
+            `Position: Immigration` = round(sum(is.na(PreT2))/n(),4),
+            `Position: Defense` = round(sum(is.na(PreT3))/n(),4),
+            `Position: Education` = round(sum(is.na(PreT4))/n(),4),
+            `Attitude: Women in Politics` = round(sum(is.na(PreT5))/n(),4),
+            `Ideology` = round(sum(is.na(PreT6))/n(),4),
+            `Political Efficacy (1)` = round(sum(is.na(PreT7_1))/n(),4),
+            `Political Efficacy (2)` = round(sum(is.na(PreT7_2))/n(),4),
+            `Political Efficacy (3)` = round(sum(is.na(PreT7_3))/n(),4),
+            `Political Efficacy (4)` = round(sum(is.na(PreT7_4))/n(),4),
+            `Political Efficacy (5)` = round(sum(is.na(PreT7_5))/n(),4),
+            `Political Efficacy (6)` = round(sum(is.na(PreT7_6))/n(),4),
+            `Political Efficacy (7)` = round(sum(is.na(PreT7_7))/n(),4),
+            `Position: COVID-19` = round(sum(is.na(PreT8))/n(),4),
+            `Gender` = round(sum(is.na(F1))/n(),4),
+            `Age` = round(sum(is.na(F2))/n(),4),
+            `Region` = round(sum(is.na(F3))/n(),4),
+            `Urbaness` = round(sum(is.na(F4))/n(),4),
+            `Migration Background` = round(sum(is.na(F5))/n(),4),
+            `Party Preference` = round(sum(is.na(F6))/n(),4),
+            `Employment` = round(sum(is.na(F7))/n(),4),
+            `Income` = round(sum(is.na(F8))/n(),4),
+            `Education` = round(sum(is.na(F9))/n(),4)) %>%
   pivot_longer(cols = `DV: Trait Evaluation`:`Education`,
@@
 
-I recode the missing values of the variables `Urbaness`, `Party Preference`, `Employment`, and `Income` to the mean value of the respective variables -- median for `Party Precerence`.
-For Income, I also include a dummy indicating whether the missing value was imputed.
+I recode the missing values of the variables `Urbaness`, `Migration Background`, `Income`, and `Education` to the mean value of the respective variables.
 
 ```{r "add missings"}
-means <- d %>%
-  summarise(F4 = round(mean(F4, na.rm = T),0),
-            F5 = round(mean(F5, na.rm = T), 0),
-            F6 = max(names(table(F6))),
-            F7 = round(mean(F7, na.rm = T),0),
-            F8 = round(mean(F8, na.rm = T),0),
-            F9 = round(mean(F9, na.rm = T),0))
-
 d <- d %>%
-  mutate(F4 = replace_na(F4, means$F4),
-         F5 = replace_na(F5, means$F5),
-         F6 = replace_na(F6, means$F6),
-         F7 = replace_na(F7, means$F7),
-         missing_F8 = if_else(is.na(F8), 1, 0),
-         F8 = replace_na(F8, means$F8),
-         F9 = replace_na(F9, means$F9))
-rm(means, descr, scales)
+  mutate(F4 = replace_na(F4, round(mean(F4, na.rm = T),0)),
+         F5 = replace_na(F5, round(mean(F5, na.rm = T),0)),
+         F8 = replace_na(F8,round(mean(F8, na.rm = T),0)),
+         F9 = replace_na(F9,round(mean(F9, na.rm = T),0)))
+rm(descr, scales)
 ```
@@
 
-The figure below shows that the data is unbalanced for the variables: `Income`, `Employment`, `Urbaness`, `Age`, `Position: COVID`, `Political Efficacy`, `Ideology`,
-`Attitudes: Women in Politics`, `Position: Education`, `Position: Defense`, `Position: Immigration`.
+The figure below shows that the data is unbalanced for the variables: `Education`,`Income`, `Employment`, `Urbaness`, `Age`, `Position: COVID`, `Political Efficacy`, `Ideology`,
+`Attitudes: Women in Politics`, `Position: Education`, `Position: Defense`, `Position: Immigration`, and `Immigration (%)`.
 As described in the Pre-Analysis Plan (p.10), I will add these covariates to the analyses as controls.

### 2021-05-27 src/analysis/balance-test.R

@@ -81,7 +81,7 @@ df <- df %>%
                                       "50+", "Bij1", "BBB", "Blanco", "CDA",
                                       "ChristenUnie", "D66", "Didn't vote", "Don't know",
                                       "Denk", "Forum for Democracy","GroenLinks", "JA21", 
-                                      "Not eligible", "PvdA", "Animal Rights Party", "PVV", 
+                                      "Not eligible", "Other Party ","PvdA", "Animal Rights Party", "PVV", 
                                       "SGP", "SP", "VOLT","VVD","Employment",
                                       "Income",  "Education: High", "Education: Middle", "Education: Low")),
          difference = Diff.Un,2) %>%

### 2021-05-27 src/analysis/data-for-analyses.R

@@ -4,53 +4,58 @@ d <- d %>%
          PT_C1 = round((PT_C1_1 + PT_C1_2 + PT_C1_3 + PT_C1_4 + PT_C1_5 + PT_C1_6)/6, 0),
          PT_I1 = round((PT_I1_1 + PT_I1_2 + PT_I1_3 + PT_I1_4 + PT_I1_5 + PT_I1_6)/6, 0),
          PreT5 = round((PreT5_1 + PreT5_2 + PreT5_3 + PreT5_4)/4,0),
-         PreT7_2 = 6 - PreT7_2,
-         PreT7_6 = 6 - PreT7_6,
-         PreT7_7 = 6 - PreT7_7,
-         PreT2 = 10 - PreT2) %>%
-  pivot_longer(cols = c(`name_D`, `name_I`, `name_E`, `name_C`),
+         PreT7 = round((PreT7_1 + PreT7_2 + PreT7_3 + PreT7_4 + PreT7_5 + PreT7_6 + PreT7_7)/7,0)) %>%
+  pivot_longer(cols = c(name_D, name_I, name_E, name_C),
                values_to = "name",
                names_to = "issue") %>%
   drop_na(name) %>%
   mutate(issue = recode(issue, 
-                        `name_C` = "COVID",
-                        `name_D` = "Defense",
-                        `name_E` = "Education",
-                        `name_I` = "Immigration")) %>%
-  pivot_longer(cols = c(`PT_D1`, `PT_E1`, `PT_C1`, `PT_I1`),
+                        name_C = "COVID",
+                        name_D = "Defense",
+                        name_E = "Education",
+                        name_I = "Immigration")) %>%
+  pivot_longer(cols = c(compromise_D, compromise_I, compromise_E, compromise_C),
+               values_to = "compromise",
+               names_to = "issue_c") %>%
+  mutate(issue_c = recode(issue_c, 
+                          compromise_C = "COVID",
+                          compromise_D = "Defense",
+                          compromise_E = "Education",
+                          compromise_I = "Immigration")) %>%
+  pivot_longer(cols = c(PT_D1, PT_E1, PT_C1, PT_I1),
                values_to = "PT1",
                names_to = "issue1") %>%
-  drop_na(PT1) %>%
   mutate(issue1 = recode(issue1, 
-                        `PT_C1` = "COVID",
-                        `PT_D1` = "Defense",
-                        `PT_E1` = "Education",
[…]

### 2021-05-27 src/analysis/descriptive-information-overview.R

@@ -1,5 +1,5 @@
 descr <- d %>%
-  select(-id, -issue, -name, -F6, -missing_F8) %>%
+  select(-id, -issue, -name, -F6) %>%
   mutate(F1 = recode(F1, `999` = 0, `2` = 0),
          F5 = as.numeric(F5)) %>%
   pivot_longer(cols = everything(),

### 2021-05-27 src/analysis/distribution_unbalanced_vars.R

@@ -1,5 +1,5 @@
 df <- d %>%
-  select(name, compromise, F2, F4, F7, F8, PreT2:PreT8,issue)  %>%
+  select(name, compromise, F2, F4, F7, F8, F9, PreT2:PreT8,issue)  %>%
   mutate(compromise = if_else(compromise==1, "Compromise", "No Compromise")) %>%
   mutate_at(c("F2", "F4", "F7", "F8", "PreT2", "PreT3", "PreT4", "PreT5", "PreT6",
               "PreT7_1", "PreT7_2", "PreT7_3", "PreT7_4", "PreT7_5", "PreT7_6",
@@ -11,6 +11,7 @@ df <- d %>%
                        `F4` = "Urbaness",
                        `F7` = "Employment",
                        `F8` = "Income",
+                       `F9` = "Education",
                        `PreT2`  = "Position: Immigration",
                        `PreT3`  = "Position: Defense",
                        `PreT4`  = "Position: Education",

### 2021-05-27 src/analysis/explore_ideology.R

@@ -1,10 +1,10 @@
 regression_explore <- function(df, a, b, compromise, issue){
   
   depVarList <- df %>% select(matches("PT[0-9]"))
-  indepVarList <- df %>% select(a, b, compromise, F2, F4, F7, F8, 
-                                PreT2:PreT5, PreT7_1:PreT8, issue)   
+  indepVarList <- df %>% select(a, b, compromise, F2, F4, F7, F8, F9, 
+                                PreT1:PreT5, PreT7_1:PreT8, issue)   
   allModels <- apply(depVarList,2,function(xl)lmer(xl ~ a * compromise * b +
-                                                     F2 + F4 + F7 + F8 +
+                                                     F2 + F4 + F7 + F8 + F9 + PreT1 +
                                                      PreT2 + PreT3 + PreT4 + PreT5 +
                                                      PreT7_1 + PreT7_2 +
                                                      PreT7_3 + PreT7_4 + PreT7_5 + 
@@ -36,7 +36,7 @@ regression_explore <- function(df, a, b, compromise, issue){
 }
 
 df <- d %>% select(a = gender, b = PreT6, compromise, 
-                   PT1:PT4, F2, F4, F7, F8, PreT2:PreT5, 
+                   PT1:PT4, F2, F4, F7, F8, F9, PreT1:PreT5, 
                    PreT7_1:PreT8, issue) 
 e1 <- regression_explore(df, a, b, compromise)
 
@@ -63,7 +63,7 @@ p1e <- e1 %>%
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") 
 
 df <- d %>% select(a = immigration, b = PreT6, compromise, 
-                   PT1:PT4, F2, F4, F7, F8, PreT2:PreT5, 
+                   PT1:PT4, F2, F4, F7, F8, F9, PreT1:PreT5, 
                    PreT7_1:PreT8, issue) 
 e2 <- regression_explore(df, a, b, compromise)
 
@@ -90,7 +90,7 @@ p2e <- e2 %>%
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") 
 
 df <- d %>% select(a = intersection, b = PreT6, compromise, 
-                   PT1:PT4, F2, F4, F7, F8, PreT2:PreT5, 
+                   PT1:PT4, F2, F4, F7, F8, F9, PreT1:PreT5, 
                    PreT7_1:PreT8, issue) 
 e3 <- regression_explore(df, a, b, compromise)
 

### 2021-05-27 src/analysis/explore_position_covid.R

@@ -1,10 +1,10 @@
 regression_explore <- function(df, a, b, compromise, issue){
   
   depVarList <- df %>% select(matches("PT[0-9]"))
-  indepVarList <- df %>% select(a, b, compromise, F2, F4, F7, F8, 
-                                PreT2:PreT7_7, issue)   
+  indepVarList <- df %>% select(a, b, compromise, F2, F4, F7, F8,  F9,
+                                PreT1:PreT7_7, issue)   
   allModels <- apply(depVarList,2,function(xl)lmer(xl ~ a * compromise * b +
-                                                     F2 + F4 + F7 + F8 +
+                                                     F2 + F4 + F7 + F8 + PreT1 +
                                                      PreT2 + PreT3 + PreT4 + PreT5 +
                                                      PreT6 + PreT7_1 + PreT7_2 +
                                                      PreT7_3 + PreT7_4 + PreT7_5 + 
@@ -36,7 +36,7 @@ regression_explore <- function(df, a, b, compromise, issue){
 }
 
 df <- d %>% select(a = gender, b = PreT8, compromise, 
-                   PT1:PT4, F2, F4, F7, F8, PreT2:PreT7_7, issue) 
+                   PT1:PT4, F2, F4, F7, F8, F9, PreT1:PreT7_7, issue) 
 e1 <- regression_explore(df, a, b, compromise)
 
 p1e <- e1 %>%
@@ -63,7 +63,7 @@ p1e <- e1 %>%
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") 
 
 df <- d %>% select(a = immigration, b = PreT8, compromise, 
-                   PT1:PT4, F2, F4, F7, F8, PreT2:PreT7_7, issue) 
+                   PT1:PT4, F2, F4, F7, F8, F9, PreT1:PreT7_7, issue) 
 e2 <- regression_explore(df, a, b, compromise)
 
 p2e <- e2 %>%
@@ -90,7 +90,7 @@ p2e <- e2 %>%
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") 
 
 df <- d %>% select(a = intersection, b = PreT8, compromise, 
-                   PT1:PT4, F2, F4, F7, F8, PreT2:PreT7_7, issue) 
+                   PT1:PT4, F2, F4, F7, F8, F9, PreT1:PreT7_7, issue) 
 e3 <- regression_explore(df, a, b, compromise)
 
 p3e <- e3 %>%

### 2021-05-27 src/analysis/explore_position_defense.R

@@ -1,10 +1,10 @@
 regression_explore <- function(df, a, b, compromise, issue){
   
   depVarList <- df %>% select(matches("PT[0-9]"))
-  indepVarList <- df %>% select(a, b, compromise, F2, F4, F7, F8, 
-                                PreT2, PreT4:PreT8, issue)   
+  indepVarList <- df %>% select(a, b, compromise, F2, F4, F7, F8, F9,
+                                PreT1, PreT2, PreT4:PreT8, issue)   
   allModels <- apply(depVarList,2,function(xl)lmer(xl ~ a * compromise * b +
-                                                     F2 + F4 + F7 + F8 +
+                                                     F2 + F4 + F7 + F8 + F9 + PreT1 +
                                                      PreT2 + PreT4 + PreT5 +
                                                      PreT6 + PreT7_1 + PreT7_2 +
                                                      PreT7_3 + PreT7_4 + PreT7_5 + 
@@ -36,7 +36,7 @@ regression_explore <- function(df, a, b, compromise, issue){
 }
 
 df <- d %>% select(a = gender, b = PreT3, compromise, 
-                   PT1:PT4, F2, F4, F7, F8, PreT2, PreT4:PreT8, issue) 
+                   PT1:PT4, F2, F4, F7, F8, F9, PreT1, PreT2, PreT4:PreT8, issue) 
 e1 <- regression_explore(df, a, b, compromise)
 
 p1e <- e1 %>%
@@ -63,7 +63,7 @@ p1e <- e1 %>%
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") 
 
 df <- d %>% select(a = immigration, b = PreT3, compromise, 
-                   PT1:PT4, F2, F4, F7, F8, PreT2, PreT4:PreT8, issue)  
+                   PT1:PT4, F2, F4, F7, F8, F9, PreT1, PreT2, PreT4:PreT8, issue)  
 e2 <- regression_explore(df, a, b, compromise)
 
 p2e <- e2 %>%
@@ -90,7 +90,7 @@ p2e <- e2 %>%
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") 
 
 df <- d %>% select(a = intersection, b = PreT3, compromise, 
-                   PT1:PT4, F2, F4, F7, F8, PreT2, PreT4:PreT8, issue) 
[…]

### 2021-05-27 src/analysis/explore_position_education.R

@@ -1,10 +1,10 @@
 regression_explore <- function(df, a, b, compromise, issue){
   
   depVarList <- df %>% select(matches("PT[0-9]"))
-  indepVarList <- df %>% select(a, b, compromise, F2, F4, F7, F8, 
-                                PreT2, PreT3, PreT5:PreT8, issue)   
+  indepVarList <- df %>% select(a, b, compromise, F2, F4, F7, F8, F9, 
+                                PreT1, PreT2, PreT3, PreT5:PreT8, issue)   
   allModels <- apply(depVarList,2,function(xl)lmer(xl ~ a * compromise * b +
-                                                     F2 + F4 + F7 + F8 +
+                                                     F2 + F4 + F7 + F8 + F9 + PreT1 +
                                                      PreT2 + PreT3 + PreT5 +
                                                      PreT6 + PreT7_1 + PreT7_2 +
                                                      PreT7_3 + PreT7_4 + PreT7_5 + 
@@ -36,7 +36,7 @@ regression_explore <- function(df, a, b, compromise, issue){
 }
 
 df <- d %>% select(a = gender, b = PreT4, compromise, 
-                   PT1:PT4, F2, F4, F7, F8, PreT2, PreT3, PreT5:PreT8, issue) 
+                   PT1:PT4, F2, F4, F7, F8,  F9, PreT1, PreT2, PreT3, PreT5:PreT8, issue) 
 e1 <- regression_explore(df, a, b, compromise)
 
 p1e <- e1 %>%
@@ -63,7 +63,7 @@ p1e <- e1 %>%
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") 
 
 df <- d %>% select(a = immigration, b = PreT4, compromise, 
-                   PT1:PT4, F2, F4, F7, F8, PreT2, PreT3, PreT5:PreT8, issue)  
+                   PT1:PT4, F2, F4, F7, F8, F9, PreT1, PreT2, PreT3, PreT5:PreT8, issue)  
 e2 <- regression_explore(df, a, b, compromise)
 
 p2e <- e2 %>%
@@ -90,7 +90,7 @@ p2e <- e2 %>%
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") 
 
 df <- d %>% select(a = intersection, b = PreT4, compromise, 
[…]

### 2021-05-27 src/analysis/explore_position_immigration.R

@@ -1,10 +1,10 @@
 regression_explore <- function(df, a, b, compromise, issue){
   
   depVarList <- df %>% select(matches("PT[0-9]"))
-  indepVarList <- df %>% select(a, b, compromise, F2, F4, F7, F8, 
+  indepVarList <- df %>% select(a, b, compromise, F2, F4, F7, F8,  F9,
                                 PreT2:PreT8, issue)   
   allModels <- apply(depVarList,2,function(xl)lmer(xl ~ a * compromise * b +
-                                                     F2 + F4 + F7 + F8 +
+                                                     F2 + F4 + F7 + F8 + F9 +
                                                      PreT2 + PreT3 + PreT4 + PreT5 +
                                                      PreT6 + PreT7_1 + PreT7_2 +
                                                      PreT7_3 + PreT7_4 + PreT7_5 + 
@@ -36,7 +36,7 @@ regression_explore <- function(df, a, b, compromise, issue){
 }
 
 df <- d %>% select(a = gender, b = PreT1, compromise, 
-                   PT1:PT4, F2, F4, F7, F8, PreT2:PreT8, issue) 
+                   PT1:PT4, F2, F4, F7, F8,  F9, PreT1:PreT8, issue) 
 e1 <- regression_explore(df, a, b, compromise)
 
 p1e <- e1 %>%
@@ -63,7 +63,7 @@ p1e <- e1 %>%
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") 
 
 df <- d %>% select(a = immigration, b = PreT1, compromise, 
-                   PT1:PT4, F2, F4, F7, F8, PreT2:PreT8, issue) 
+                   PT1:PT4, F2, F4, F7, F8, F9, PreT1:PreT8, issue) 
 e2 <- regression_explore(df, a, b, compromise)
 
 p2e <- e2 %>%
@@ -90,7 +90,7 @@ p2e <- e2 %>%
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") 
 
 df <- d %>% select(a = intersection, b = PreT1, compromise, 
-                   PT1:PT4, F2, F4, F7, F8, PreT2:PreT8, issue) 
+                   PT1:PT4, F2, F4, F7, F8, F9, PreT1:PreT8, issue) 
 e3 <- regression_explore(df, a, b, compromise)
 
 p3e <- e3 %>%
@@ -119,10 +119,10 @@ p3e <- e3 %>%
[…]

### 2021-05-27 src/analysis/explore_women_politics.R

@@ -1,10 +1,10 @@
 regression_explore <- function(df, a, b, compromise, issue){
   
   depVarList <- df %>% select(matches("PT[0-9]"))
-  indepVarList <- df %>% select(a, b, compromise, F2, F4, F7, F8, 
-                                PreT2:PreT4, PreT6:PreT8, issue)   
+  indepVarList <- df %>% select(a, b, compromise, F2, F4, F7, F8, F9, 
+                                PreT1:PreT4, PreT6:PreT8, issue)   
   allModels <- apply(depVarList,2,function(xl)lmer(xl ~ a * compromise * b +
-                                                     F2 + F4 + F7 + F8 +
+                                                     F2 + F4 + F7 + F8 + F9 + PreT1 +
                                                      PreT2 + PreT3 + PreT4 + 
                                                      PreT6 + PreT7_1 + PreT7_2 +
                                                      PreT7_3 + PreT7_4 + PreT7_5 + 
@@ -36,7 +36,7 @@ regression_explore <- function(df, a, b, compromise, issue){
 }
 
 df <- d %>% select(a = gender, b = PreT5, compromise, 
-                   PT1:PT4, F2, F4, F7, F8, PreT2:PreT4, 
+                   PT1:PT4, F2, F4, F7, F8, F9, PreT1:PreT4, 
                    PreT6:PreT8, issue) 
 e1 <- regression_explore(df, a, b, compromise)
 
@@ -64,7 +64,7 @@ p1e <- e1 %>%
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") 
 
 df <- d %>% select(a = immigration,  b = PreT5, compromise, 
-                   PT1:PT4, F2, F4, F7, F8, PreT2:PreT4, 
+                   PT1:PT4, F2, F4, F7, F8, F9, PreT1:PreT4, 
                    PreT6:PreT8, issue) 
 e2 <- regression_explore(df, a, b, compromise)
 
@@ -92,7 +92,7 @@ p2e <- e2 %>%
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") 
 
 df <- d %>% select(a = intersection, b = PreT5, compromise, 
-                   PT1:PT4, F2, F4, F7, F8, PreT2:PreT4, 
+                   PT1:PT4, F2, F4, F7, F8, F9, PreT1:PreT4, 
                    PreT6:PreT8, issue)  
 e3 <- regression_explore(df, a, b, compromise)
 

### 2021-05-27 src/analysis/explore_wtac.R

@@ -1,10 +1,10 @@
 regression_explore <- function(df, a, b, compromise, issue){
   
   depVarList <- df %>% select(matches("PT[0-9]"))
-  indepVarList <- df %>% select(a, b, compromise, F2, F4, F7, F8, 
-                                PreT2:PreT7_5, PreT7_7:PreT8, issue)   
+  indepVarList <- df %>% select(a, b, compromise, F2, F4, F7, F8, F9,
+                                PreT1:PreT7_5, PreT7_7:PreT8, issue)   
   allModels <- apply(depVarList,2,function(xl)lmer(xl ~ a * compromise * b +
-                                                     F2 + F4 + F7 + F8 +
+                                                     F2 + F4 + F7 + F8 + F9 + PreT1 +
                                                      PreT2 + PreT3 + PreT4 + PreT5 +
                                                      PreT6 + PreT7_1 + PreT7_2 +
                                                      PreT7_3 + PreT7_4 + PreT7_5 + 
@@ -36,7 +36,7 @@ regression_explore <- function(df, a, b, compromise, issue){
 }
 
 df <- d %>% select(a = gender, b = PreT7_6, compromise, 
-                   PT1:PT4, F2, F4, F7, F8, PreT2:PreT7_5, 
+                   PT1:PT4, F2, F4, F7, F8, F9, PreT1:PreT7_5, 
                    PreT7_7:PreT8, issue) 
 e1 <- regression_explore(df, a, b, compromise)
 
@@ -64,7 +64,7 @@ p1e <- e1 %>%
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") 
 
 df <- d %>% select(a = immigration, b = PreT7_6, compromise, 
-                   PT1:PT4, F2, F4, F7, F8, PreT2:PreT7_5, 
+                   PT1:PT4, F2, F4, F7, F8, F9, PreT1:PreT7_5, 
                    PreT7_7:PreT8, issue) 
 e2 <- regression_explore(df, a, b, compromise)
 
@@ -92,7 +92,7 @@ p2e <- e2 %>%
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") 
 
 df <- d %>% select(a = intersection, b = PreT7_6, compromise, 
-                   PT1:PT4, F2, F4, F7, F8, PreT2:PreT7_5, 
+                   PT1:PT4, F2, F4, F7, F8, F9, PreT1:PreT7_5, 
[…]

### 2021-05-27 src/analysis/h1.R

@@ -1,7 +1,7 @@
 # H1a & H1b
 issues <- unique(d$issue)
 for(i in 1:length(issues)){
-  df <- d %>% select(a = gender, compromise, PT1:PT4, F2, F4, F7, F8, PreT2:PreT8, issue) %>%
+  df <- d %>% select(a = gender, compromise, PT1:PT4, F2, F4, F7, F8, F9, PreT1:PreT8, issue) %>%
     filter(issue == issues[i]) %>%
     select(-issue)
   if(i==1){

### 2021-05-27 src/analysis/h2.R

@@ -1,7 +1,7 @@
 ## H2
 issues <- unique(d$issue)
 for(i in 1:length(issues)){
-  df <- d %>% select(a = immigration, compromise, PT1:PT4, F2, F4, F7, F8, PreT2:PreT8, issue) %>%
+  df <- d %>% select(a = immigration, compromise, PT1:PT4, F2, F4, F7, F8, F9, PreT1:PreT8, issue) %>%
     filter(issue == issues[i]) %>%
     select(-issue)
   if(i==1){

### 2021-05-27 src/analysis/h3-pooled.R

@@ -1,5 +1,5 @@
 ## H3
-df <- d %>% select(a = intersection, compromise, PT1:PT4,issue, F2, F4, F7, F8, PreT2:PreT8)
+df <- d %>% select(a = intersection, compromise, PT1:PT4,issue, F2, F4, F7, F8, F9, PreT1:PreT8)
 h3p <- pooled_regression(df, a, compromise, issue)
 
 p3p <- h3p %>%

### 2021-05-27 src/analysis/h3.R

@@ -1,7 +1,7 @@
 ## H3
 issues <- unique(d$issue)
 for(i in 1:length(issues)){
-  df <- d %>% select(a = intersection, compromise, PT1:PT4, F2, F4, F7, F8, PreT2:PreT8, issue) %>%
+  df <- d %>% select(a = intersection, compromise, PT1:PT4, F2, F4, F7, F8, F9, PreT1:PreT8, issue) %>%
     filter(issue == issues[i]) %>%
     select(-issue)
   if(i==1){

### 2021-05-27 src/lib/functions.R

@@ -19,9 +19,9 @@ fig_cols <- as.character(fig_cols[1:8])
 regression <- function(df, a, compromise){
   
   depVarList <- df %>% select(matches("PT[0-9]"))
-  indepVarList <- df %>% select(a, compromise, F2, F4, F7, F8, PreT2:PreT8) 
+  indepVarList <- df %>% select(a, compromise, F2, F4, F7, F8, F9, PreT1:PreT8) 
   allModels <- apply(depVarList,2,function(xl)lm(xl ~ a * compromise +
-                                                   factor(F2) + F4 + F7 + F8 +
+                                                   factor(F2) + F4 + F7 + F8 + F9 + PreT1 +
                                                    PreT2 + PreT3 + PreT4 + PreT5 +
                                                    PreT6 + PreT7_1 + PreT7_2 +
                                                    PreT7_3 + PreT7_4 + PreT7_5 + 
@@ -54,9 +54,9 @@ regression <- function(df, a, compromise){
 pooled_regression <- function(df, a, compromise, issue){
   
   depVarList <- df %>% select(matches("PT[0-9]"))
-  indepVarList <- df %>% select(a, compromise, F2, F4, F7, F8, PreT2:PreT8, issue) 
+  indepVarList <- df %>% select(a, compromise, F2, F4, F7, F8, F9, PreT1:PreT8, issue) 
   allModels <- apply(depVarList,2,function(xl)lmer(xl ~ a * compromise +
-                                                     F2 + F4 + F7 + F8 +
+                                                     F2 + F4 + F7 + F8 + F9 + PreT1 +
                                                      PreT2 + PreT3 + PreT4 + PreT5 +
                                                      PreT6 + PreT7_1 + PreT7_2 +
                                                      PreT7_3 + PreT7_4 + PreT7_5 + 

### 2021-05-31 report/draft.Rmd
updates

@@
 I inspect this using four different measures of how people can judge the quality of a political representative. 
-The upper-left panel of Figure \ref{fig:results} demonstrates that people's evaluations of women politicians compared to men politicians differ between measures -- displayed on the y-axis of the figure -- and between issue areas -- displayed with different colors in the figure.
+The upper-left panel of Figure \ref{fig:results} demonstrates that people's evaluations of women politicians compared to men politicians are typically higher -- displayed on the y-axis of the figure -- for all issues, except for the issue of immigration -- displayed with different colors in the figure.
 
-- Looking at trait evaluation, only women who compromise on the issue migration are evaluated more negatively then men, yet the coefficient is not statistically significant.
-For the other three issues -- COVID, defense, and education -- the coefficients are positive, yet not statistically significant.
+- Looking at trait evaluation, only women who compromise on the issues of education, defense, and COVID are seen as more positive than men, yet the coefficient is not statistically significant for the issue COVID.
 - The same pattern is shown for how well people feel represented by the politician.
 Women, compared to men, are lower evaluated for the issue migration, but higher evaluated for the other three issues.
-Only the effect of education is statistically significant.
-This indicates that if female polticians compromise and vote in favor of the bill on extending extra-curricular activities at elementary schools, people feel better represented by this politician compared to if the same compromise was made by a male politician.
-- Regarding feelings of favorability towards the politician, there is no statistical significant difference between male or female politicians who strike a compromise.
-The same holds for the politicians' career prospects.
+Only the effect of education and defense are statistically significant.
+This indicates that if female polticians compromise and vote in favor of the bill on extending extra-curricular activities at elementary schools or compromise and vote in favor of intensifying cooperation of military services, people feel better represented by this politician compared to if the same compromise was made by a male politician.
+- The same pattern also holds for the favorability towards the politician: compromising female politicians are seen as more favorable than male politicians, yet only statistically significant for the issues defense and Covid.
+- There is no statistical significant difference between male or female politicians who strike a compromise when it comes to evaluating politicians' career prospects.
 
@@
 - When women politicians stand their grounds, they are evaluated higher on their leadership skills than their male counterparts.
-This finding holds accross issues, but is not statistically significant for the issue immigration.
-- In addition, compared to male politicians, female politicians that stand their ground make people feel better represented, except when this is about an education-related policy.
+This finding holds accross issues, but is only statistically significant for the issue COVID.
+- In addition, compared to male politicians, female politicians that stand their ground make people feel better represented, except when this is about a COVID-related policy.
 This finding is statistically significant for the issues immigration and defense.
@@
 This finding is only statistically significant when women, compared to men, vote against a bill on intensifying cooperation of the army services.
-- Also, not striking a compromise is considered good for a women's career prospects, yet these findings are not statistically significant.
+- Also, not striking a compromise is considered good for a women's career prospects, yet these findings are not statistically significant except for the issue of defense.
 
@@
 - Regarding how well people feel represented, there is no difference between politicians with and without a migration background.
-- Looking at how favorable people feel towards a politcian, we see that people feel more favorable towards politician with a migration background when they compromise on issues related to immigration and education compared to politicians without a migration background, but not for issues related to COVID-19 and defense.
-- For career perspectives, people rate the career prospects more negative when a politician with a migration background compromises on the issue migration.
-For the other issues, there is no difference between politicians with and without a migration background.
+- Looking at how favorable people feel towards a politcian, we see that people feel more favorable towards politician with a migration background when they compromise on issues related to immigration compared to politicians without a migration background, but not for the other issues.
+- For career perspectives, people rate the career prospects more negative when a politician with a migration background compromises.
+Yet, this is only significant for the issues immigration and defense.
 
@@
 
-- Trait: no differences for COVID-19 and immigration, insignificant positive effects for defense and education, pooling significant positive effect
-- Representation: Positive and signicant for education, nothing for the other issues, pooling significant positive effect
+- Trait: no differences for COVID-19, defense and immigration, significant positive effects for education, pooling significant positive effect
+- Representation: Positive and signicant for education and defense, nothing for the other issues, pooling significant positive effect
 - Favorability:  Positive and signicant for education, nothing for the other issues, pooling significant positive effect
@@
 This hypothesis is tested in the lower-center-left panel of Figure \ref{fig:results} for the separate issues, and in the lower-right panel of Figure \ref{fig:results} pooling the issues.
+For none of the measures in both the analyses per issue and in the pooled analysis, we see support for the hypothesis.
 
-- Trait: positive and significant for COVID-19, nothing for the other issues or in the pooled analysis.
-- Representation: no differences
-- Favorability: positive and significant for COVID-19, nothing for the other issues or in the pooled analysis.
-- Career prospects:negative and significant for defense,  nothing for the other issues or in the pooled analysis.
-
-Paragraph on what it means for theory, and justification for explorations (below).
+_ ADD: Paragraph on what it means for theory, and justification for explorations (below)._
 

### 2021-05-31 src/analysis/h1.R

@@ -37,7 +37,7 @@ p1 <- h1 %>%
   labs(x = "", y = "Average Marginal Effects of Being a Women Politician",
        title = "Gender Hypothesis") +
   facet_grid(.~compromise) +
-  ylim(c(-.3, .7)) +
+  ylim(c(-.4, .7)) +
   theme(plot.title = element_text(hjust = 0.5),
         plot.subtitle = element_text(hjust = 0.5),
         legend.position="none",
